### 2020-04-04 milestone6.Rmd
milestone 6 done

---
title: "GOV 1006: Milestone 6"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/3/2020"
output: 
  bookdown::pdf_document2:
    keep_tex: true
bibliography: milestone5_bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

## Introduction

The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018). ^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0)] It was authored by Paul C. Bauer in 2018. The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general. Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.

The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general. Bauer also controls for variations in age, education, and party membership. Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon. All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.

Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy. These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions. However, Bauer does find that unemployment is negatively related to life satisfaction. People who are unemployed are generally less satisfied with their lives than those who are employed. This finding is consistent with previous research on the topic. Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals. For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.

## Replication

I the appendix, I provide five replicated tables from the original publication. Of the five, Tables 1,3,4,5 were all replicable with no discrepencies. However, my replication of Table 2, did not completely match that of the paper. In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source. In his replication material, I can find where Bauer creates each of the other tables but not Table 2. Nonetheless, I attempted to replicate the table and largely suceeded. There were two variations between our tables. Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent. These discrepencies need to be explored further.

## Extension

The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy. The goal of my extension to provide further insights and clarity into that relationship. I intend build off the general models created by Bauer by including an interaction term between education and age in the regressions. As it stands, Bauer uses an additive regression with age, education, and membership as the controls. Given the entirety of the dataset is used in the current analysis, there is a limitation as to what is available for my extension. However, I feel that the addition of an interaction term between education and age could prove to be a valuable contribution to the models presented in the paper. My assumption is that there could be heterogeneous effects of education on the relationship between unemployment and trust in government or satisfaction with democracy depending on one's age. This proposed interaction is relatively straight forward.

Though the inclusion of the interaction is valuable, I feel there is an even more important extension I can attach to Bauer’s paper. Because his paper utilizes panel data, it tracks households across time. He mentions a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment. My hope is to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time. By identifying these households, I would like to test how their unemployment experiences effect their views on democracy and the government and compare that to households with one-off unemployment and households without unemployment. My hypothesis is in line with Bauer’s. I predict that households that are experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.

I’m still working through my exact plan of action for completing the long-term vs. short-term unemployment extension. However, my initial thoughts suggest that I will create a new variable indicating whether someone had been unemployed the year before. That variable can be added to the regression as a control. I am also thinking about creating a variable with the number of years a household reported being unemployed during the reporting and attaching that to the regression. I may end up running separate regressions so to avoid overfitting the data but we will see.

\newpage

## Appendix

```{r data}

# Loaded the LISS data from the directory

load(file = "./data-long-liss.RData")

# Saved the loaded data as liss

liss <- data.long.liss

# Loaded the SHP data from the directory

load(file = "./data-long-shp.RData")

# Saved the data as SHP

shp <- data.long.shp
```

```{r table1, results='asis'}

# Set results = 'asis' to get the stargazer output to show up

# Reformatted the liss data to get it into the manner in which it is presented in the table
# Caluclated the total number of responses for each year broken down by employed vs unemployed
# Spread that data to make it wide rather than long

liss_1 <- liss %>%
  group_by(time, unemployed) %>%
  summarize(n = n()) %>%
  drop_na() %>%
  spread(time, n) %>%
  select(-unemployed)

# Did the same reformating for the shp data and then added the liss data beneath it using
# rbind_fill
# Changed all NA values to blanks to match the table formatting

shp_1 <- shp %>%
  group_by(time, unemployed) %>%
  summarize(n = n()) %>%
  drop_na() %>%
  spread(time, n) %>%
  select(-unemployed) %>%
  rbind.fill(liss_1) %>%
  replace(is.na(.), "")

# Added rownames to the conjoined table in accordance with what they are in the paper

row.names(shp_1) <- c("SHP: employed", "SHP: unemployed", "LISS: employed", "LISS: unemployed")

# Displayed the table using stargazer
# Set header to false to hide the comments from the creator of the package
# Set summary to false to just display the table as is
# Changed font size and column separation width to get the table the right size for the pdf

stargazer(
  shp_1,
  header = FALSE,
  summary = FALSE,
  font.size = "small",
  column.sep.width = "-7.5pt",
  title = "Unemployment across Years",
  notes = " LISS = Longitudinal Internet Studies for the Social Sciences; SHP = Swiss Household Panel."
)
```

```{r table2,results='asis'}

# I begin with the LISS data
# I go through each column and classify whether there was a response or not (- for response and
# blank for NA)
# I summarize to calculate which years there were no responses for a given survey question
# I spread the data to get the years as columns

liss_2 <- liss %>%
  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
  group_by(time) %>%
  summarize(tig_2 = sum(trust_in_government),
            swd_2 = sum(satisfaction_with_democracy),
            ls_2 = sum(life_satisfaction),
            ue_2 = sum(unemployed)) %>%
  mutate_at(c("tig_2", "swd_2", "ls_2", "ue_2"), ~ifelse(. == 0, "", "-")) %>%
  gather("topic", "value", tig_2:ue_2) %>%
  group_by(topic) %>%
  spread(time, value)

# I create an ordering of rows that will be used in the below table formatting

ordering <- c("tig","swd","ls","ue","tig_2","swd_2","ls_2","ue_2")

# I repeat the steps from LISS for SHP
# Once I have made the table and add the LISS table below
# I arrange by the ordering vector I just made

shp_2<- shp %>%
  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
  group_by(time) %>%
  summarize(tig = sum(trust_in_government),
            swd = sum(satisfaction_with_democracy),
            ls = sum(life_satisfaction),
            ue = sum(unemployed)) %>%
  mutate_at(c("tig", "swd", "ls", "ue"), ~ifelse(. == 0, "", "-")) %>%
  gather("topic", "value", tig:ue) %>%
  group_by(topic) %>%
  spread(time, value) %>%
  rbind.fill(liss_2) %>%
  replace(is.na(.), "") %>%
  mutate(topic = factor(topic, levels = ordering)) %>%
  arrange(topic) %>%
  select(-topic)

# Change row names to match those in the paper

row.names(shp_2) <- c("Trust in government (SHP)", "Satisfaction with democracy (SHP", "Life Satisfaction (SHP)", "Employment Status (SHP)", "Trust in government (LISS)", "Satisfaction with democracy (LISS)", "Life Satisfaction (LISS)", "Employment Status (LISS)")

# Displayed the table using stargazer
# Set header to false to hide the comments from the creator of the package
# Set summary to false to just display the table as is
# Changed font size and column separation width to get the table the right size for the pdf

stargazer(
  shp_2,
  header = FALSE,
  summary = FALSE,
  font.size = "small",
  column.sep.width = "-7.5pt",
  title = "Measures across panel waves in the SHP and the LISS"
)
```

```{r table3, results='asis'}

# SHP
# I run six regressions
# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
# The first regression is just with unemployed as the indenpendent variable
# The second regression includes the controls (age, education, and member)
# The regression uses a pooling technique (plm) to track observations across units (households) 
# over time

shp.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

# LISS
# Same as above but with the LISS data instead of the SHP data

liss.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

# I display the results using a stargazer table
# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
# adjusting the separation width between columns
# I can't figure out how to add a split header above the dependent variables to separate between 
# SHP and LISS
# I will keep working on this

stargazer(shp.fit.pooling.tig, shp.fit.pooling.control.tig, shp.fit.pooling.swd, shp.fit.pooling.control.swd, shp.fit.pooling.ls, shp.fit.pooling.control.ls, liss.fit.pooling.tig, liss.fit.pooling.control.tig, liss.fit.pooling.swd, liss.fit.pooling.control.swd, liss.fit.pooling.ls, liss.fit.pooling.control.ls,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: pooled models",
          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )

```

```{r table4, results = 'asis'}

# SHP
# The same process as above but I used a fixed effects model instead of a pooled model
# The only difference is I change model from "pooled" to "within"

shp.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

# LISS
# Same as for SHP but with the LISS data

liss.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

# Stargazer output with the same formatting as Table 3

stargazer(shp.fit.fe.tig, shp.fit.fe.control.tig, shp.fit.fe.swd, shp.fit.fe.control.swd, shp.fit.fe.ls, shp.fit.fe.control.ls, liss.fit.fe.tig, liss.fit.fe.control.tig, liss.fit.fe.swd, liss.fit.fe.control.swd, liss.fit.fe.ls, liss.fit.fe.control.ls,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-3",
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"), 
          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

```{r table5calc, include=FALSE}

# SHP
# Same regressions but this time with the weighted fixed effects
# I didn't really understand how these were created so I largely mimicked what Bauer did in his
# replication code

shp.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                      unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# LISS
# Same as SHP but with LISS data

liss.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# The above regressions do not create an output that can be displayed through stargazer
# Instead I needed to manually run the regression with the included weights and then manually
# input those values into stargazer
# Again, I didn't really know how to do this so I just followed what Bauer did.

  regressors <- c("Unemployed", "Age", "Education", "Member")
  d <- as.data.frame(matrix(rnorm(10 * 5), nc = 5))
  dep.var <- "Trust_in_government"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p1 <- lm(f, d)
  dep.var <- "Satisfaction_with_democracy"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p2 <- lm(f, d)
  dep.var <- "Life_satisfaction"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p3 <- lm(f, d)

```

```{r table5output, results='asis'}

# Stargazer output
# I manually pull out the coefficient values from the regressions and add those to the
# skeleton of the regression that was created above
# I have to do this for each coefficient, each standard error, and each t and p value

# Then I format the stargazer table in the same manner as the previous two

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    coef = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,1]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,1])

                ),
    se = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,2]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,2])
              ),
    t = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,3]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,3])

             ),  
    p = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,4]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,4])
             ),  
    omit.stat = "all",
    notes = "SEs in parentheses.",
    notes.append = TRUE,
    font.size = "tiny",
    digits = 2,
    column.sep.width = "-7.5pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001),
    covariate.labels = c("Unemployed", "Age", "Education", "Member"),
    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
    header = FALSE)

```

\newpage

## References

### 2020-04-18 milestone6.Rmd
still can't figure out the alignment of my stargazer tables

@@
     keep_tex: true
+document_class: article
 bibliography: milestone5_bib.bib
@@
 
+library(rsconnect)
 library(stargazer)
@@
 library(tidyverse)
+```
+
+```{r data}
+
+# Loaded the LISS data from the directory
+
+load(file = "./data-long-liss.RData")
+
+# Saved the loaded data as liss
+
+liss <- data.long.liss
+
+# Loaded the SHP data from the directory
+
+load(file = "./data-long-shp.RData")
+
+# Saved the data as SHP
+
+shp <- data.long.shp
 ```
@@
 
+```{r extension}
+
+liss_2.0 <- liss %>%
+  group_by(unit) %>%
+  summarize(total_unemployment = sum(unemployed))
+
+liss_3.0 <- liss %>%
+  filter(time == 2014) %>%
+  inner_join(liss_2.0, by = "unit")
+
+modelExtension_1 <- lm(trust_in_government ~ unemployed + age + education + member, data = liss_3.0)
+
+liss <- liss %>%
+  group_by(unit) %>%
+  arrange(time) %>%
+  mutate(lagged_unemployed = lag(unemployed)) %>%
+  ungroup(unit)
+
+shp_2.0 <- shp %>%
+  group_by(unit) %>%
+  summarize(total_unemployment = sum(unemployed))
+
+shp <- shp %>%
+  group_by(unit) %>%
+  arrange(time) %>%
+  mutate(lagged_unemployed = lag(unemployed)) %>%
+  ungroup(unit)
+
+```
+
+```{r tableExtension, results = 'asis'}
+
+# SHP
+# The same process as above but I used a fixed effects model instead of a pooled model
+# The only difference is I change model from "pooled" to "within"
+
+shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = shp,
+                        index = c("unit", "time"),
+                        model = "within")
+
+# LISS
+# Same as for SHP but with the LISS data
+
+liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
+                        data = liss,
+                        index = c("unit", "time"),
+                        model = "within")
+
+# Stargazer output with the same formatting as Table 3
+
+stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
+          omit.stat=c("LL","ser","f","adj.rsq"),
+          header = FALSE,
+          font.size = "tiny",
+          digits = 2,
+          label = "table-5",
+          column.sep.width = "-7.5pt",
+          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
+          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
+          covariate.labels = c("Unemployed", "Lagged Unemployed", "Unemployed:Lagged Unemployed", "Age", "Education", "Member"),
+          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
+          model.names = FALSE,
+          model.numbers = FALSE
+          )
+```
+
 \newpage
@@
 ## Appendix
-
-```{r data}
-
-# Loaded the LISS data from the directory
-
-load(file = "./data-long-liss.RData")
-
-# Saved the loaded data as liss
-
-liss <- data.long.liss
-
-# Loaded the SHP data from the directory
-
-load(file = "./data-long-shp.RData")
-
-# Saved the data as SHP
-
-shp <- data.long.shp
-```
 

### 2020-04-18 milestone7.Rmd
still can't figure out the alignment of my stargazer tables

---
title: "GOV 1006: Milestone 7"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/17/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "left")

library(rsconnect)
library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

```{r data}

# Loaded the LISS data from the directory

load(file = "./data-long-liss.RData")

# Saved the loaded data as liss

liss <- data.long.liss

# Loaded the SHP data from the directory

load(file = "./data-long-shp.RData")

# Saved the data as SHP

shp <- data.long.shp
```

## Introduction

The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018). ^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0)] It was authored by Paul C. Bauer in 2018. The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general. Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.

The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general. Bauer also controls for variations in age, education, and party membership. Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon. All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.

Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy. These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions. However, Bauer does find that unemployment is negatively related to life satisfaction. People who are unemployed are generally less satisfied with their lives than those who are employed. This finding is consistent with previous research on the topic. Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals. For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.

## Literature Review

The impetus for Bauer's paper relies on the fundamental assumption that should a person blame the government or its institutions for their current situation in life, a decrease in the quality of that situation would result in a corresponding decrease in their satisfaction with the government. This assumption stems from the work of John Hudson who examined the relationship between trust in institutions and one's subjective well-being (@hudson2006). Research shows a statistically significant relationship between one's employment status and their life satisfaction (@jimeno2007). As one moves from employed to unemployed, their life satisfaction tends to decrease. Given the two findings, the aim of Bauer's work is to test the hypothesis that unemployment leads to lower levels of trust in government and satisfaction with democracy.

## Replication

I the appendix, I provide five replicated tables from the original publication. Of the five, Tables 1,3,4,5 were all replicable with no discrepencies. However, my replication of Table 2, did not completely match that of the paper. In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source. In his replication material, I can find where Bauer creates each of the other tables but not Table 2. Nonetheless, I attempted to replicate the table and largely suceeded. There were two variations between our tables. Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent. These discrepencies need to be explored further.

## Extension

The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy. The goal of my extension to provide further insights and clarity into that relationship.

Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes. In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment. Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.

My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time. By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment. My hypothesis was in line with Bauer’s. I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.

To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment. I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment. The coefficient on the interaction term represents a household with unemployment in the present year and in the year before. The interaction coefficient is the one I am most interested in. As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.

```{r extension}

liss <- liss %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

shp <- shp %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

```

```{r tableExtension1, results='asis'}

# SHP
# I run six regressions
# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
# The first regression is just with unemployed as the indenpendent variable
# The second regression includes the controls (age, education, and member)
# The regression uses a pooling technique (plm) to track observations across units (households) 
# over time

shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

# LISS
# Same as above but with the LISS data instead of the SHP data

liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

# I display the results using a stargazer table
# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
# adjusting the separation width between columns
# I can't figure out how to add a split header above the dependent variables to separate between 
# SHP and LISS
# I will keep working on this

stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          column.sep.width = "-8.5pt",
          title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )

```

```{r tableExtension2, results = 'asis'}

# SHP
# The same process as above but I used a fixed effects model instead of a pooled model
# The only difference is I change model from "pooled" to "within"

shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

# LISS
# Same as for SHP but with the LISS data

liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

# Stargazer output with the same formatting as Table 3

stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-5",
          column.sep.width = "-8.5pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

```{r extension3, include=FALSE}

# SHP
# Same regressions but this time with the weighted fixed effects
# I didn't really understand how these were created so I largely mimicked what Bauer did in his
# replication code

shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                      unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# LISS
# Same as SHP but with LISS data

liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# The above regressions do not create an output that can be displayed through stargazer
# Instead I needed to manually run the regression with the included weights and then manually
# input those values into stargazer
# Again, I didn't really know how to do this so I just followed what Bauer did.

  regressors_int <- c("Unemployed", "Lagged")

  regressors_cont <- c("Age", "Education", "Member")

  d <- as.data.frame(matrix(rnorm(10 * 7), nc = 7))

  dep.var1 <- "Trust_in_government"

  names(d) <- c(dep.var1, regressors_int, regressors_cont)

  f <- as.formula(paste(dep.var1, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))

  p1 <- lm(f, d)

  dep.var2 <- "Satisfaction_with_democracy"

  names(d) <- c(dep.var2, regressors_int, regressors_cont)

   f <- as.formula(paste(dep.var2, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))

  p2 <- lm(f, d)

  dep.var3 <- "Life_satisfaction"

  names(d) <- c(dep.var3, regressors_int, regressors_cont)

   f <- as.formula(paste(dep.var3, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))

  p3 <- lm(f, d)

```

```{r table3output, results='asis'}

# Stargazer output
# I manually pull out the coefficient values from the regressions and add those to the
# skeleton of the regression that was created above
# I have to do this for each coefficient, each standard error, and each t and p value

# Then I format the stargazer table in the same manner as the previous two

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    coef = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])

                ),
    se = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
              ),
    t = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])

             ),  
    p = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
             ),  
    omit.stat = "all",
    notes = "SEs in parentheses.\n Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
    notes.append = TRUE,
    font.size = "tiny",
    digits = 2,
    column.sep.width = "-10pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001),
    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
    header = FALSE
    )

```

\newpage

## Conclusion

\newpage

## References

### 2020-04-18 milestone6.Rmd
got it to publish

@@
 date: "4/3/2020"
+abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy.
+I was able to completely replicate the majority of his findings aside from a summary table of the data.
+My extension evaluates how consistent or long-term unemployment may impact one's views.
+Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
 output: 
@@
     keep_tex: true
+    toc: no
 document_class: article
@@
 The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018).
-^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0)] It was authored by Paul C.
+^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone6/milestone6.pdf).] It was authored by Paul C.
 Bauer in 2018.
@@
 The goal of my extension to provide further insights and clarity into that relationship.
-I intend build off the general models created by Bauer by including an interaction term between education and age in the regressions.
-As it stands, Bauer uses an additive regression with age, education, and membership as the controls.
-Given the entirety of the dataset is used in the current analysis, there is a limitation as to what is available for my extension.
-However, I feel that the addition of an interaction term between education and age could prove to be a valuable contribution to the models presented in the paper.
-My assumption is that there could be heterogeneous effects of education on the relationship between unemployment and trust in government or satisfaction with democracy depending on one's age.
-This proposed interaction is relatively straight forward.
 
-Though the inclusion of the interaction is valuable, I feel there is an even more important extension I can attach to Bauer’s paper.
-Because his paper utilizes panel data, it tracks households across time.
-He mentions a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-My hope is to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
-By identifying these households, I would like to test how their unemployment experiences effect their views on democracy and the government and compare that to households with one-off unemployment and households without unemployment.
-My hypothesis is in line with Bauer’s.
-I predict that households that are experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
+Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes.
+In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
+Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
 
-I’m still working through my exact plan of action for completing the long-term vs.
-short-term unemployment extension.
-However, my initial thoughts suggest that I will create a new variable indicating whether someone had been unemployed the year before.
-That variable can be added to the regression as a control.
-I am also thinking about creating a variable with the number of years a household reported being unemployed during the reporting and attaching that to the regression.
-I may end up running separate regressions so to avoid overfitting the data but we will see.
+My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
+By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment.
+My hypothesis was in line with Bauer’s.
+I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
+
+To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment.
+I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment.
+The coefficient on the interaction term represents a household with unemployment in the present year and in the year before.
+The interaction coefficient is the one I am most interested in.
+As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.
 

### 2020-04-18 milestone7.Rmd
got it to publish

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.align = "left")
+knitr::opts_chunk$set(echo = FALSE)
 
@@
 The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018).
-^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0)] It was authored by Paul C.
+^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] It was authored by Paul C.
 Bauer in 2018.
@@
     omit.stat = "all",
-    notes = "SEs in parentheses.\n Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
+    notes = "SEs in parentheses. Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
     notes.append = TRUE,

### 2020-04-22 milestone8.Rmd
update with milestone 8

--- 2020-04-18 milestone7.Rmd
@@
 ---
-title: "GOV 1006: Milestone 7"
+title: "GOV 1006: Milestone 8"
 subtitle: "Paper Replication"
@@
 bibliography: milestone5_bib.bib
+mainfont: Wingdings
+sansfont: Wingdings
+fontsize: 12pt
 ---
@@
 
-## Introduction
+# Introduction
 
-The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018).
-^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] It was authored by Paul C.
-Bauer in 2018.
-The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general.
-Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.
-
-The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general.
-Bauer also controls for variations in age, education, and party membership.
-Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon.
-All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.
-
-Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy.
+"Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation", authored by Paul Bauer, explores how unemployment affects a person's trust in the government and their views towards democracy in general (@bauer2018).
+Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment and feelings towards government on an individual level.
+Due to prior findings on the link between life satisfaction and unemployment, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon.
+Bauer finds that a household's unemployment status has no consistent effect on either trust in the government or satisfaction with democracy.
 These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions.
-However, Bauer does find that unemployment is negatively related to life satisfaction.
+However, Bauer does find that unemployment is negatively associated with life satisfaction.
 People who are unemployed are generally less satisfied with their lives than those who are employed.
-This finding is consistent with previous research on the topic.
+This finding is consistent with previous research on the topic (@hudson2006; @jimeno2007).
 Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
@@
 
-## Literature Review
+Starting with the replication materials provided by Bauer through the Harvard Dataverse, I worked to replicate the findings of Bauer's paper (@dataverse).^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is available through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] As Bauer did, I conducted my replication and subsequent extension in RStudio (@RStudio).
+Thanks to Bauer well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.
+
+# Literature Review
 
@@
 
-## Replication
+# Replication
 
@@
 
-## Extension
+# Extension
 
@@
 As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.
+
+My findings largely confirmed Bauer's.
+The interaction term between unemployment in the present year and unemployment in the previous year was not statistically significant.
+The lack of statistical significance indicates that the aggregation of two years of unemployment does not create significant impacts on one's views towards government and democracy.
+However, in the dataset from Switzerland (SHP) there was a statistically significant negative relationship between satisfaction with democracy and lagged unemployment.
+This relationship is only present in the pooled model and the fixed effects model.
+Because the relationship between lagged unemployment and satisfaction with democracy is not present in the weighted fixed effects model which is supposed to be the most robust model, it is unclear how strong that finding is.
 
@@
 
-## Conclusion
+# Conclusion
 
@@
 
-## References
+# References

### 2020-04-26 milestone8.Rmd
completed milestone 8 - rough draft of my paper

@@
 title: "GOV 1006: Milestone 8"
-subtitle: "Paper Replication"
+subtitle: "Paper Replication Rough Draft"
 author: "Pieter Quinton"
 date: "4/17/2020"
-abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy.
+abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy.
 I was able to completely replicate the majority of his findings aside from a summary table of the data.
 My extension evaluates how consistent or long-term unemployment may impact one's views.
-Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
+Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
 output: 
@@
 
-```{r data}
-
-# Loaded the LISS data from the directory
-
-load(file = "./data-long-liss.RData")
-
-# Saved the loaded data as liss
-
-liss <- data.long.liss
-
-# Loaded the SHP data from the directory
-
-load(file = "./data-long-shp.RData")
-
-# Saved the data as SHP
-
-shp <- data.long.shp
-```
-
 # Introduction
@@
 "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation", authored by Paul Bauer, explores how unemployment affects a person's trust in the government and their views towards democracy in general (@bauer2018).
-Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment and feelings towards government on an individual level.
-Due to prior findings on the link between life satisfaction and unemployment, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon.
+Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment status and feelings towards government on an individual level.
+Due to prior findings on the link between life satisfaction and unemployment, Bauer uses that relationship as a base metric to evaluate the magnitude of the other effects upon.
 Bauer finds that a household's unemployment status has no consistent effect on either trust in the government or satisfaction with democracy.
@@
 This finding is consistent with previous research on the topic (@hudson2006; @jimeno2007).
-Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
+Moving forward, Bauer indicates an interest in increasing the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
 For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.
@@
 Starting with the replication materials provided by Bauer through the Harvard Dataverse, I worked to replicate the findings of Bauer's paper (@dataverse).^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is available through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] As Bauer did, I conducted my replication and subsequent extension in RStudio (@RStudio).
-Thanks to Bauer well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.
+Thanks to Bauer's well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.
+
+In addition to replicating Bauer's work, I conducted an extension utilizing both his data and models to begin to understand a potential variation in effect between short-term and long-term unemployment.
+Prior to conducting the extension, I began with the hypothesis that households experiencing longer bouts of unemployment would be more likely to harbor negative feelings towards the current system of government than those with singular years of unemployment.
+I built my extension off the existing work from Bauer, making a slight tweak to his models.
+Taking advantage of the panel data, I created a new variable indicating whether a household was unemployed in the previous year.
+I included this variable in Bauer's regression model as an interaction term with the existing unemployment variable.
+The inclusion of the lagged unemployment variable allowed me to test the effect of two years of continuous unemployment on a household's feelings towards government and democracy.
+
+Despite, the inclusion of lagged unemployment, I observed no meaningful and consistent changes to the regression model results.
+The interaction between unemployment and lagged unemployment was not statistically significant, contradicting my initial hypothesis.
+The lagged unemployment variable was statistically significant, on its own, but not in the most robust model, weighted fixed effects.
+Again, I echo Bauer's concerns that more data is needed to concretely test the differences in effect between long-term and short-term unemployment.
+However, the heterogenous effect sizes for lagged unemployment across model types indicates that this is a relationship worth studying in more detail.
 
@@
 
+Bauer's work draws on the theoretical concepts of James Laurence who argued that the loss of one's job may lead to a deterioration of their trust in the economic system (@laurence2015).
+Furthermore, the loss of one's job brings people into closer connect with bureaucratic institutions and government social programs.
+Such interactions may incite a frusturation with the way in which the government supports individuals experiencing joblessness and could lead to a dissolusionment with the current government (@waters2007).
+It is from this theoretical basis that Bauer hypothesizes unemployment to be negatively associated with trust in government and satisfaction with democracy.
+There is, however, an alternative theory.
+Should a person feel supported and appreciated by the government and its programs during their period of joblessness, their feelings towards the government may not change or may even improve (@roth2009).
+
 # Replication
 
-I the appendix, I provide five replicated tables from the original publication.
-Of the five, Tables 1,3,4,5 were all replicable with no discrepencies.
-However, my replication of Table 2, did not completely match that of the paper.
-In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source.
+Using Bauer's data and original code, I worked to replicate five of the tables from his publication.
+Of the five, Tables 1,3,4,5 were replicable with no discrepencies.
+My results matched his exactly.
+However, my replication of Table 2 did not completely match that of the paper.
+In reviewing the code for Bauer's paper, it appears as though he inputs that table from another source.
 In his replication material, I can find where Bauer creates each of the other tables but not Table 2.
 Nonetheless, I attempted to replicate the table and largely suceeded.
-There were two variations between our tables.
+Table 2 is a summary table of the data indicating years that data is present from each of the survey questions.
+Utilizing the data provided by Bauer, I created a similar version of that table.
+However, there were two variations between our tables.
 Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent.
-These discrepencies need to be explored further.
+These discrepencies need to be explored further especially considering I was able to get the same regression outputs as Bauer using the data he provided.
 
@@
 
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
+The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction with democracy.
 The goal of my extension to provide further insights and clarity into that relationship.
 
-Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes.
-In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
+Because Bauer utilizes panel data, he is able to track households across time, providing an opportunity to analyze multi-year changes.
+However, Bauer, in his conclusion, discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
+Though Bauer, correctly, acknowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
 
@@
 To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment.
-I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment.
+I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction term with unemployment.
 The coefficient on the interaction term represents a household with unemployment in the present year and in the year before.
@@
 
+The first regression, displayed in Table 1, illustrates the results of the pooled model.
+In that model, unemployed is statistically significant across all questions of both surveys.
+Lagged unemployed is statistically significant across all questions from the SHP survey but is only statistically significant for the life satisfaction question of the LISS survey.
+The interaction term is only statistically significant for the life statisfaction question of each survey.
+
+\input{./extension-table-1.tex}
+
+Because were are unable to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model.
+There are strong differences between the pooled model and the fixed effects model.
+The size of the coefficients has dropped across all of the covariates by a considerable amount.
+As such, fewer coefficients are statistically significant.
+Unemployed is no longer statistically significant, aside from the life satisfaction questions.
+Lagged unemployed remains statistically significant for satisfaction with democracy while the interaction term is only statistically significant for life satisfaction.
+
+\input{./extension-table-2.tex}
+
+Finally, I conduct the regression analysis using the weighted fixed effects model used by Bauer.
+The coefficients have remained similar, in size, to the fixed effects model.
+However, lagged unemployed and the interaction between unemployed and lagged unemployed are no longer statistically significant for any question.
+Unemployed is statistically significant for the life satisfaction question.
+
+\input{./extension-table-3.tex}
+
 My findings largely confirmed Bauer's.
+Unemployment does not appear to have a statistically significant effect on trust in government or satisfaction with democracy.
 The interaction term between unemployment in the present year and unemployment in the previous year was not statistically significant.
@@
 This relationship is only present in the pooled model and the fixed effects model.
-Because the relationship between lagged unemployment and satisfaction with democracy is not present in the weighted fixed effects model which is supposed to be the most robust model, it is unclear how strong that finding is.
+Because the relationship between lagged unemployment and satisfaction with democracy is not present in the weighted fixed effects model, supposedly the most robust model, it is unclear how strong that finding is.
 
-```{r extension}
+# Conclusion
 
-liss <- liss %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
+In 2018, Paul Bauer published the paper, "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" in which he explored the relationship between a person's unemployment status and their trust in government and satisfaction with democracy (@bauer2018).
+Using data from the SHP and LISS household surveys, Bauer found that there was no statistically significant effect between unemployment and either trust in government or statisfaction with democracy.
+These findings challenged his hypothesis that short-term unemployment would people to loss faith in the government and its institutions.
+Bauer's hypothesis was based on theory and prior findings of a link between unemployment and decreasing life satisfcation.
 
-shp <- shp %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
+Using RStudio, I took Bauer's data and models and attempted to explore the possibility of heterogenous effects between short-term and long-term unemployment.
+I took advantage of the panel data to create a variable called lagged unemployment, which indicated whether a household had been unemployed in the previous year.
+I included the lagged unemployment variable in Bauer's regression models as an interaction term with unemployment.
+I was very interested in the coefficient on the interaction term (signifying a household that was unemployed in both the previous year and the current year).
+I assumed, like Bauer, that the extended period of unemployment would lead to a decrease in their trust in government and satisfaction with democracy.
+The results from the regressions disproved that hypothesis and reaffirmed Bauer's findings.
+Again, there were no statistically significant effects from the longer period of unemployment on either trust in government or satisfaction with democracy.
 
-```
-
-```{r tableExtension1, results='asis'}
-
-# SHP
-# I run six regressions
-# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
-# The first regression is just with unemployed as the indenpendent variable
-# The second regression includes the controls (age, education, and member)
-# The regression uses a pooling technique (plm) to track observations across units (households) 
-# over time
-
-shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# LISS
-# Same as above but with the LISS data instead of the SHP data
-
-liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# I display the results using a stargazer table
-# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
-# adjusting the separation width between columns
-# I can't figure out how to add a split header above the dependent variables to separate between 
-# SHP and LISS
-# I will keep working on this
-
-stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          column.sep.width = "-8.5pt",
-          title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
-          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-
-```
-
-```{r tableExtension2, results = 'asis'}
-
-# SHP
-# The same process as above but I used a fixed effects model instead of a pooled model
-# The only difference is I change model from "pooled" to "within"
-
-shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# LISS
-# Same as for SHP but with the LISS data
-
-liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# Stargazer output with the same formatting as Table 3
-
-stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          label = "table-5",
-          column.sep.width = "-8.5pt",
-          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
-          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-```
-
-```{r extension3, include=FALSE}
-
-# SHP
-# Same regressions but this time with the weighted fixed effects
-# I didn't really understand how these were created so I largely mimicked what Bauer did in his
-# replication code
-
-shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                      unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# LISS
-# Same as SHP but with LISS data
-
-liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# The above regressions do not create an output that can be displayed through stargazer
-# Instead I needed to manually run the regression with the included weights and then manually
-# input those values into stargazer
-# Again, I didn't really know how to do this so I just followed what Bauer did.
-
-  regressors_int <- c("Unemployed", "Lagged")
-
-  regressors_cont <- c("Age", "Education", "Member")
-
-  d <- as.data.frame(matrix(rnorm(10 * 7), nc = 7))
-
-  dep.var1 <- "Trust_in_government"
-
-  names(d) <- c(dep.var1, regressors_int, regressors_cont)
-
-  f <- as.formula(paste(dep.var1, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p1 <- lm(f, d)
-
-  dep.var2 <- "Satisfaction_with_democracy"
-
-  names(d) <- c(dep.var2, regressors_int, regressors_cont)
-
-   f <- as.formula(paste(dep.var2, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p2 <- lm(f, d)
-
-  dep.var3 <- "Life_satisfaction"
-
-  names(d) <- c(dep.var3, regressors_int, regressors_cont)
-
-   f <- as.formula(paste(dep.var3, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p3 <- lm(f, d)
-
-```
-
-```{r table3output, results='asis'}
-
-# Stargazer output
-# I manually pull out the coefficient values from the regressions and add those to the
-# skeleton of the regression that was created above
-# I have to do this for each coefficient, each standard error, and each t and p value
-
-# Then I format the stargazer table in the same manner as the previous two
-
-  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
-    coef = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])
-
-                ),
-    se = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
-              ),
-    t = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])
-
-             ),  
-    p = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
-             ),  
-    omit.stat = "all",
-    notes = "SEs in parentheses. Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
-    notes.append = TRUE,
-    font.size = "tiny",
-    digits = 2,
-    column.sep.width = "-10pt", 
-    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
-    digit.separator="",
-    rownames = FALSE,
-    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
-    model.names = FALSE,
-    model.numbers = FALSE,
-    star.cutoffs=c(0.05,0.01,0.001),
-    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-    header = FALSE
-    )
-
-```
+Both my results, and Bauer's, can offer encouraging interpretations.
+As Felix Roth theorized, positive interactions with government programs and institutions arising from one's unemployment may in fact lead to improvements in that individuals feelings towards the government, or at the very least no real change (@roth2009).
+It is possible that the lack of statistically significant effects in the regression models is due to highly effective government programs for those experiencing joblessness in Switzerland and the Netherlands.
+However, it could also be due to limitations with the data.
+Regardless, futher studies making use of longer term data across several countries are warranted to more conclusively understand the link between unemployment and feelings towards government.
 
@@
 
-# Conclusion
+# Appendix
+
+My replications of the first two tables in Bauer's paper are below.
+
+\input{./replication-table-1.tex}
+
+\input{./replication-table-2.tex}
+
+The actual tables created by Bauer are below. As you can see, there are discrepencies between my Table 2 and his.
+
+\input{./table-1.tex}
+
+\input{./table-2.tex}
 

### 2020-04-28 Dataverse/paper_and_analysis_bauer_2018_socius.Rmd
organzing my repo

---
title: |
  | Unemployment, Trust in Government
  | and Satisfaction with Democracy: 
  | An Empirical Investigation*^[ Acknowledgements: I thank the participants of the Swiss Political Science Conference 2016, the annual conference for the European Political Science Association 2015, Hanspeter Kriesi, Stefanie Reher, Jonathan Chapman, Florian Stöckel and anonymous reviewers for their helpful comments. I am also grateful to Giada Gianola for excellent research assistance. Reproduction files and data can be accessed under http://dx.doi.org/10.7910/DVN/DUMGLT. This study has been realized using data collected by the Swiss Household Panel (SHP), which is based at the Swiss Centre of Expertise in the Social Sciences FORS and financed by the Swiss National Science Foundation as well as data from the LISS (Longitudinal Internet Studies for the Social sciences) panel, administered by CentERdata (Tilburg University, The Netherlands). The publication of this article was funded by the "Mannheim Centre for European Social Research". Corresponding Author: mail@paulcbauer.eu, University Mannheim, Mannheim Centre for European Social Research (MZES), 68131  Mannheim Germany, http://www.paulcbauer.eu.]
author: 'Paul C. Bauer'
date: ''
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Evidence suggests that unemployment negatively affects various aspects of individuals' lives. We investigate whether unemployment changes individuals' political evaluations in the form of trust in government and satisfaction with democracy. While most research in this area operates on the macro level, we provide individual-level evidence. In doing so, we investigate the assumed causal link with panel data from Switzerland and the Netherlands. In addition, we study the impact on life satisfaction, a 'control outcome', known to be affected by unemployment. While there is strong evidence that changes in employment status do affect life satisfaction, effects on trust in government and satisfaction with democracy seem mostly absent or negligible in size. \vspace{.8cm}
bibliography: Paperpile.bib
output: 
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
    toc: no
    keep_tex: true
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
documentclass: article
geometry: margin=1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
---

\newcommand*{\secref}[1]{Section~\ref{#1}}

```{r setup, include = FALSE}
  library(knitr)
  set.seed(12345)

# RAW DATA AVAILABLE FROM 
  # Swiss Household Panel: http://forscenter.ch/en/our-surveys/swiss-household-panel/
  # LISS data: http://www.lissdata.nl

# Suggestion: Use the RMarkdown Document Outline in Rstudio to navigate this document.
# Important: As compared to the PDF generated by this .Rmd file, the published manuscript contains various corrections.

# SETUP:
  # R version 3.4.1 (2017-06-30) 
  # Platform: x86_64-w64-mingw32/x64 (64-bit) 
  # Running under: Windows 7 x64 (build 7601) Service Pack 1 
  #  
  # Matrix products: default 
  #  
  # locale: 
  # [1] LC_COLLATE=German_Germany.1252  LC_CTYPE=German_Germany.1252    LC_MONETARY=German_Germany.1252 
  # [4] LC_NUMERIC=C                    LC_TIME=German_Germany.1252     
  #  
  # attached base packages: 
  # [1] stats     graphics  grDevices utils     datasets  methods   base      
  #  
  # other attached packages: 
  # [1] Formula_1.2-1 stargazer_5.2 bindrcpp_0.2  haven_1.0.0   tidyr_0.6.3   stringr_1.2.0 dplyr_0.7.1   plyr_1.8.4    
  # [9] knitr_1.16    
  #  
  # loaded via a namespace (and not attached): 
  #  [1] Rcpp_0.12.14        bdsmatrix_1.3-2     lattice_0.20-35     zoo_1.8-0           assertthat_0.2.0    
  #  [6] rprojroot_1.2       digest_0.6.12       lmtest_0.9-35       R6_2.2.2            backports_1.1.0     
  # [11] acepack_1.4.1       labelled_1.0.0      evaluate_0.10.1     coda_0.19-1         ggplot2_2.2.1       
  # [16] miscTools_0.6-22    rlang_0.1.4         lazyeval_0.2.0      minqa_1.2.4         data.table_1.10.4-3 
  # [21] nloptr_1.0.4        rpart_4.1-11        Matrix_1.2-10       checkmate_1.8.3     rmarkdown_1.6       
  # [26] splines_3.4.1       lme4_1.1-13         readr_1.1.1         foreign_0.8-69      htmlwidgets_0.9     
  # [31] munsell_0.4.3       compiler_3.4.1      pkgconfig_2.0.1     base64enc_0.1-3     maxLik_1.3-4        
  # [36] htmltools_0.3.6     nnet_7.3-12         tibble_1.3.3        gridExtra_2.2.1     htmlTable_1.9       
  # [41] bookdown_0.5        Hmisc_4.0-3         MASS_7.3-47         grid_3.4.1          nlme_3.1-131        
  # [46] arm_1.9-3           gtable_0.2.0        magrittr_1.5        scales_0.5.0        stringi_1.1.5       
  # [51] latticeExtra_0.6-28 sandwich_2.3-4      RColorBrewer_1.1-2  tools_3.4.1         glue_1.1.1          
  # [56] hms_0.3             abind_1.4-5         survival_2.41-3     yaml_2.1.14         colorspace_1.3-2    
  # [61] cluster_2.0.6       bindr_0.1

  library(plyr)
  library(dplyr)
  library(stringr)
  library(tidyr)
  library(haven)
```

```{r shp-create-data, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Import and merge data
  shp <- read_dta("shp99_p_user.dta")
  shp <- full_join(shp, read_dta("shp00_p_user.dta"), by="idpers")

  # Identify variables across years by first letters
  relevant.variables <- c("idint", "idpers", "idhous04", "status", "p45", "y02",
                          "l34", "l60", "l61", "l70", "l71", "l80", "l81", "sex",
                          "age", "educat", "wyn", "l101", "l100", "r04","r05",
                          "civsta", "l16", "l01", "n39", "n40", "n41", "n42",
                          "n43", "n44", "n45", "n46", "l21", "i02", "wstat",
                          "p04","p02" ,"reg.1", "w153", "c44", "w12", "w04")

  # Merge and subset variables inbetween (speed!)
  used.vars <- NULL
  for (i in relevant.variables){used.vars <- c(used.vars, names(shp)[grepl(i, names(shp))])}
  shp <- shp[c(used.vars)]
  shp <- full_join(shp, read_dta("shp01_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp02_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp03_p_user.dta"), by="idpers")
  used.vars <- NULL
  for (i in relevant.variables){used.vars <- c(used.vars, names(shp)[grepl(i, names(shp))])}
  shp <- shp[c(used.vars)]
  shp <- full_join(shp, read_dta("shp04_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp05_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp06_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp07_p_user.dta"), by="idpers")
  used.vars <- NULL
  for (i in relevant.variables){used.vars <- c(used.vars, names(shp)[grepl(i, names(shp))])}
  shp <- shp[c(used.vars)]
  shp <- full_join(shp, read_dta("shp08_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp09_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp10_p_user.dta"), by="idpers")
  used.vars <- NULL
  for (i in relevant.variables){used.vars <- c(used.vars, names(shp)[grepl(i, names(shp))])}
  shp <- shp[c(used.vars)]
  shp <- full_join(shp, read_dta("shp11_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp12_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp13_p_user.dta"), by="idpers")
  shp <- full_join(shp, read_dta("shp_lj.dta"), by="idpers")
  used.vars <- NULL
  for (i in relevant.variables){used.vars <- c(used.vars, names(shp)[grepl(i, names(shp))])}
  data <- shp[c(used.vars)]
  rm(shp)

  data <- data[ , !duplicated(colnames(data))] # ATTENTION

#### Unit ID ####
    data <- rename(data, unit = idpers)

#### Interview Status #### Type of interviews completed: grid, proxy, personal; 0 = individual questionnaire
    data <- mutate(data, status.1999 = status99,
                         status.2000 = status00,
                         status.2001 = status01,
                         status.2002 = status02,
                         status.2003 = status03,
                         status.2004 = status04,
                         status.2005 = status05,
                         status.2006 = status06,
                         status.2007 = status07,
                         status.2008 = status08,
                         status.2009 = status09,
                         status.2010 = status10,
                         status.2011 = status11,                         
                         status.2012 = status12,
                         status.2013 = status13)
    data <- data %>% labelled::remove_labels() %>%
    mutate_at( .funs = funs(dplyr::recode(., 
                                          `0` = 1,
                                   .default = NA_real_)),
              .vars = vars(matches("status"))
    )

#### OUTCOME VAR ####

  # TRUST IN GOVERNMENT
    data <- mutate(data, trust_in_government.1999 = p99p04,
                         trust_in_government.2000 = p00p04,
                         trust_in_government.2001 = p01p04,
                         trust_in_government.2002 = p02p04,
                         trust_in_government.2003 = p03p04,
                         trust_in_government.2004 = p04p04,
                         trust_in_government.2005 = p05p04,
                         trust_in_government.2006 = p06p04,
                         trust_in_government.2007 = p07p04,
                         trust_in_government.2008 = p08p04,
                         trust_in_government.2009 = p09p04,
                         trust_in_government.2011 = p11p04)# GAP in 2010
    # RECODE
    vars <- names(dplyr::select(data, contains("trust_in_government")))
    for (i in vars){data[c(i)][data[c(i)]==-3 | data[c(i)]==-2 | data[c(i)]==-1] <- NA}
    #table(data$trust_in_government.2011, data$p11p04)

  # SATISFACTION WITH DEMOCRACY
        data <- mutate(data, satisfaction_with_democracy.1999 = p99p02,
                          satisfaction_with_democracy.2000 = p00p02,
                          satisfaction_with_democracy.2001 = p01p02, # GAP BEFORE
                          satisfaction_with_democracy.2002 = p02p02,
                          satisfaction_with_democracy.2003 = p03p02,
                          satisfaction_with_democracy.2004 = p04p02,
                          satisfaction_with_democracy.2005 = p05p02,
                          satisfaction_with_democracy.2006 = p06p02,
                          satisfaction_with_democracy.2007 = p07p02,
                          satisfaction_with_democracy.2008 = p08p02,
                          satisfaction_with_democracy.2009 = p09p02,
                          satisfaction_with_democracy.2011 = p11p02) # GAP IN 2010)#
    # RECODE
    vars <- names(dplyr::select(data, contains("satisfaction_with_democracy"))) 
    for (i in vars){data[c(i)][data[c(i)]==-3 | data[c(i)]==-2 | data[c(i)]==-1] <- NA}

  # SATISFACTION WITH LIFE
            data <- mutate(data, life_satisfaction.2000 = p00c44, # no 1999
                                 life_satisfaction.2001 = p01c44,
                                 life_satisfaction.2002 = p02c44,
                                 life_satisfaction.2003 = p03c44,
                                 life_satisfaction.2004 = p04c44,
                                 life_satisfaction.2005 = p05c44,
                                 life_satisfaction.2006 = p06c44,
                                 life_satisfaction.2007 = p07c44,
                                 life_satisfaction.2008 = p08c44,
                                 life_satisfaction.2009 = p09c44,
                                 life_satisfaction.2010 = p10c44,
                                 life_satisfaction.2011 = p11c44,
                                 life_satisfaction.2012 = p12c44,
                                 life_satisfaction.2013 = p13c44) # GAP IN 2010)#
    # RECODE
    vars <- names(dplyr::select(data, contains("life_satisfaction"))) 
    for (i in vars){data[c(i)][data[c(i)]==-3 | data[c(i)]==-2 | data[c(i)]==-1] <- NA}

#### TREATMENT VAR ####
  # UNEMPLOYMENT at t
    data <- mutate(data, 
                   unemployed.1999 = wstat99,
                   unemployed.2000 = wstat00,
                   unemployed.2001 = wstat01,
                   unemployed.2002 = wstat02,
                   unemployed.2003 = wstat03,
                   unemployed.2004 = wstat04,
                   unemployed.2005 = wstat05,
                   unemployed.2006 = wstat06,
                   unemployed.2007 = wstat07,
                   unemployed.2008 = wstat08,
                   unemployed.2009 = wstat09,
                   unemployed.2010 = wstat10,
                   unemployed.2011 = wstat11,
                   unemployed.2012 = wstat12,
                   unemployed.2013 = wstat13) # GA

    # RECODE
    data <- data %>% labelled::remove_labels() %>%
    mutate_at( .funs = funs(recode(., # `3` = 0, # not in labor force
                                      `1` = 0, #actively occupied
                                      `2` = 1, #unemployed
                                   .default = NA_real_)),
              .vars = vars(matches("unemployed"))
    )
    #table(data$unemployed.2004, data$wstat04)

  # P04W04: In the last four weeks, have you been looking for a job?
  #  -8 other error; -7 filter error; -3 inapplicable; -2 no answer; -1 does not know; 1 yes; 2 no
        data <- mutate(data, 
                   lookforjob.1999 = p99w04,
                   lookforjob.2000 = p00w04,
                   lookforjob.2001 = p01w04,
                   lookforjob.2002 = p02w04,
                   lookforjob.2003 = p03w04,
                   lookforjob.2004 = p04w04,
                   lookforjob.2005 = p05w04,
                   lookforjob.2006 = p06w04,
                   lookforjob.2007 = p07w04,
                   lookforjob.2008 = p08w04,
                   lookforjob.2009 = p09w04,
                   lookforjob.2010 = p10w04,
                   lookforjob.2011 = p11w04,
                   lookforjob.2012 = p12w04,
                   lookforjob.2013 = p13w04)

    # RECODE
    library(dplyr)
    data <- data %>% labelled::remove_labels() %>%
    mutate_at( .funs = funs(recode(., `1` = 1, #yes
                                      `2` = 0, #no
                                   .default = NA_real_)),
              .vars = vars(matches("lookforjob"))
    )
    #table(data$lookforjob.1999, data$p99w04)
    #table(data$lookforjob.2005, data$p05w04)

# Check whether there are any unemployed people who are not lookign for a job!    
  table(data$lookforjob.1999, data$unemployed.1999)    
  table(data$lookforjob.2001, data$unemployed.2001)   
  table(data$lookforjob.2002, data$unemployed.2002)   
  table(data$lookforjob.2003, data$unemployed.2003)   
  table(data$lookforjob.2004, data$unemployed.2004)   
  table(data$lookforjob.2005, data$unemployed.2005)   
  table(data$lookforjob.2006, data$unemployed.2006)   
  table(data$lookforjob.2007, data$unemployed.2007)   
  table(data$lookforjob.2008, data$unemployed.2008)   
  table(data$lookforjob.2009, data$unemployed.2009)   
  table(data$lookforjob.2010, data$unemployed.2010)   
  table(data$lookforjob.2011, data$unemployed.2011)   
  table(data$lookforjob.2012, data$unemployed.2012)   
  table(data$lookforjob.2013, data$unemployed.2013)   
  # There are people who are not in the labour force but looking for a job (e.g. students, pupils etc.)
  # There are no people that are actively occupied and looking for a job (hence the 0 category)

#### CONTROL VARs ####
  years <- c("1999","2000","2001","2002", "2003", "2004", "2005", "2006", "2007", "2008" , "2009", "2010", "2011", "2012", "2013")

# AGE
  for (i in years){
    y <- paste("age.", i, sep="")
    z <- paste("age", substr(i, 3, 4), sep="")
    data[c(y)] <- data[z]
    data[c(y)][data[c(y)]<=-1] <- NA
  }
  # table(data$age.2002, data$age02)

# EDUCATION
  for (i in years){
    y <- paste("education.", i, sep="")
    z <- paste("educat", substr(i, 3, 4), sep="")
    data[c(y)] <- data[z]
    data[c(y)][data[c(y)]<=-1] <- NA
  }
  # table(data$education.2007, data$educat07)

# MEMBER: 1 IF MEMBER IN AT LEAST ONE ASSOCIATION (P04N39-P04N46)
  # NO DATA AFTER 2009
  for (i in years[1:11]){
    data[c(paste("member.", i, sep=""))] <- 0
    data[c(paste("member.", i, sep=""))][data[c(paste("p", substr(i, 3, 4), "n39", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n40", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n41", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n42", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n43", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n44", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n45", sep=""))]==1 |
                                         data[c(paste("p", substr(i, 3, 4), "n46", sep=""))]==1] <- 1

  }
  # table(data$member.2007)

# KEEP RELEVANT VARIABLES
  data <- dplyr::select(data, matches('unit|status\\.|trust_in_government|satisfaction_with_democracy|life_satisfaction|unemployed\\.[0-9]{4}|unemployed\\.[0-9]{2}\\.[0-9]{2}|age\\.|education|member'))

# CHECK DATA TYPES OF RELEVANT VARIABLES
  str(data)

# CREATE LONGFORMAT ####
  data.wide <- dplyr::select(data, matches('unit|trust_in_government|satisfaction_with_democracy|life_satisfaction|unemployed\\.[0-9]{4}|age\\.|education|member'))
  # Convert to long format (row = unit*time*variable)
  data.wide$unit <- factor(data.wide$unit) # convert id variable to factor
  data.long <- data.wide %>% gather(key = key, value = value, -unit)
  data.long <- data.long %>%
  separate(col = key, into = c("variable", "time"), sep = "\\.")
  data.long <-  data.long %>% spread(key = variable, value = value) %>% 
    mutate_all(funs(as.numeric)) %>% arrange(unit, time) 
  data.long <- filter(data.long, age>=18, age<=65)
  nrow(data.long) # check length: length(unique(data.long$time))*length(unique(data$unit))
  # Make it balanced make.pbalanced()

# NAME DATA OBJECTS  
  data.shp <- data
  data.long.shp <- data.long
  save(data.shp, file = "./data-shp.RData") 
  save(data.long.shp, file = "./data-long-shp.RData")

  rm(list=ls())

```

```{r liss-create-data, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# gender
    data <- read_dta("Gender.dta")
    d08 <- filter(data, wave==200812) %>% 
      mutate(gender.08 = geslacht) %>% dplyr::select(nomem_encr, gender.08)
    d09 <- filter(data, wave==200912) %>% 
      mutate(gender.09 = geslacht) %>% dplyr::select(nomem_encr, gender.09)
    d10 <- filter(data, wave==201012) %>% 
      mutate(gender.10 = geslacht) %>% dplyr::select(nomem_encr, gender.10)
    d11 <- filter(data, wave==201112) %>% 
      mutate(gender.11 = geslacht) %>% dplyr::select(nomem_encr, gender.11)
    d12 <- filter(data, wave==201212) %>% 
      mutate(gender.12 = geslacht) %>% dplyr::select(nomem_encr, gender.12)
    d13 <- filter(data, wave==201312) %>% 
      mutate(gender.13 = geslacht) %>% dplyr::select(nomem_encr, gender.13)
    d14 <- filter(data, wave==201412) %>% 
      mutate(gender.14 = geslacht) %>% dplyr::select(nomem_encr, gender.14)

    data <- full_join(d08, d09, by="nomem_encr")
    data <- full_join(data, d10, by="nomem_encr")
    data <- full_join(data, d11, by="nomem_encr")
    data <- full_join(data, d12, by="nomem_encr")
    data <- full_join(data, d13, by="nomem_encr")
    data <- full_join(data, d14, by="nomem_encr")
    rm(d08, d09, d10, d11, d12, d13, d14)

    liss <- data

# age  
  data <- read_dta("Age.dta")
  d08 <- filter(data, wave==200812) %>% mutate(age.08 = leeftijd) %>% dplyr::select(nomem_encr, age.08)
  d09 <- filter(data, wave==200912) %>% mutate(age.09 = leeftijd) %>% dplyr::select(nomem_encr, age.09)
  d10 <- filter(data, wave==201012) %>% mutate(age.10 = leeftijd) %>% dplyr::select(nomem_encr, age.10)
  d11 <- filter(data, wave==201112) %>% mutate(age.11 = leeftijd) %>% dplyr::select(nomem_encr, age.11)
  d12 <- filter(data, wave==201212) %>% mutate(age.12 = leeftijd) %>% dplyr::select(nomem_encr, age.12)
  d13 <- filter(data, wave==201312) %>% mutate(age.13 = leeftijd) %>% dplyr::select(nomem_encr, age.13)
  d14 <- filter(data, wave==201412) %>% mutate(age.14 = leeftijd) %>% dplyr::select(nomem_encr, age.14)

  data <- full_join(d08, d09, by="nomem_encr")
  data <- full_join(data, d10, by="nomem_encr")
  data <- full_join(data, d11, by="nomem_encr")
  data <- full_join(data, d12, by="nomem_encr")
  data <- full_join(data, d13, by="nomem_encr")
  data <- full_join(data, d14, by="nomem_encr")
  rm(d08, d09, d10, d11, d12, d13, d14)

  liss <- full_join(liss, data, by="nomem_encr")

# education
  data <- read_dta("Education.dta")
  d08 <- filter(data, wave==200812) %>% mutate(education.08 = oplmet) %>% dplyr::select(nomem_encr, education.08)
  d09 <- filter(data, wave==200912) %>% mutate(education.09 = oplmet) %>% dplyr::select(nomem_encr, education.09)
  d10 <- filter(data, wave==201012) %>% mutate(education.10 = oplmet) %>% dplyr::select(nomem_encr, education.10)
  d11 <- filter(data, wave==201112) %>% mutate(education.11 = oplmet) %>% dplyr::select(nomem_encr, education.11)
  d12 <- filter(data, wave==201212) %>% mutate(education.12 = oplmet) %>% dplyr::select(nomem_encr, education.12)
  d13 <- filter(data, wave==201312) %>% mutate(education.13 = oplmet) %>% dplyr::select(nomem_encr, education.13)
  d14 <- filter(data, wave==201412) %>% mutate(education.14 = oplmet) %>% dplyr::select(nomem_encr, education.14)

  data <- full_join(d08, d09, by="nomem_encr")
  data <- full_join(data, d10, by="nomem_encr")
  data <- full_join(data, d11, by="nomem_encr")
  data <- full_join(data, d12, by="nomem_encr")
  data <- full_join(data, d13, by="nomem_encr")
  data <- full_join(data, d14, by="nomem_encr")
  rm(d08, d09, d10, d11, d12, d13, d14)

  liss <- full_join(liss, data, by="nomem_encr")

# life satisfaction
  data <- read_dta("Life-satisfaction.dta")
  data <- transmute(data, nomem_encr = nomem_encr, 
                 life_satisfaction.08 = cp08a011,
                 life_satisfaction.09 = cp09b011,
                 life_satisfaction.10 = cp10c011,
                 life_satisfaction.11 = cp11d011,
                 life_satisfaction.12 = cp12e011,
                 life_satisfaction.13 = cp13f011,
                 life_satisfaction.14 = cp14g011) 
  liss <- full_join(liss, data, by="nomem_encr")

# satisfaction with democracy
  data <- read_dta("Satisfaction-with-democracy.dta")
  data <- transmute(data, nomem_encr = nomem_encr, 
                 satisfaction_with_democracy.08 = cv08a044,
                 satisfaction_with_democracy.09 = cv09b044,
                 satisfaction_with_democracy.10 = cv10c044,
                 satisfaction_with_democracy.11 = cv11d044,
                 satisfaction_with_democracy.12 = cv12e044,
                 satisfaction_with_democracy.13 = cv13f044,
                 satisfaction_with_democracy.14 = cv14g044) 
  liss <- full_join(liss, data, by="nomem_encr")

# trust in government
  data <- read_dta("Trust-in-government.dta")
  data <- transmute(data, nomem_encr = nomem_encr, 
                 trust_in_government.08 = cv08a013,
                 trust_in_government.09 = cv09b013,
                 trust_in_government.10 = cv10c013,
                 trust_in_government.11 = cv11d013,
                 trust_in_government.12 = cv12e013,
                 trust_in_government.13 = cv13f013,
                 trust_in_government.14 = cv14g013) 
  liss <- full_join(liss, data, by="nomem_encr")

# perform paid work
  data <- read_dta("I-perform-paid-work.dta")
  data <- transmute(data, nomem_encr = nomem_encr, 
                 performpaidwork.08 = cw08a088,
                 performpaidwork.09 = cw09b088,
                 performpaidwork.10 = cw10c088,
                 performpaidwork.11 = cw11d088,
                 performpaidwork.12 = cw12e088,
                 performpaidwork.13 = cw13f088,
                 performpaidwork.14 = cw14g088) 
  liss <- full_join(liss, data, by="nomem_encr")

# not working but in past
  data <- read_dta("I-am-looking-for-work-following-the-loss.dta")
  data <- transmute(data, nomem_encr = nomem_encr, 
                 lookingforwork.08 = cw08a091,
                 lookingforwork.09 = cw09b091,
                 lookingforwork.10 = cw10c091,
                 lookingforwork.11 = cw11d091,
                 lookingforwork.12 = cw12e091,
                 lookingforwork.13 = cw13f091,
                 lookingforwork.14 = cw14g091) 
  liss <- full_join(liss, data, by="nomem_encr")

# membership
  data <- read_dta("Membership-in-organisations.dta")
  liss <- full_join(liss, data, by="nomem_encr")

  # Add household identifer! - nohouse_encr
  data <- read_dta("Household-identifier.dta")
  data <- data[!duplicated(data$nomem_encr), ]
  data <- arrange(data, wave)
  liss <- full_join(liss, data, by="nomem_encr")

  data <- liss
  rm(liss)

#### OUTCOME VAR ####

    #GENERATE CHANGE/DIFFERENCE IN
    vars <- names(dplyr::select(data, contains("trust_in_government")))
    for (i in vars){data[c(i)][data[c(i)]==999] <- NA}

    #SATISFACTION WITH DEMOCRACY
    vars <- names(dplyr::select(data, contains("satisfaction_with_democracy")))
    for (i in vars){data[c(i)][data[c(i)]==999] <- NA}

    #LIFE SATISFACTION
    vars <- names(dplyr::select(data, contains("life_satisfaction")))
    for (i in vars){data[c(i)][data[c(i)]==999] <- NA}

#### TREATMENT VAR ####

    # Please indicate which of the following statements apply to your situation. Try to be as thorough as you can. Checkmark at least one square; more than one answer is permitted. 
    # cw10c088 I perform paid work (even if is it just for one or several hours per week or for a brief period)
    # cw10c091 I am looking for work following the loss of my previous job
    data$unemployed.08 <- NA
    data$unemployed.09 <- NA
    data$unemployed.10 <- NA
    data$unemployed.11 <- NA
    data$unemployed.12 <- NA
    data$unemployed.13 <- NA
    data$unemployed.14 <- NA
    data$unemployed.08[data$performpaidwork.08==1] <- 0
    data$unemployed.09[data$performpaidwork.09==1] <- 0
    data$unemployed.10[data$performpaidwork.10==1] <- 0
    data$unemployed.11[data$performpaidwork.11==1] <- 0
    data$unemployed.12[data$performpaidwork.12==1] <- 0
    data$unemployed.13[data$performpaidwork.13==1] <- 0
    data$unemployed.14[data$performpaidwork.14==1] <- 0
    data$unemployed.08[data$lookingforwork.08==1] <- 1
    data$unemployed.09[data$lookingforwork.09==1] <- 1
    data$unemployed.10[data$lookingforwork.10==1] <- 1
    data$unemployed.11[data$lookingforwork.11==1] <- 1
    data$unemployed.12[data$lookingforwork.12==1] <- 1
    data$unemployed.13[data$lookingforwork.13==1] <- 1
    data$unemployed.14[data$lookingforwork.14==1] <- 1

    # if sum(cw10c088 through cw10c102)>1 This only lists the labor market options that were marked 'yes' in cw10c088 through
    # cw10c102. cw10c104
    # You gave several answers to the previous question. Please indicate here which of these answers best describes your situation? 
    # Above there might be some inconsistencies

#### CONTROL VARs ####

  # GENDER -> 1 = Male, 0 = Female
    vars <- names(dplyr::select(data, contains("gender.")))
    for (i in vars){data[c(i)][data[c(i)]==2] <- 0}
    names(data) <- str_replace_all(names(data), "gender", "male")

  # EDUCATION -
    vars <- names(dplyr::select(data, contains("education.")))
    for (i in vars){
    data[c(i)][data[c(i)]==7] <- NA
    data[c(i)][data[c(i)]==8] <- 0
    data[c(i)][data[c(i)]==9] <- 0
      }

    #MEMBER IN AT LEAST ONE ASSOCIATION -> 1=Yes, 0=No
    data$member.08 <- 0
    data$member.08[data$cs08a006==1 | data$cs08a011==1 | data$cs08a016==1 |
                      data$cs08a021==1 | data$cs08a026==1 | #data$cs08a031==1 |
                          data$cs08a036==1 | data$cs08a041 ==1| data$cs08a046==1 |
                      data$cs08a051==1 | data$cs08a056==1 | data$cs08a061==1] <- 1
    data$member.09 <- 0
    data$member.09[data$cs09b006==1 | data$cs09b011==1 | data$cs09b016==1 |
                      data$cs09b021==1 | data$cs09b026==1 | #data$cs09b031==1 |
                        data$cs09b036==1 | data$cs09b041 ==1| data$cs09b046==1 |
                      data$cs09b051==1 | data$cs09b056==1 | data$cs09b061==1] <- 1
    data$member.10 <- 0
    data$member.10[data$cs10c006==1 | data$cs10c011==1 | data$cs10c016==1 |
                      data$cs10c021==1 | data$cs10c026==1 | #data$cs10c031==1 |
                          data$cs10c036==1 | data$cs10c041 ==1| data$cs10c046==1 |
                      data$cs10c051==1 | data$cs10c056==1 | data$cs10c061==1] <- 1
    data$member.11 <- 0
    data$member.11[data$cs11d006==1 | data$cs11d011==1 | data$cs11d016==1 |
                      data$cs11d021==1 | data$cs11d026==1 | #data$cs11d031==1 |
                          data$cs11d036==1 | data$cs11d041 ==1| data$cs11d046==1 |
                      data$cs11d051==1 | data$cs11d056==1 | data$cs11d061==1] <- 1
    data$member.12 <- 0
    data$member.12[data$cs12e006==1 | data$cs12e011==1 | data$cs12e016==1 |
                      data$cs12e021==1 | data$cs12e026==1 | #data$cs12e031==1 |
                          data$cs12e036==1 | data$cs12e041 ==1| data$cs12e046==1 |
                      data$cs12e051==1 | data$cs12e056==1 | data$cs12e061==1] <- 1
    data$member.13 <- 0
    data$member.13[data$cs13f006==1 | data$cs13f011==1 | data$cs13f016==1 |
                      data$cs13f021==1 | data$cs13f026==1 | #data$cs13f031==1 |
                          data$cs13f036==1 | data$cs13f041 ==1| data$cs13f046==1 |
                      data$cs13f051==1 | data$cs13f056==1 | data$cs13f061==1] <- 1
    data$member.14 <- 0
    data$member.14[data$cs14g006==1 | data$cs14g011==1 | data$cs14g016==1 |
                      data$cs14g021==1 | data$cs14g026==1 | #data$cs14g031==1 |
                          data$cs14g036==1 | data$cs14g041 ==1| data$cs14g046==1 |
                      data$cs14g051==1 | data$cs14g056==1 | data$cs14g061==1] <- 1
    names(data) <- gsub("(\\.)([0-9][0-9])", "\\120\\2", names(data))

    # rename variables
    data <- rename(data, unit = nomem_encr)

    # keep relevant variables
    data <- dplyr::select(data, 
                          matches('unit|male|age|trust_in_government|satisfaction_with_democracy|life_satisfaction|unemployed|education|member'))

    # check object types
      str(data)

    # replace NaN with NA
      data[is.na(data)] <- NA

    # CREATE LONGFORMAT ####
      data.wide <- data
      # Convert to long format (row = unit*time*variable)
      # data.wide$unit <- factor(data.wide$unit) # convert id variable to factor
      data.long <- data.wide %>% gather(key = key, value = value, -unit)
      data.long <- data.long %>%
      separate(col = key, into = c("variable", "time"), sep = "\\.")
      data.long <-  data.long %>% spread(key = variable, value = value) %>% 
        mutate_all(funs(as.numeric)) %>% arrange(unit, time) 
      data.long <- filter(data.long, age>=18, age<=65) %>% dplyr::select(-male)
      nrow(data.long) # CHECK: length(unique(data.long$time))*length(unique(data$unit))

    # name data objects
      data.liss <- data
      data.long.liss <- data.long
      # data.wide.liss <- data.wide

      save(data.liss, file = "./data-liss.RData") 
      save(data.long.liss, file = "./data-long-liss.RData")

      rm(list=ls())

```

```{r table-1, message=FALSE, warning=FALSE, include=FALSE}

#### START: REPRODUCTION W/O RAW DATA HERE ####

      load(file = "./data-long-shp.RData") 
      load(file = "./data-long-liss.RData") 
      x1 <- group_by(data.long.shp, time) %>% summarise_all(funs(sum(.==0, na.rm = TRUE))) %>% pull(unemployed)
      x2 <- group_by(data.long.shp, time) %>% summarise_all(funs(sum(.==1, na.rm = TRUE))) %>% pull(unemployed)
      names(x1) <- 1999:2013
      names(x2) <- 1999:2013

      x3 <- group_by(data.long.liss, time) %>% summarise_all(funs(sum(.==0, na.rm = TRUE))) %>% pull(unemployed)
      x4 <- group_by(data.long.liss, time) %>% summarise_all(funs(sum(.==1, na.rm = TRUE))) %>% pull(unemployed)
      names(x3) <- 2008:2014
      names(x4) <- 2008:2014
      samples <- data.frame(bind_rows(x1,x2,x3,x4))
      row.names(samples) <- c("SHP: Employed", "SHP: Unemployed", "LISS: Employed", "LISS: Unemployed")
      names(samples) <- 1999:2014
      stargazer::stargazer(samples, summary = FALSE, 
                out = "table-1.tex",
                font.size = "tiny",
                label = "table-1",
                table.placement="!ht",
                column.sep.width = ".1pt", 
                title = "Unemployment across years",
                digit.separator="")

      rm(list=ls())

```

```{r shp-analyze-data, message=FALSE, warning=FALSE, include=FALSE}
  library(dplyr)
  library(stargazer)

  load(file = "./data-long-shp.RData")  
  data.long <- data.long.shp
  rm(data.long.shp)

# Table 6 & 7: SUMMARY STATISTICS ####
  summary.stats <- 
  bind_cols(
  data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(sum(!is.na(.))))  %>%
    gather(key = "variable", 
           value = "n",
           -time),

  data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(mean(., na.rm = TRUE)))  %>%
    gather(key = "variable2", 
           value = "mean",
           -time),

   data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(sd(., na.rm = TRUE)))  %>%
    gather(key = "variable3", 
           value = "sd",
           -time),

    data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
   summarise_all(funs(min(., na.rm = TRUE)))  %>%
    gather(key = "variable4", 
           value = "min",
           -time),

    data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
   summarise_all(funs(max(., na.rm = TRUE)))  %>%
    gather(key = "variable5", 
           value = "max",
           -time))  %>% dplyr::select(-variable2, -variable3, -variable4, -variable5,
                               -time2, -time3, -time4) %>%
    filter(n!=0) %>% unite(variable, time, col = "variable")

    summary.stats[,4:5] <- round(summary.stats[,4:5],2)

    summary.stats$variable <- (str_replace_all(summary.stats$variable, "_|\\.", " "))

    #Hmisc::capitalize

    names(summary.stats) <- c("Variable", "N", "Time", "Mean", "SD", "Min", "Max")
  stargazer(summary.stats[1:55,], summary = FALSE, out="./table-6.tex", type="latex", 
              label = "table-6", font.size="scriptsize", table.placement="!ht", column.sep.width = ".2pt" , title = "SHP Switzerland: summary statistics", digits = 2,
                rownames = FALSE)

    stargazer(summary.stats[56:94,], summary = FALSE, out="./table-7.tex", type="latex", 
              label = "table-7", font.size="scriptsize", table.placement="!ht", column.sep.width = ".2pt" , title = "SHP Switzerland: summary statistics continued", digits = 2,
                rownames = FALSE)

    rm(summary.stats)

      library(plm)

# M1-M6: POOLING ####

      fit.pooling.trust_in_government <- plm(trust_in_government ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.trust_in_government)

      fit.pooling.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.satisfaction_with_democracy)

      fit.pooling.life_satisfaction <- plm(life_satisfaction ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.life_satisfaction)

      fit.pooling.control.trust_in_government <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.trust_in_government)

      fit.pooling.control.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.satisfaction_with_democracy)

      fit.pooling.control.life_satisfaction <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.life_satisfaction)

# M13-M18: FIXED EFFECTS/WITHIN ####

      fit.fe.trust_in_government <- plm(trust_in_government ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.trust_in_government)

      fit.fe.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.satisfaction_with_democracy)

      fit.fe.life_satisfaction <- plm(life_satisfaction ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.life_satisfaction)

      fit.fe.control.trust_in_government <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.trust_in_government)

      fit.fe.control.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.satisfaction_with_democracy)

      fit.fe.control.life_satisfaction <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.life_satisfaction)

  detach("package:plm", unload=TRUE)

  library(wfe)

# M25-M30: WEIGHTED LINEAR: FIXED EFFECTS ####

#### trust_in_government ###
  fit.wfe_fe.trust_in_government <- wfe(trust_in_government ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.trust_in_government)

  fit.wfe_fe.control.trust_in_government <- wfe(trust_in_government ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.trust_in_government)

#### satisfaction_with_democracy ###
  fit.wfe_fe.satisfaction_with_democracy <- wfe(satisfaction_with_democracy ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.satisfaction_with_democracy)

  fit.wfe_fe.control.satisfaction_with_democracy <- wfe(satisfaction_with_democracy ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.satisfaction_with_democracy)

#### life_satisfaction ###
  fit.wfe_fe.life_satisfaction <- wfe(life_satisfaction ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.life_satisfaction)

  fit.wfe_fe.control.life_satisfaction <- wfe(life_satisfaction ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.life_satisfaction)

  rm(data.long)

# SHP: GENERATE MODEL OBJECTS ####  
      objects <- c("fit.pooling.trust_in_government", "fit.pooling.control.trust_in_government", 
                   "fit.pooling.satisfaction_with_democracy", "fit.pooling.control.satisfaction_with_democracy",
                   "fit.pooling.life_satisfaction", "fit.pooling.control.life_satisfaction", "fit.fe.trust_in_government",
                   "fit.fe.control.trust_in_government", "fit.fe.satisfaction_with_democracy",
                   "fit.fe.control.satisfaction_with_democracy", "fit.fe.life_satisfaction", "fit.fe.control.life_satisfaction",
                   "fit.wfe_fe.trust_in_government", "fit.wfe_fe.control.trust_in_government", "fit.wfe_fe.satisfaction_with_democracy",
                   "fit.wfe_fe.control.satisfaction_with_democracy", "fit.wfe_fe.life_satisfaction",
                   "fit.wfe_fe.control.life_satisfaction") 
      for(i in objects){assign(paste0("shp.", i), get(i))} # store objects with new name
      rm(list = objects)
      rm(i, objects) # rm(i, names, objects, x, z)

#### SHP: DATA FOR PLOT ####
  names <- c("shp.fit.pooling.trust_in_government", "shp.fit.pooling.control.trust_in_government", "shp.fit.pooling.satisfaction_with_democracy", "shp.fit.pooling.control.satisfaction_with_democracy", "shp.fit.pooling.life_satisfaction", "shp.fit.pooling.control.life_satisfaction", "shp.fit.fe.trust_in_government", "shp.fit.fe.control.trust_in_government", "shp.fit.fe.satisfaction_with_democracy", "shp.fit.fe.control.satisfaction_with_democracy", "shp.fit.fe.life_satisfaction", "shp.fit.fe.control.life_satisfaction", "shp.fit.wfe_fe.trust_in_government", "shp.fit.wfe_fe.control.trust_in_government", "shp.fit.wfe_fe.satisfaction_with_democracy", "shp.fit.wfe_fe.control.satisfaction_with_democracy", "shp.fit.wfe_fe.life_satisfaction", "shp.fit.wfe_fe.control.life_satisfaction")
  plot.data.shp <- data.frame(coef = rep(NA, 18), se =  rep(NA, 18), t =  rep(NA, 18), p =  rep(NA, 18))
  row.names(plot.data.shp) <- names
  i <- 1
  for(z in list(shp.fit.pooling.trust_in_government, shp.fit.pooling.control.trust_in_government, shp.fit.pooling.satisfaction_with_democracy, shp.fit.pooling.control.satisfaction_with_democracy, shp.fit.pooling.life_satisfaction, shp.fit.pooling.control.life_satisfaction, shp.fit.fe.trust_in_government,  shp.fit.fe.control.trust_in_government, shp.fit.fe.satisfaction_with_democracy, shp.fit.fe.control.satisfaction_with_democracy, shp.fit.fe.life_satisfaction, shp.fit.fe.control.life_satisfaction, shp.fit.wfe_fe.trust_in_government, shp.fit.wfe_fe.control.trust_in_government, shp.fit.wfe_fe.satisfaction_with_democracy, shp.fit.wfe_fe.control.satisfaction_with_democracy, shp.fit.wfe_fe.life_satisfaction, shp.fit.wfe_fe.control.life_satisfaction)){
    # print(coef(summary(fit))[1,1])

    # print(deparse(substitute(z)))
    x <- coef(summary(z))["unemployed",]
    plot.data.shp[i,"coef"] <- x[1]
    plot.data.shp[i,"se"] <- x[2]
    plot.data.shp[i,"t"] <- x[3]
    plot.data.shp[i,"p"] <- x[4]
    i <- i + 1
  }

```

```{r liss-analyze-data, message=FALSE, warning=FALSE, include=FALSE}
  load(file = "./data-long-liss.RData")  
  data.long <- data.long.liss
  rm(data.long.liss)

# Table 8: SUMMARY STATISTICS ####
  summary.stats <- 
  bind_cols(
  data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(sum(!is.na(.))))  %>%
    gather(key = "variable", 
           value = "n",
           -time),

  data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(mean(., na.rm = TRUE)))  %>%
    gather(key = "variable2", 
           value = "mean",
           -time),

   data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
    summarise_all(funs(sd(., na.rm = TRUE)))  %>%
    gather(key = "variable3", 
           value = "sd",
           -time),

    data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
   summarise_all(funs(min(., na.rm = TRUE)))  %>%
    gather(key = "variable4", 
           value = "min",
           -time),

    data.long %>% dplyr::select(-unit) %>%
    group_by(time) %>%
   summarise_all(funs(max(., na.rm = TRUE)))  %>%
    gather(key = "variable5", 
           value = "max",
           -time))  %>% dplyr::select(-variable2, -variable3, -variable4, -variable5,
                               -time2, -time3, -time4) %>%
    filter(n!=0) %>% unite(variable, time, col = "variable")

    summary.stats[,4:5] <- round(summary.stats[,4:5],2)

    summary.stats$variable <- (str_replace_all(summary.stats$variable, "_|\\.", " "))

    # Hmisc::capitalize

    names(summary.stats) <- c("Variable", "N", "Time", "Mean", "SD", "Min", "Max")  
    stargazer::stargazer(summary.stats, summary = FALSE, out="./table-8.tex", type="latex",
                label = "table-8", font.size="scriptsize", table.placement="!ht",
                column.sep.width = ".2pt", title = "LISS Netherlands: summary statistics", digits = 2,
                rownames = FALSE)
    rm(summary.stats)

      library(plm)

# M7-M12: POOLING ####

      fit.pooling.trust_in_government <- plm(trust_in_government ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.trust_in_government)

      fit.pooling.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.satisfaction_with_democracy)

      fit.pooling.life_satisfaction <- plm(life_satisfaction ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.life_satisfaction)

      fit.pooling.control.trust_in_government <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.trust_in_government)

      fit.pooling.control.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.satisfaction_with_democracy)

      fit.pooling.control.life_satisfaction <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "pooling")
      summary(fit.pooling.control.life_satisfaction)

# M19-M24: FIXED EFFECTS/WITHIN ####

      fit.fe.trust_in_government <- plm(trust_in_government ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.trust_in_government)

      fit.fe.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.satisfaction_with_democracy)

      fit.fe.life_satisfaction <- plm(life_satisfaction ~ unemployed, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.life_satisfaction)

      fit.fe.control.trust_in_government <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.trust_in_government)

      fit.fe.control.satisfaction_with_democracy <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.satisfaction_with_democracy)

      fit.fe.control.life_satisfaction <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = data.long,
                        index = c("unit", "time"),
                        model = "within")
      summary(fit.fe.control.life_satisfaction)

      detach("package:plm", unload=TRUE)

  library(wfe)

# M31-M36: WEIGHTED LINEAR: FIXED EFFECTS ####

#### trust_in_government ###
  fit.wfe_fe.trust_in_government <- wfe(trust_in_government ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.trust_in_government)

  fit.wfe_fe.control.trust_in_government <- wfe(trust_in_government ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.trust_in_government)

#### satisfaction_with_democracy ###
  fit.wfe_fe.satisfaction_with_democracy <- wfe(satisfaction_with_democracy ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.satisfaction_with_democracy)

  fit.wfe_fe.control.satisfaction_with_democracy <- wfe(satisfaction_with_democracy ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.satisfaction_with_democracy)

#### life_satisfaction ###
  fit.wfe_fe.life_satisfaction <- wfe(life_satisfaction ~ unemployed, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.life_satisfaction)

  fit.wfe_fe.control.life_satisfaction <- wfe(life_satisfaction ~ unemployed + age + education  + member, data = data.long, treat = "unemployed",
               unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)
  summary(fit.wfe_fe.control.life_satisfaction)

  detach("package:wfe", unload=TRUE)

  rm(data.long)

# LISS: GENERATE MODEL OBJECTS ####
      objects <- c("fit.pooling.trust_in_government", "fit.pooling.control.trust_in_government", 
                   "fit.pooling.satisfaction_with_democracy", "fit.pooling.control.satisfaction_with_democracy",
                   "fit.pooling.life_satisfaction", "fit.pooling.control.life_satisfaction", 
                   "fit.fe.trust_in_government", "fit.fe.control.trust_in_government", "fit.fe.satisfaction_with_democracy",
                   "fit.fe.control.satisfaction_with_democracy", "fit.fe.life_satisfaction", 
                   "fit.fe.control.life_satisfaction", "fit.wfe_fe.trust_in_government", 
                   "fit.wfe_fe.control.trust_in_government", "fit.wfe_fe.satisfaction_with_democracy",
                   "fit.wfe_fe.control.satisfaction_with_democracy", "fit.wfe_fe.life_satisfaction", "fit.wfe_fe.control.life_satisfaction") 
      for(i in objects){assign(paste0("liss.", i), get(i))} 
      rm(list = objects)
      rm(i, names, objects, x, z)

#### LISS: DATA FOR PLOT ####
  names <- c("liss.fit.pooling.trust_in_government", "liss.fit.pooling.control.trust_in_government", "liss.fit.pooling.satisfaction_with_democracy", "liss.fit.pooling.control.satisfaction_with_democracy", "liss.fit.pooling.life_satisfaction", "liss.fit.pooling.control.life_satisfaction", "liss.fit.fe.trust_in_government", 
             "liss.fit.fe.control.trust_in_government", "liss.fit.fe.satisfaction_with_democracy", "liss.fit.fe.control.satisfaction_with_democracy", "liss.fit.fe.life_satisfaction", "liss.fit.fe.control.life_satisfaction", "liss.fit.wfe_fe.trust_in_government", "liss.fit.wfe_fe.control.trust_in_government", "liss.fit.wfe_fe.satisfaction_with_democracy", "liss.fit.wfe_fe.control.satisfaction_with_democracy", "liss.fit.wfe_fe.life_satisfaction", "liss.fit.wfe_fe.control.life_satisfaction")
  plot.data.liss <- data.frame(coef = rep(NA, 18), se =  rep(NA, 18), t =  rep(NA, 18), p =  rep(NA, 18))
  row.names(plot.data.liss) <- names
  i <- 1
  for(z in list(liss.fit.pooling.trust_in_government, liss.fit.pooling.control.trust_in_government, 
                liss.fit.pooling.satisfaction_with_democracy, liss.fit.pooling.control.satisfaction_with_democracy, 
                liss.fit.pooling.life_satisfaction, liss.fit.pooling.control.life_satisfaction, liss.fit.fe.trust_in_government,
                liss.fit.fe.control.trust_in_government, liss.fit.fe.satisfaction_with_democracy, 
                liss.fit.fe.control.satisfaction_with_democracy, liss.fit.fe.life_satisfaction, liss.fit.fe.control.life_satisfaction,
                liss.fit.wfe_fe.trust_in_government, liss.fit.wfe_fe.control.trust_in_government, 
                liss.fit.wfe_fe.satisfaction_with_democracy, liss.fit.wfe_fe.control.satisfaction_with_democracy, 
                liss.fit.wfe_fe.life_satisfaction, liss.fit.wfe_fe.control.life_satisfaction)){
    # print(coef(summary(fit))[1,1])

    # print(deparse(substitute(z)))
    x <- coef(summary(z))["unemployed",]
    plot.data.liss[i,"coef"] <- x[1]
    plot.data.liss[i,"se"] <- x[2]
    plot.data.liss[i,"t"] <- x[3]
    plot.data.liss[i,"p"] <- x[4]
    i <- i + 1
  }

#### MERGE PLOT DATA ####  
    plot.data <- rbind(plot.data.shp, plot.data.liss)
    plot.data$upper95 <- plot.data$coef + 1.96*plot.data$se
    plot.data$lower95 <- plot.data$coef - 1.96*plot.data$se  
    plot.data$outcome <- str_replace(str_extract_all(rownames(plot.data), "\\.[a-z_]*$"), "\\.", "")
    plot.data$survey <- str_replace(str_extract(rownames(plot.data), "[a-z_]*\\."), "\\.", "")
    plot.data$pch[plot.data$survey=="shp"] <- 20
    plot.data$pch[plot.data$survey=="liss"] <- 18
    plot.data$model <- gsub("\\.[a-z_]*$", "", gsub("^[a-z]*\\.[a-z]*\\.", "", rownames(plot.data)))

    plot.data$x.modeltype <- as.numeric(mapvalues(plot.data$model,
                                       from = c("pooling", "pooling.control", "fe", "fe.control", "wfe_fe", "wfe_fe.control" ),
                                       to = c(1,1,2,2,3,3)))
    plot.data$x.controltype <- as.numeric(mapvalues(plot.data$model,
                                       from = c("pooling", "pooling.control", "fe", "fe.control", "wfe_fe", "wfe_fe.control" ),
                                       to = c(1,2,1,2,1,2)))
    plot.data$x.datatype <- as.numeric(mapvalues(plot.data$survey,
                                       from = c("shp", "liss" ),
                                       to = c(1,2)))
    plot.data$x.outcometype <- as.numeric(mapvalues(plot.data$outcome,
                                       from = c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction"),
                                       to = c(1,2,3)))
    # Add Model Names
      plot.data <- arrange(plot.data, x.modeltype, x.datatype, x.outcometype, x.controltype)
      plot.data$name <- paste("M", 1:36, sep="")

    # Rearrange for plot and add x coordinates
      plot.data <- arrange(plot.data, x.modeltype, x.controltype, x.outcometype, x.datatype)
      plot.data$x.plotorder <- 1:36

    # Add x-axis positions
      positions <- c(0.2, 0.3, 0.5, 0.6, 0.8, 0.9) 
      plot.data$x.positions <- rep(positions, 6) + rep(0:5, each = 6)
    # Add colours
      plot.data$color <- mapvalues(plot.data$outcome,
                                       from = c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction"),
                                       to = c("black","orange","blue"))
    # Add symbols
      plot.data$symbol <- as.numeric(mapvalues(plot.data$survey,
                                       from = c("shp", "liss" ),
                                       to = c(20,18)))
    # Add symbols readable for black & white
      plot.data$symbol2[plot.data$survey=="shp" & plot.data$outcome=="trust_in_government"] <- 16
      plot.data$symbol2[plot.data$survey=="shp" & plot.data$outcome=="satisfaction_with_democracy"] <- 15        
      plot.data$symbol2[plot.data$survey=="shp" & plot.data$outcome=="life_satisfaction"] <- 17 
      plot.data$symbol2[plot.data$survey=="liss" & plot.data$outcome=="trust_in_government"] <- 1
      plot.data$symbol2[plot.data$survey=="liss" & plot.data$outcome=="satisfaction_with_democracy"] <- 0        
      plot.data$symbol2[plot.data$survey=="liss" & plot.data$outcome=="life_satisfaction"] <- 2
    # Add symbols readable for black & white

      rm(plot.data.liss, plot.data.shp, i, x, z, names, positions)

# FIGURE 1: Visualization of effects across models, outcomes and datasets ####
jpeg("fig-1.jpg", width = 8, height = 4, units = 'in', res = 800)
par(oma = c(0,0,0,0), mar = c(2,4,1,2))

plot(1, type="n", 
     xlab="", 
     ylab="Outcome", 
     ylim = c(-1.1,1.1),
     xlim = c(0.2,5.8),
     xaxt='n',
    cex.axis= 0.8)

abline(h = 0, col = "red", lty = 2)
abline(h = c(-1, -0.75, -0.5, -0.25, 0.25, 0.5, 0.75, 1), col = "lightgray")
abline(v = c(1, 2, 3, 4, 5, lty = 2), col = "black", lty = 3)
points(plot.data$x.positions, 
     plot.data$coef, 
     pch = plot.data$symbol2,
     col = plot.data$color) 
segments(x0 = plot.data$x.positions,
      y0 = plot.data$lower95,
      x1 = plot.data$x.positions,
      y1 = plot.data$upper95,
      col = plot.data$color)

# Plot Modelnames
  text(plot.data$x.positions,
       plot.data$upper95 + 0.05, 
       plot.data$name,
       srt = 90,
       cex = 0.7,
       adj = c(0,NA))

axis(1, at=0.5:5.5, labels=c("Pooled", "Pooled w.\nControls",
                         "FE", "FE w.\nControls",
                         "WFE", "WFE w.\nControls"), las=1, tck=-0.01, cex.axis= 0.8)

pos <- legend('topright', 
              legend=c("Trust in government",
                       "Satisfaction w. democracy",
                       "Life satisfaction"),
              # box.lwd = 0,
              #box.col = "#FFFFFF80",
              bg = "#FFFFFF80",
              bty = "n",
              cex = 0.8)
points(x = rep(pos$text$x, times=2) - c(0.25,0.1),
       y = rep(pos$text$y, each=2),
       pch = c(16,1,15,0,17,2),
       col = rep(c("black", "orange", "blue"), each=2))

text(x = pos$text$x[1]- c(0.25,0.1),
     y = rep(pos$text$y[3],2)-0.17,
     labels = c("SHP", "LISS"),
     srt = 90,
     cex = 0.8)

dev.off()

      dep.var.labels <- (str_replace_all(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "trust_in_government", "satisfaction_with_democracy", "life_satisfaction"), "_", " "))

   # Hmisc::capitalize

# TABLE 3: POOLING TABLE ####
        stargazer(shp.fit.pooling.trust_in_government,  shp.fit.pooling.control.trust_in_government, 
                shp.fit.pooling.satisfaction_with_democracy, shp.fit.pooling.control.satisfaction_with_democracy,
                shp.fit.pooling.life_satisfaction, shp.fit.pooling.control.life_satisfaction,

                liss.fit.pooling.trust_in_government,  liss.fit.pooling.control.trust_in_government, 
                liss.fit.pooling.satisfaction_with_democracy, liss.fit.pooling.control.satisfaction_with_democracy,
                liss.fit.pooling.life_satisfaction, liss.fit.pooling.control.life_satisfaction,
                type = "latex",
                out="./table-3.tex",
                omit.stat=c("LL","ser","f","adj.rsq"), 
                ci=FALSE, digits=2, 
                ci.level=0.95,
                single.row=FALSE, 
                label = "table-3", 
                font.size="scriptsize", 
                table.placement="!ht", 
                column.sep.width = "-4pt",
                title = "SHP Switzerland and LISS Netherlands: pooling",
                align = TRUE,
                column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
                model.names = FALSE,
                model.numbers = FALSE,
                star.cutoffs = c(0.05, 0.01, 0.001),
                                covariate.labels = c("Unemployed", "Age", "Education", "Member"),
                dep.var.labels = dep.var.labels)

        # CUSTOM TABLE
                custom_table <- function(dataset_labels, ..., cat_output=TRUE, out_file=NULL) {
                    tbl <- capture.output(stargazer::stargazer(...))
                    pattern1 <- 'Dependent variable:'
                    pattern2 <- '(?<= \\& ).+(?= \\\\)'
                    first_row_index <- which(grepl(pattern=pattern1, x=tbl))
                    first_row <- tbl[first_row_index]
                    colspan <- as.numeric(gsub(pattern='[^0-9]+', replacement='', first_row))
                    colspan <- colspan / length(dataset_labels)
                    new_first_row <- sub('[0-9]+', colspan, first_row)
                    replacement <- rep(stringr::str_extract(new_first_row, pattern2), 2)
                    replacement <- stringr::str_replace(replacement, pattern1, dataset_labels)
                    replacement <- paste(replacement, collapse=' & ')
                    new_first_row <- stringr::str_replace(new_first_row, pattern2, replacement)
                    new_first_row <- stringr::str_replace_all(new_first_row, 'multi', '\\\\multi')
                    new_first_row <- stringr::str_replace_all(new_first_row, 'textit', '\\\\textit')
                    tbl[first_row_index] <- new_first_row
                    if ( cat_output ) {
                        cat(tbl, sep='\n')
                    }
                    if ( !is.null(out_file) ) {
                        cat(tbl, sep='\n', file=out_file)
                    }
                }

    custom_table(c('SHP Switzerland', 'LISS Netherlands'),
                out_file="./table-3.tex",
                shp.fit.pooling.trust_in_government,  shp.fit.pooling.control.trust_in_government, 
                shp.fit.pooling.satisfaction_with_democracy, shp.fit.pooling.control.satisfaction_with_democracy,
                shp.fit.pooling.life_satisfaction, shp.fit.pooling.control.life_satisfaction,

                liss.fit.pooling.trust_in_government,  liss.fit.pooling.control.trust_in_government, 
                liss.fit.pooling.satisfaction_with_democracy, liss.fit.pooling.control.satisfaction_with_democracy,
                liss.fit.pooling.life_satisfaction, liss.fit.pooling.control.life_satisfaction,
                type = "latex",
                omit.stat=c("LL","ser","f","adj.rsq"), 
                ci=FALSE, digits=2, 
                ci.level=0.95,
                single.row=FALSE, 
                label = "table-3", 
                font.size="tiny", 
                table.placement="!ht", 
                column.sep.width = "-4pt",
                title = "SHP Switzerland and LISS Netherlands: pooled models",
                align = TRUE,
                column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
                model.names = FALSE,
                model.numbers = FALSE,
                star.cutoffs = c(0.05, 0.01, 0.001),
                                covariate.labels = c("Unemployed", "Age", "Education", "Member"),
                dep.var.labels = dep.var.labels)

# TABLE 4: FE TABLE ####           
           stargazer(shp.fit.fe.trust_in_government,  shp.fit.fe.control.trust_in_government, 
                shp.fit.fe.satisfaction_with_democracy, shp.fit.fe.control.satisfaction_with_democracy,
                shp.fit.fe.life_satisfaction, shp.fit.fe.control.life_satisfaction,

                liss.fit.fe.trust_in_government,  liss.fit.fe.control.trust_in_government, 
                liss.fit.fe.satisfaction_with_democracy, liss.fit.fe.control.satisfaction_with_democracy,
                liss.fit.fe.life_satisfaction, liss.fit.fe.control.life_satisfaction,
                type = "latex",
                out="./table-4.tex",
                omit.stat=c("LL","ser","f","adj.rsq"), 
                ci=FALSE, digits=2, 
                ci.level=0.95,
                single.row=FALSE, 
                label = "table-4", 
                font.size="tiny", 
                table.placement="!ht", 
                column.sep.width = "-4pt",
                title = "SHP Switzerland and LISS Netherlands: fixed effects models",
                align = TRUE,
                column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"), 
                model.names = FALSE,
                model.numbers = FALSE,
                star.cutoffs = c(0.05, 0.01, 0.001),
                                covariate.labels = c("Unemployed", "Age", "Education", "Member"),
                dep.var.labels = dep.var.labels)

        # CUSTOM TABLE
                custom_table <- function(dataset_labels, ..., cat_output=TRUE, out_file=NULL) {
                    tbl <- capture.output(stargazer::stargazer(...))
                    pattern1 <- 'Dependent variable:'
                    pattern2 <- '(?<= \\& ).+(?= \\\\)'
                    first_row_index <- which(grepl(pattern=pattern1, x=tbl))
                    first_row <- tbl[first_row_index]
                    first_row <- gsub("\\[[0-9]+\\]", "", first_row)
                    colspan <- as.numeric(gsub(pattern='[^0-9]+', replacement='', first_row))
                    colspan <- colspan / length(dataset_labels)
                    new_first_row <- sub('[0-9]+', colspan, first_row)
                    replacement <- rep(stringr::str_extract(new_first_row, pattern2), 2)
                    replacement <- stringr::str_replace(replacement, pattern1, dataset_labels)
                    replacement <- paste(replacement, collapse=' & ')
                    new_first_row <- stringr::str_replace(new_first_row, pattern2, replacement)
                    new_first_row <- stringr::str_replace_all(new_first_row, 'multi', '\\\\multi')
                    new_first_row <- stringr::str_replace_all(new_first_row, 'textit', '\\\\textit')
                    tbl[first_row_index] <- new_first_row
                    if ( cat_output ) {
                        cat(tbl, sep='\n')
                    }
                    if ( !is.null(out_file) ) {
                        cat(tbl, sep='\n', file=out_file)
                    }
                }

    custom_table(c('SHP Switzerland', 'LISS Netherlands'),
                out_file='./table-4.tex',        
                shp.fit.fe.trust_in_government,  shp.fit.fe.control.trust_in_government, 
                shp.fit.fe.satisfaction_with_democracy, shp.fit.fe.control.satisfaction_with_democracy,
                shp.fit.fe.life_satisfaction, shp.fit.fe.control.life_satisfaction,

                liss.fit.fe.trust_in_government,  liss.fit.fe.control.trust_in_government, 
                liss.fit.fe.satisfaction_with_democracy, liss.fit.fe.control.satisfaction_with_democracy,
                liss.fit.fe.life_satisfaction, liss.fit.fe.control.life_satisfaction,
                type = "latex",
                omit.stat=c("LL","ser","f","adj.rsq"), 
                ci=FALSE, digits=2, 
                ci.level=0.95,
                single.row=FALSE, 
                label = "table-4", 
                font.size="tiny", 
                table.placement="!ht", 
                column.sep.width = "-4pt",
                title = "SHP Switzerland and LISS Netherlands: fixed effects models",
                align = TRUE,
                column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"), 
                model.names = FALSE,
                model.numbers = FALSE,
                star.cutoffs = c(0.05, 0.01, 0.001),
                                covariate.labels = c("Unemployed", "Age", "Education", "Member"),
                dep.var.labels = dep.var.labels)

# TABLE 5: WFE TABLE ####
  regressors <- c("Unemployed", "Age", "Education", "Member")
  d <- as.data.frame(matrix(rnorm(10 * 5), nc = 5))
  dep.var <- "Trust_in_government"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p1 <- lm(f, d)
  dep.var <- "Satisfaction_with_democracy"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p2 <- lm(f, d)
  dep.var <- "Life_satisfaction"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p3 <- lm(f, d)

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    coef = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,1]),

                as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,1])

                ),
    se = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,2]),

              as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,2])
              ),
    t = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,3]),

             as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,3])

             ),  
    p = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,4]),

             as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,4])
             ),  
    omit.stat = "all",
    notes = "SEs in parentheses.",
    notes.append = TRUE,
    out = "table-5.tex",
    font.size = "tiny",
    label = "table-5",
    table.placement="!ht",
    column.sep.width = "-4pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    digits = 2,
    align = TRUE,
    digits.extra = 0,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001))

        # CUSTOM TABLE
                custom_table <- function(dataset_labels, ..., cat_output=TRUE, out_file=NULL) {
                    tbl <- capture.output(stargazer::stargazer(...))
                    pattern1 <- 'Dependent variable:'
                    pattern2 <- '(?<= \\& ).+(?= \\\\)'
                    first_row_index <- which(grepl(pattern=pattern1, x=tbl))
                    first_row <- tbl[first_row_index]
                    first_row <- gsub("\\[[0-9]+\\]", "", first_row)
                    colspan <- as.numeric(gsub(pattern='[^0-9]+', replacement='', first_row))
                    colspan <- colspan / length(dataset_labels)
                    new_first_row <- sub('[0-9]+', colspan, first_row)
                    replacement <- rep(stringr::str_extract(new_first_row, pattern2), 2)
                    replacement <- stringr::str_replace(replacement, pattern1, dataset_labels)
                    replacement <- paste(replacement, collapse=' & ')
                    new_first_row <- stringr::str_replace(new_first_row, pattern2, replacement)
                    new_first_row <- stringr::str_replace_all(new_first_row, 'multi', '\\\\multi')
                    new_first_row <- stringr::str_replace_all(new_first_row, 'textit', '\\\\textit')
                    tbl[first_row_index] <- new_first_row
                    if ( cat_output ) {
                        cat(tbl, sep='\n')
                    }
                    if ( !is.null(out_file) ) {
                        cat(tbl, sep='\n', file=out_file)
                    }
                }

    custom_table(c('SHP Switzerland', 'LISS Netherlands'),
                out_file='./table-5.tex',        
                p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
                  coef = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,1]),
                              as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,1]),
                              as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,1]),
                              as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,1]),
                              as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,1]),
                              as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,1]),

                              as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,1]),
                              as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,1]),
                              as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,1]),
                              as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,1]),
                              as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,1]),
                              as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,1])

                              ),
                  se = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,2]),
                              as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,2]),
                              as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,2]),
                              as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,2]),
                              as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,2]),
                              as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,2]),

                            as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,2]),
                              as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,2]),
                              as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,2]),
                              as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,2]),
                              as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,2]),
                              as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,2])
                            ),
                  t = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,3]),
                              as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,3]),
                              as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,3]),
                              as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,3]),
                              as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,3]),
                              as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,3]),

                           as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,3]),
                              as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,3]),
                              as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,3]),
                              as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,3]),
                              as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,3]),
                              as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,3])

                           ),  
                  p = list(as.numeric(summary(shp.fit.wfe_fe.trust_in_government)[2]$coefficients[,4]),
                              as.numeric(summary(shp.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,4]),
                              as.numeric(summary(shp.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,4]),
                              as.numeric(summary(shp.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,4]),
                              as.numeric(summary(shp.fit.wfe_fe.life_satisfaction)[2]$coefficients[,4]),
                              as.numeric(summary(shp.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,4]),

                           as.numeric(summary(liss.fit.wfe_fe.trust_in_government)[2]$coefficients[,4]),
                              as.numeric(summary(liss.fit.wfe_fe.control.trust_in_government)[2]$coefficients[,4]),
                              as.numeric(summary(liss.fit.wfe_fe.satisfaction_with_democracy)[2]$coefficients[,4]),
                              as.numeric(summary(liss.fit.wfe_fe.control.satisfaction_with_democracy)[2]$coefficients[,4]),
                              as.numeric(summary(liss.fit.wfe_fe.life_satisfaction)[2]$coefficients[,4]),
                              as.numeric(summary(liss.fit.wfe_fe.control.life_satisfaction)[2]$coefficients[,4])
                           ),  
                  omit.stat = "all",
                  notes = "Heteroscedastic / Autocorrelation Robust Standard Errors in parentheses.",
                  notes.append = TRUE,
                  font.size = "tiny",
                  label = "table-5",
                  table.placement="!ht",
                  column.sep.width = "-4pt", 
                  title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
                  digit.separator="",
                  rownames = FALSE,
                  digits = 2,
                  align = TRUE,
                  digits.extra = 0,
                  column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
                  model.names = FALSE,
                  model.numbers = FALSE,
                  star.cutoffs=c(0.05,0.01,0.001),
                  covariate.labels = c("Unemployed", "Age", "Education", "Member"),
                  dep.var.labels = dep.var.labels)

# FOOTNOTE 7 ####
  # Estimating the within individual variance across time to be better able to compare the effects of 
  # political evaluations to those of life satisfaction
    rm(list=ls())
    load(file = "./data-long-shp.RData") 
    load(file = "./data-long-liss.RData")

  # SHP
    sd.trust_in_government.shp <- sd(data.long.shp$trust_in_government, na.rm=TRUE) # Variation across 
    sd.satisfaction_with_democracy.shp <- sd(data.long.shp$satisfaction_with_democracy, na.rm=TRUE) # Variation across 
    sd.life_satisfaction.shp <- sd(data.long.shp$life_satisfaction, na.rm=TRUE) # Variation across 
    # Variance(Individual values - mean(for each individual))

    x <- data.long.shp %>% group_by(unit) %>% 
    mutate(mean_trust_in_government=mean(trust_in_government, na.rm=TRUE))  %>% 
    mutate(centered_trust_in_government = trust_in_government - mean_trust_in_government) %>% 
    mutate(mean_satisfaction_with_democracy=mean(satisfaction_with_democracy, na.rm=TRUE))  %>% 
    mutate(centered_satisfaction_with_democracy = satisfaction_with_democracy - mean_satisfaction_with_democracy) %>% 
    mutate(mean_life_satisfaction=mean(life_satisfaction, na.rm=TRUE))  %>% 
    mutate(centered_life_satisfaction = life_satisfaction - mean_life_satisfaction)

    sd(x$centered_trust_in_government, na.rm=TRUE) # SD of deviation from individual mean across years (
    sd(x$centered_satisfaction_with_democracy, na.rm=TRUE)
    sd(x$centered_life_satisfaction, na.rm=TRUE)

    mean(x$centered_trust_in_government, na.rm=TRUE)
    mean(x$centered_satisfaction_with_democracy, na.rm=TRUE)
    mean(x$centered_life_satisfaction, na.rm=TRUE)

  # SHP
    sd.trust_in_government.liss <- sd(data.long.liss$trust_in_government, na.rm=TRUE) # Variation across 
    sd.satisfaction_with_democracy.liss <- sd(data.long.liss$satisfaction_with_democracy, na.rm=TRUE) # Variation across 
    sd.life_satisfaction.liss <- sd(data.long.liss$life_satisfaction, na.rm=TRUE) # Variation across 
    # Variance(Individual values - mean(for each individual))

    x <- data.long.liss %>% group_by(unit) %>% 
    mutate(mean_trust_in_government=mean(trust_in_government, na.rm=TRUE))  %>% 
    mutate(centered_trust_in_government = trust_in_government - mean_trust_in_government) %>% 
    mutate(mean_satisfaction_with_democracy= mean(satisfaction_with_democracy, na.rm=TRUE))  %>% 
    mutate(centered_satisfaction_with_democracy = satisfaction_with_democracy - mean_satisfaction_with_democracy) %>% 
    mutate(mean_life_satisfaction=mean(life_satisfaction, na.rm=TRUE))  %>% 
    mutate(centered_life_satisfaction =    life_satisfaction - mean_life_satisfaction)

    sd(x$centered_trust_in_government, na.rm=TRUE) # SD of deviation from individual mean across years
    sd(x$centered_satisfaction_with_democracy, na.rm=TRUE)
    sd(x$centered_life_satisfaction, na.rm=TRUE)

    mean(x$centered_trust_in_government, na.rm=TRUE)
    mean(x$centered_satisfaction_with_democracy, na.rm=TRUE)
    mean(x$centered_life_satisfaction, na.rm=TRUE)

```

\setlength{\tabcolsep}{2pt}

# Introduction
Trust in government and more generally satisfaction with democracy are regarded as indicators of the stability and performance of democratic systems but also as important determinants thereof [@Almond1963-bp; @Easton1975-pe; @Pharr2000-qy; @Dalton2004-ba; @Hetherington2005-el; @Levi2000-dx]. Especially in the wake of the economic crisis in 2008, scholars rang the alarm bells and pointed to the threat that rising unemployment levels may pose to democratic systems [@Arias2013-px; @Kroknes2015-ft; @Muro2014-jg; @Roth2009-jh]. While most research focuses on unemployment's negative personal consequences such as depression or suicidal tendencies, there is also a long research tradition that links it to political phenomena such as voting behavior and political extremism [e.g. @Jahoda1974-or; @Bay2002-fg; @Lundin2009-gh; @Falk2011-ni; @Siedler2006-yw; @Linn1985-gi; @Stokes1984-so]. This research program, in part, speaks to the classic debate that contrasts pocketbook voters whose preferences are assumed to be "swayed most of all by the immediate and tangible circumstances of their private lives" [@Kinder1981-nz, 130], and sociotropic voters whose preferences are influenced by a country's economic condition [@Kinder1981-nz, 129-130; @Hansford2015-pd].     
The present study is guided by the following question: *Does unemployment affect political evaluations in the form of trust in government and satisfaction with democracy?* We contribute to current scholarship in several ways. First, while the classic pocketbook vs. sociotropic voter debate focuses on voting behavior, we investigate the link between unemployment and political evaluations, i.e. trust in government and satisfaction with democracy [e.g. @Kinder1981-nz; @Hansford2015-pd]. Both are regarded as essential resources for the performance and stability of political systems [e.g. @Hetherington1998-kn; @Levi2000-dx]. We thereby contribute to a growing literature that investigates this link empirically [e.g. @Arias2013-px; @Kroknes2015-ft; @Muro2014-jg; @Roth2009-jh]. We summarize previous arguments and empirical evidence, and provide an overview of what we know so far.    
Second, empirical evidence on this relationship is limited. It is either U.S.-centered, comparative in nature, or characterized by certain shortcomings. While unemployment regularly appears as a control variable in multivariate models [@Armingeon2014-ut; @Armingeon2014-xg; @Mishler2001-fp; @Foster2017-si], few studies focus on it as a principal cause, and if so, they operate on the group level comparing either countries or cohorts [@Arias2013-px; @Roth2011-nb]. Here, we focus on the impact of direct, individual-level experiences of unemployment.^[@Laurence2015-nk uses a similar approach but focuses on its impact on generalized trust. Similarly, @Margalit2013-ph and @Naumann2016-yh investigate the impact of unemployment on social policy preferences.] Our study provides a stronger set of evidence in that it expands macro-level evidence with evidence on the individual level and focuses on causal identification. In doing so, we rely on panel data which allows us to investigate the impact of individual-level changes in employment status on individual-level changes in political evaluations. We study this relationship on the basis of data from two different European countries, Switzerland and the Netherlands. This choice is linked both to data availability -- we can rely on high-quality panel surveys that contain the necessary measures -- and to the fact that we expect less crisis-induced distortions in those countries.    
Third, we also examine the effect of unemployment on a control outcome -- life satisfaction. This additional analysis allows us to ensure that our findings are not merely a result of the design choices we made. By showing that our design identifies short-term effects of unemployment on life satisfaction, we alleviate concerns that it may be too conservative to study effects on trust in government or satisfaction with democracy.
We proceed as follows: Section [2](#sec:theory) outlines arguments and empirical evidence that link unemployment and political evaluations. Section [3](#sec:data) presents the design, data and measures. Section [4](#sec:results) summarizes the results. Section [5](#sec:conclusion) provides a summary, discusses limitations and provides rationales for future research.

# Theory, hypotheses and empirical evidence {#sec:theory}
In this study, we link short-term unemployment to political evaluations.^[While the effects of long-term unemployment are just as relevant [e.g. @European_Commission2012-pk], panel surveys generally include too few observations of long-term unemployed respondents to study them in a meaningful way.] Various studies have pointed to direct and indirect mechanisms that connect unemployment to political evaluations [@Ahn2004-mg; @Chabanet2007-ro; @Hudson2006-hz; @Newton2011-ix]. First, we may argue that there is a direct causal path. Let's assume that A loses her job. Given that A blames the government or the political system in general, we would assume that A's support for these same institutions decreases [@Hudson2006-hz, 59; @Mishler2005-mk]. Following this idea, it is argued that job "[d]isplacement may erode institutional-based trust in employers and the economic sphere in general" [@Laurence2015-nk, 47].^[@Laurence2015-nk [p. 48] suggests that the a potential effect of unemployment on generalised trust is mediated by individuals' institutional trust. See also @Delhey2003-hv, @Misztal2001-vv, @Perrucci2009-yq and @Uslaner2002-ks.] While we would expect stronger effects for evaluations of government, people may very well translate their frustration into dissatisfaction with a political system in general.   
Second, there may be various indirect causal paths: becoming unemployed leads to other events that in turn may affect someone's political evaluations. To start, unemployed individuals encounter and experience various institutions that assess their right to benefits and assist them in finding a new job. Those institutions often demand a lot of engagement on the part of the unemployed. Negative experiences with such lower-level institutions (e.g. an employment office) may spill over into one's overall evaluation of political institutions. Unemployment is also linked to various other negative outcomes, i.e. it is supposed to lead to a loss of identity and self-esteem, to a feeling of marginalization or to decrease life satisfaction, optimism, personal efficacy, political participation and to increase stress, anxiety about the future and depression [@Ahn2004-mg; @Archer1993-bq; @Chabanet2007-ro; @Leana1992-cp; @Goldsmith1996-ks; @Laurence2015-nk; @Linn1985-gi; @Rantakeisu1997-lb; @Scott1979-aw; @Waters2007-os; @Winkelmann1998-kb; @Zawadzki1935-gg, 235]. These outcomes in turn may affect political evaluations such as trust in government/satisfaction with democracy. For instance, as depression changes the outlook on life more generally, it should also affect the evaluation of political objects negatively. Overall, these various mechanisms lead to a first hypothesis: *unemployment has a negative effect on trust in government and satisfaction with democracy ($H_{1}$)*.   
At the same time, the above arguments hinge on certain assumptions, the rejection of which leads to an alternative hypothesis. In what concerns the direct effect described, it really hinges on the assumption that someone who becomes unemployed blames the political system or specific institutions for his misfortune. In other words, if someone does not draw the connection between his personal situation and the government/political system, this explanation loses validity. It is also possible that the blame is directed at other actors, e.g. economic actors.      
Second, states make various efforts to cope with the problem of unemployment and implement policies as well as special programs to simplify the reinsertion in the labor market. Fighting unemployment is one of governments' most important tasks (Cezanne 2005, 275). Someone who loses his job is not left alone, but rather helped by the state in many ways, especially in developed countries. If unemployed persons feel that the political institutions are on their side and help them, their political evaluations should either not change at all or possibly in a positive direction [@Roth2009-jh]. These arguments lead to an alternative hypothesis: *unemployment has no effect on trust in government and satisfaction with democracy ($H_{0}$).*    
While the causal pathways described above are hardly testable without the necessary fine-grained data, they provide feasible stories for both $H_{1}$ and $H_{0}$. Similarly, empirical evidence is inconsistent and supports both hypotheses. A first study analyses the General Social Survey 1972-79 with pooled cross-sectional models, introduces unemployment as one of many variables in a structural equation model and yields the following conclusion [@Brehm1997-qy, 1016]: "as aggregate unemployment and inflation fall, and economic expectations rise, confidence in federal institutions also rise". Another study investigates data from the Eurobarometer and the Latinobarometer, uses cohorts as unit of analysis and concludes that the relationship between employment and trust depends on context: increases in cyclical unemployment precede decreases in trust among Europeans, but the opposite seems true among Latin Americans [@Arias2013-px]. A third study investigates how the financial crisis of 2009 and its consequences affected political trust. Analyzing data from the Eurobarometer, the authors investigate 27 EU countries and find that declines in trust in government are related to an increase in unemployment especially in the EU-15 countries [@Roth2011-nb]. A study of the origins of political trust in Post-Communist societies relies on data from the New Democracies Barometer V and the New Russia Barometer VII. It concludes that the "recent experience of unemployment also significantly reduces political trust, but its effect are weak and add little to the overall explanation of trust" [@Mishler2001-fp, 52]. Finally, a study relying on the Eurobarometer, examines the decline of political satisfaction and trust towards parliament in 26 European countries. Unemployment is added as a control variable and has a negative effect on both satisfaction and political trust [@Armingeon2014-xg, 434].

# Data, measures and design {#sec:data}

We investigate three outcomes: *trust in government*, *satisfaction with democracy* and *life satisfaction*. While we lack strong evidence that causally links unemployment and the former two outcomes, there is convincing evidence that unemployment affects life satisfaction negatively [cf. @Winkelmann1998-kb]. Therefore, we use the latter as 'control outcome' to validate our design.  
The data comes from two panel surveys collected in Switzerland and the Netherlands. We restrict our sample to individuals of working age between 18 and 65 years who  can  potentially  experience a period of    unemployment. Both countries show comparably low levels of unemployment within Europe. In the first quartile of 2017, the unemployment rate (national definition) in both countries was at 5.3 percent [@Oecd2017-lj], the more comparable harmonized unemployment rate (HUR) was at 4.9 percent in Switzerland and at 6.7 percent in the Netherlands [@Oecd2017-pq]. Moreover, both countries were among those that weathered the economic crisis relatively well. While unemployment skyrocketed in countries such as Greece or Spain, the increases in Switzerland and the Netherlands were much lower in comparison [@Oecd2017-pq]. Both countries’ electoral systems can be classified as proportional; however, there are various institutional differences. Such institutional differences may, in principle, be responsible for any differences we find between the two countries. For instance, Switzerland is characterized by extensive direct democratic institutions and rights compared to the Netherlands, were the barriers to such forms of participation are higher. In other words, if we were to observe significantly different results across those two datasets, institutional factors may lay at the origin of those differences.      
First, we use data from the *Swiss Household Panel Study (SHP)*, which follows a random sample of households in Switzerland over time by means of computer-assisted telephone interviewing. The SHP started in 1999 with 5,074 households/12,931 household members. In 2004, a second sample of 2,538 households/6,569 household members was added. Second, we rely on the *Longitudinal Internet Studies for the Social Sciences (LISS)*, which is the only other panel study to our knowledge that contains the measures we require. The LISS is based on a random sample of Dutch households drawn from the population register. It consists of 5000 households comprising 8000 household members. Monthly data have been collected by online questionnaires of about 15 to 30 minutes since October 2007. One member in the household provides the household data and updates this information at regular intervals. As described above, both Switzerland and the Netherlands are characterized by rather low rates of unemployment. Table \ref{table-1} gives an overview of the distribution of unemployment in our samples across time.

\input{./table-1.tex}

\input{./table-2.tex}

The measures for both outcomes and treatment are similar across the SHP and the LISS. Table \ref{table-2} gives an overview of the panel waves that contain our measures.     
In the *SHP*, our outcomes are measured as follows: Beginning with the first wave in 1999 (with the exception of 2010), respondents were asked both a trust question and a satisfaction-with-democracy question: "*How much confidence do you have in [The Federal Government (in Bern)], if 0 means 'no confidence' and 10 means 'full confidence'?*" and "*Overall, how satisfied are you with the way in which democracy works in our country, if 0 means 'not at all satisfied' and 10 'completely satisfied'?*" In addition, life satisfaction was queried starting in 2000: "*In general, how satisfied are you with your life if 0 means 'not at all satisfied' and 10 means 'completely satisfied'?*". Our treatment variable ```Unemployed``` takes the value ```1``` if a respondent's working status is actively occupied and is ```0``` if a respondent's working status is unemployed. Respondents who are not in the labor force are coded as missing. Most of the models we estimate focus on change in employment status, i.e. the treatment group are respondents that have become unemployed, whereas the control group is made up of people that have remained employed.^[As unemployment is measured in yearly intervals, a situation in which respondents become unemployed and get another job within this period can not be observed. Nevertheless, we assume that the number of such cases is relatively low. In addition, all those coded as unemployed also answered "*yes*" to the question "*In the last four weeks, have you been looking for a job?*". In other words, they indicated that they are actively seeking a job.]       
In the *LISS*, our outcomes are measured as follows: beginning with the first wave in October 2007 respondents were asked to respond to questions about trust in government, satisfaction with democracy and life satisfaction. Trust in government is measured with the question "*Can you indicate, on a scale from 0 to 10, how much confidence you personally have in each of the following institutions [Dutch government]? 0 means that you have no confidence in an institution and 10 means that you have full confidence*". Satisfaction with democracy is measured with the question "*How satisfied are you with the way in which the following institutions operate in the Netherlands? 0 means that you are very dissatisfied with how the institution operates and 10 means that you are very satisfied*" and respondents evaluate the institution "*democracy*". Life satisfaction is measured with the question "*How satisfied are you with the life you lead at the moment? 0 means not at all satisfied with the life you lead at the moment and 10 means you are completely satisfied*". Apart from that, respondents are queried about their employment situation. Our treatment variable  ```Unemployed``` takes the value ```1``` if a respondent indicates "*I perform paid work (even if is it just for one or several hours per week or for a brief period)*" and it is ```0``` if a respondent indicates "*I am looking for work following the loss of my previous job*". While the LISS measures are not exactly the same as in the Swiss Household Panel, they represent satisfactory proxies. Table \ref{table-2} in the appendix presents summary statistics for all variables used in the analysis.    
In terms of design, a major concern in investigating the link between unemployment and our outcomes are time-invariant and time-variant confounders that may affect both phenomena. Observing units at multiple points in time allows us to link the variance of within-unit changes in unemployment to the variance of within-unit changes in our outcomes of interest.             
We rely on models classically used to analyze panel data [@Croissant2008-tb] but proceed with newer estimation techniques [@Imai2016-td].^[Analyses were conducted relying on R [@R_Core_Team2017-bp], the plm R package [@Croissant2017-mt] and the wfe R package [@Kim2017-vu]. Tables were generated using the Stargazer R package [@Hlavac2014-wd].] First, we estimate linear models that pool the data across all units $i$ and time periods $t$ [@Croissant2008-tb, 2]. The estimated treatment effects represent the difference between observations of individuals who became unemployed and observations of individuals who did not. Thus, treatment and control group may comprise observations of the same individual at different points in time. We estimate those models with and without controls (see Table \ref{table-3}). The results from this first step serve as a point of reference. Second, we continue with fixed effects models (FE models). Through demeaning the data, time-invariant individual components are removed [@Wooldridge2010-jb, 300ff; @Croissant2008-tb, 3]. Again, we estimate models with and without controls for all three outcomes (see Table \ref{table-4}).
Third, we contrast the results from the classic FE estimation strategy with newer methods developed in @Imai2016-td, namely weighted linear fixed effects regression models (WFE models). We refer the reader to @Imai2016-td for an elaborate discussion of the assumptions that are necessary to interpret estimates from fixed effects models as causal effects. @Kim2017-vu provide the software to estimate WFE models for causal inference relying on different weighting schemes (see Table \ref{table-5}).     
In what concerns causality, our main concern is selection on time-invariant covariates, i.e. stable variables that may affect both an individual's propensity to become unemployed and her political evaluations. However, time-invariant confounders cancel out of the equation in the FE and WFE models. Then there may be attributes/variables that are time-variant and affect both unemployment and trust in government/satisfaction with democracy. However, such events/changes only represent a problem, i.e. introduce bias if they are linked to both treatment and outcome and occur among a large enough number of units in our sample. While it is difficult to come up with realistic examples of that kind, we do account for a set of variables that tend to be linked to the risk of unemployment and to trust in government/satisfaction with democracy namely age, education and organizational membership [@Blackaby1999-qd; @Blundell1987-qz; @Collier2005-ja, 144; @Granovetter1973-vq, 1360; @Mishler2001-fp, 49; @Newton2011-ix; @Putnam2000-ea]. While the phenomena we control for are largely stable, they still do change at particular times of an individual's life. And changes in education, or particular jumps on the age scale, could be related to our treatment and outcomes. Moreover, they may also function as proxies for other non-stable phenomena, i.e. events that affect both unemployment and political evaluations may be more likely among those with low education. Table \ref{table-6}, \ref{table-7} and \ref{table-8} in the appendix present summary statistics for all variables used in the analysis.^[In principle, any conclusions we derive may be threatened by non-response bias, i.e. the treated/non-treated in our sample may be not representative of the corresponding groups in the population, selective attrition bias, i.e. individuals who drop out at t are systematically different in terms of treatment and outcome, and finally measurement error, e.g. individuals who become unemployed do not reveal their status to the interviewer. We have to assume that these biases are either absent or at least not strong enough to distort our findings.] 
Apart from the effect on political evaluations, we investigate the effect of unemployment on life satisfaction. This is to safeguard that our findings are not merely a result of the design choices we made.         
Finally, a comment on reverse causality. We rely on data that measures both outcome and treatment at the beginning/end of yearly periods. We relate within-year changes in the treatment to within-year changes in the outcome. In principle, we do not know when those changes occur within these time periods. In other words, we do not know when exactly people changed their employment status or their political evaluations (and what precedes what). This is a general limitation of panel data. However, in our view it is unlikely that changes in trust in government/satisfaction with democracy cause people to become unemployed. In other words, arguments that describe a causal path from trust in government/satisfaction with democracy to unemployment seem implausible, meaning that such causal paths do not realistically apply to a significant number of people in our sample.

# Empirical results {#sec:results}

Table \ref{table-3} displays the results for the pooled data for both the SHP Switzerland and the LISS Netherlands, pooling all units (individuals) across time. The large N in the respective models reflects the number of unit*time observations. The coefficients for unemployed describe the differences in the outcome averages between those who are employed and those who are not. The respective models (M1-M12) consistently show that unemployment negatively affects trust in government, satisfaction with democracy and life satisfaction. All coefficients are statistically significant both with and without controls. Moreover, while we would argue that all coefficients are also substantively significant (outcomes are measured on 11-point scales), i.e. in terms of size, unemployment has a much larger effect on life satisfaction than on political evaluations, as can be seen from Model 5, 6, 11, 12 in Table \ref{table-3}. Table \ref{table-3} also reveals that the effects are relatively consistent across the two panel datasets. All are negative, and the differences across the two datasets are altogether not that strong. However, we would expect that the results in Table \ref{table-3} are biased, as there are various unobserved time-invariant and time-variant confounders affecting both unemployment and our outcomes of interest.

\input{./table-3.tex}

Therefore, in a second step we rely on fixed effects models (FE) as displayed in Table \ref{table-4}. We find that the differences to the pooled models are considerable. The effect on life satisfaction is consistently statistically significant and substantially significant (M17, M18, M23, M24). In contrast, the effect on satisfaction with democracy is not statistically significant and substantially small (M15, M16, M21, M22). The effects on trust in government are substantially small and not statistically significant in the SHP (M13, M14). In the LISS dataset, the effect is stronger in the model which excludes controls (M19); however, it weakens as we add controls (M20). While these results are not exactly clear-cut, in our view, they are not consistent enough to infer that there is a causal effect of unemployment on satisfaction with democracy or trust in government in the present sample, especially for the latter outcome. First, the effects on our outcomes are much smaller compared to the effect on life satisfaction, especially when we focus on the models that include covariates (M14, M16, M20, M22). Second, only a single coefficient (M20) reaches statistical significance considering a p < 0.05 threshold. However, such a p-value is regarded by some as only providing suggestive evidence [@Benjamin2017-rf], while others suggest to abandon such arbitrary cut-off values altogether [@McShane2017-bc].

\input{./table-4.tex}

\input{./table-5.tex}

Finally, following the arguments provided in @Imai2016-td, we estimate a further set of weighted linear fixed effects (WFE) models. Table \ref{table-5} displays the corresponding results, which mirror those obtained through FE estimation. The effect on life satisfaction remains robust, with and without controls. Moreover, the effect sizes seem substantively significant. In comparison, the effects on trust in government and satisfaction (M26, M28, M32, M34) are only partly statistically significant (p < 0.05 in M28, M32). Furthermore, they are generally small in size as compared to the effect on life satisfaction, despite the fact that all outcomes are measured on 11-point scales.^[The within-unit over time variation of life satisfaction is lower than that of trust in government and satisfaction with democracy. Besides, scholars recently suggested that p-values between 0.005 and 0.05 can only be regarded as suggestive evidence [@Benjamin2017-rf, 3].] Given this inconsistency, our results seem to support $H_{0}$, namely that *unemployment has no effect on trust in government or satisfaction with democracy*. This general pattern is visualized in Figure \ref{fig-results}, which summarizes the results. We discuss limitations that may undermine this conclusion below.

\begin{figure}[h]
\centering
\caption{Visualization of effects across models, outcomes and datasets}\label{fig-results}
		\includegraphics[width=1\linewidth]{fig-1.jpg}
\begin{flushleft}
\scriptsize Note: Filled (SHP data) and empty (LISS data) symbols represent point estimates of effects for 36 models; lines represent 95\% confidence intervals;  model names M1-M36 correspond to model names in Table 3, 4 and 5; see plot legend for further explanation; FE = fixed effects, WFE = Weighted linear fixed effects; data: Swiss Household Panel (SHP) and Longitudinal Internet Studies for the Social sciences (LISS).
\end{flushleft}
\end{figure}

# Discussion and conclusion {#sec:conclusion}
We investigate whether unemployment affects trust in government and satisfaction with democracy. We thereby contribute to current scholarship on the effects of unemployment [@Brand2015-rr; @Naumann2016-yh; @Margalit2013-ph], on causes of political trust and satisfaction with democracy [e.g. @Listhaug2017-et], and on the more general link between experiences and trust [@Listhaug2017-et; @Dinesen2015-fr]. Relying on panel data and corresponding models, we find no consistent evidence that unemployment negatively affects trust in government or satisfaction with democracy, which is in line with $H_{0}$. However, we can replicate earlier findings on the negative relationship between unemployment and life satisfaction [cf. @Winkelmann1998-kb], which suggests that our apparent non-finding is not merely a result of the methods we apply. Our findings somewhat contrast macro-level evidence that links unemployment to political trust [e.g. @Kroknes2015-ft; @Roth2011-nb] but also micro-level evidence that links unemployment to support for the welfare state and unemployment benefits [@Naumann2016-yh; @Margalit2013-ph]. The former contrast can possibly be explained by both the classic pocketbook--sociotropic voter argument and by case selection. The latter difference is more intriguing. It seems to indicate that an experience of unemployment may affect concrete attitudes towards policies linked to unemployment, while more abstract attitudes remain largely unaffected.      
Our study is characterized by limitations. These may explain the above-mentioned differences but also serve as starting points for future research. First, in line with other panel-data studies that focus on single countries [e.g. @Margalit2013-ph; @Naumann2016-yh], we analyze panel data from "only" two countries, Switzerland and the Netherlands. As discussed before, the relationship between unemployment and political evaluations may hinge on the prevalence of certain norms, on the basis of which the unemployed blame the government or the political system for their fate or not. Such a mechanism seems highly unlikely in some contexts, e.g. the U.S., but more likely in other contexts, e.g. Spain. While the effects we find are relatively consistent across two countries, more panel data from a wider set of countries may allow researchers to investigate such potential for context dependence.     
A second drawback concerns the particular types of unemployment experiences we study. We do not have enough information to properly unpack what experiences lurk behind our unemployment variable. The reasons why someone has become unemployed should matter. Future studies would ideally measure and differentiate between such reasons for unemployment in a more fine-grained way. For instance, someone whose unemployment was a direct consequence of the crisis may be quicker to connect her situation to politics. Furthermore, we focus on the effects of direct unemployment experiences. However, following the sociotropic argument, indirect experiences of unemployment, e.g. observing people in one's network [@Newman2017-ls] or in one's neighborhood [@Bisgaard2015-xb; @Oesch2013-za], may equally matter. Studying and contrasting such indirect experiences with direct experiences is an important area of future research.    
Third, time matters. To start, the length of treatment could matter. It seems plausible that long-term unemployment affects political evaluations to a greater extent than short-term unemployment. Our data do not contain enough observations of the long-term unemployed. Although collecting such data is challenging, we nevertheless think that studying the political attitudes of citizens who have been excluded from the labor market for long periods is relevant, especially given predictions of how automation may increase levels of unemployment [e.g. @Arntz2016-od]. Of course, studying such long-term lags and the effects of long-term unemployment is challenging from a design perspective. The longer an individual's period of unemployment is, the less likely we are to find a suitable control unit or observation that displays a similar life trajectory and differentiates itself only through being employed. On another note, with one-year panel periods we may fail to capture effects that are more short-term. Thus, future studies would ideally measure our individual-level outcomes on a more frequent basis both before and after the onset of unemployment.     
Finally, our investigation is limited by the sample size. In principle, it is possible that the effect of unemployment is heterogeneous across (subgroups of) individuals (treatment effect heterogeneity). For certain individuals, the causal story we provide may seem more plausible. For instance, unemployment may have a stronger effect on groups that are already disadvantaged in the labor market, such as women or individuals with lower class background. Similarly, individuals' ideology should determine whether they link their personal economic situation to a government or to the wider political system. Future data collections that comprise more individuals may allow for an exploration of such assumed treatment heterogeneity.

\newpage

# Appendix {#sec:appendix}

\input{./table-6.tex}

\input{./table-7.tex}

\input{./table-8.tex}

\normalsize

\clearpage

# References

### 2020-04-28 Dataverse/paper_and_analysis_bauer_2018_socius.tex
organzing my repo

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Wingdings}
    \setsansfont[]{Wingdings}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdfauthor={Paul C. Bauer},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Unemployment, Trust in Government\\
and Satisfaction with Democracy:\\
An Empirical Investigation*\footnote{Acknowledgements: I thank the participants of the Swiss Political Science Conference 2016, the annual conference for the European Political Science Association 2015, Hanspeter Kriesi, Stefanie Reher, Jonathan Chapman, Florian Stöckel and anonymous reviewers for their helpful comments. I am also grateful to Giada Gianola for excellent research assistance. Reproduction files and data can be accessed under \url{http://dx.doi.org/10.7910/DVN/DUMGLT}. This study has been realized using data collected by the Swiss Household Panel (SHP), which is based at the Swiss Centre of Expertise in the Social Sciences FORS and financed by the Swiss National Science Foundation as well as data from the LISS (Longitudinal Internet Studies for the Social sciences) panel, administered by CentERdata (Tilburg University, The Netherlands). The publication of this article was funded by the ``Mannheim Centre for European Social Research''. Corresponding Author: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}, University Mannheim, Mannheim Centre for European Social Research (MZES), 68131 Mannheim Germany, \url{http://www.paulcbauer.eu}.}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
    \date{}
    \predate{}\postdate{}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{url}
\usepackage{array}
\usepackage{setspace}
\usepackage{graphics}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{lscape}
\usepackage{array}
\usepackage{color}
\usepackage{setspace}
\usepackage{float}
\usepackage{cleveref}[2012/02/15]
\usepackage{fullpage}
\usepackage[charter]{mathdesign}
\usepackage{bm}

\crefformat{footnote}{#2\footnotemark[#1]#3}
\usepackage{color}
\usepackage{hyperref}

\newenvironment{tightcenter}{%
  \setlength\topsep{0pt}
  \setlength\parskip{0pt}
  \begin{center}
}{%
  \end{center}
}

%\setstretch{1.1}
% Dutch style of paragraph formatting
\parskip 5pt
\makeatletter
% Separation between lines
\doublerulesep 1pt

\usepackage[table]{xcolor}

\definecolor{lightred}{rgb}{0.7,0,0}
\definecolor{darkgreen}{rgb}{0,0.8,0}
\definecolor{lightblue}{rgb}{0,0,0.7}

\hypersetup{colorlinks,
  linkcolor = lightred,
  filecolor = lightred,
  urlcolor = lightblue,
  citecolor = lightred}

% Spaces in bibliography
\let\oldthebibliography=\thebibliography
\let\endoldthebibliography=\endthebibliography
\renewenvironment{thebibliography}[1]{%
  \begin{oldthebibliography}{#1}%
    \setlength{\parskip}{0ex}%
    \setlength{\itemsep}{0.1ex}%
  }%
  {%
  \end{oldthebibliography}%
}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\setlength{\parindent}{0pt} % no indentation

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}Evidence suggests that unemployment negatively affects various aspects of individuals' lives. We investigate whether unemployment changes individuals' political evaluations in the form of trust in government and satisfaction with democracy. While most research in this area operates on the macro level, we provide individual-level evidence. In doing so, we investigate the assumed causal link with panel data from Switzerland and the Netherlands. In addition, we study the impact on life satisfaction, a `control outcome', known to be affected by unemployment. While there is strong evidence that changes in employment status do affect life satisfaction, effects on trust in government and satisfaction with democracy seem mostly absent or negligible in size. \vspace{.8cm}
\end{abstract}

\newcommand*{\secref}[1]{Section~\ref{#1}}

\setlength{\tabcolsep}{2pt}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Trust in government and more generally satisfaction with democracy are regarded as indicators of the stability and performance of democratic systems but also as important determinants thereof (Almond and Verba 1963; Easton 1975; Pharr and Putnam 2000; Dalton 2004; Hetherington 2005; Levi and Stoker 2000). Especially in the wake of the economic crisis in 2008, scholars rang the alarm bells and pointed to the threat that rising unemployment levels may pose to democratic systems (Arias et al. 2013; Kroknes, Jakobsen, and Grønning 2015; Muro and Vidal 2014; Roth 2009). While most research focuses on unemployment's negative personal consequences such as depression or suicidal tendencies, there is also a long research tradition that links it to political phenomena such as voting behavior and political extremism (e.g. Jahoda and Zeisel 1974; Bay and Blekesaune 2002; Lundin and Hemmingsson 2009; Falk, Kuhn, and Zweimueller 2011; Siedler 2006; Linn, Sandifer, and Stein 1985; Stokes and Cochrane 1984). This research program, in part, speaks to the classic debate that contrasts pocketbook voters whose preferences are assumed to be ``swayed most of all by the immediate and tangible circumstances of their private lives'' (Kinder and Roderick Kiewiet 1981, 130), and sociotropic voters whose preferences are influenced by a country's economic condition (Kinder and Roderick Kiewiet 1981, 129--30; Hansford and Gomez 2015).\\
The present study is guided by the following question: \emph{Does unemployment affect political evaluations in the form of trust in government and satisfaction with democracy?} We contribute to current scholarship in several ways. First, while the classic pocketbook vs.~sociotropic voter debate focuses on voting behavior, we investigate the link between unemployment and political evaluations, i.e.~trust in government and satisfaction with democracy (e.g. Kinder and Roderick Kiewiet 1981; Hansford and Gomez 2015). Both are regarded as essential resources for the performance and stability of political systems (e.g. Hetherington 1998; Levi and Stoker 2000). We thereby contribute to a growing literature that investigates this link empirically (e.g. Arias et al. 2013; Kroknes, Jakobsen, and Grønning 2015; Muro and Vidal 2014; Roth 2009). We summarize previous arguments and empirical evidence, and provide an overview of what we know so far.\\
Second, empirical evidence on this relationship is limited. It is either U.S.-centered, comparative in nature, or characterized by certain shortcomings. While unemployment regularly appears as a control variable in multivariate models (Armingeon and Ceka 2014; Armingeon and Guthmann 2014; Mishler and Rose 2001; Foster and Frieden 2017), few studies focus on it as a principal cause, and if so, they operate on the group level comparing either countries or cohorts (Arias et al. 2013; Roth, Nowak-Lehmann, and Otter 2011). Here, we focus on the impact of direct, individual-level experiences of unemployment.\footnote{Laurence (2015) uses a similar approach but focuses on its impact on generalized trust. Similarly, Margalit (2013) and Naumann, Buss, and Bähr (2016) investigate the impact of unemployment on social policy preferences.} Our study provides a stronger set of evidence in that it expands macro-level evidence with evidence on the individual level and focuses on causal identification. In doing so, we rely on panel data which allows us to investigate the impact of individual-level changes in employment status on individual-level changes in political evaluations. We study this relationship on the basis of data from two different European countries, Switzerland and the Netherlands. This choice is linked both to data availability -- we can rely on high-quality panel surveys that contain the necessary measures -- and to the fact that we expect less crisis-induced distortions in those countries.\\
Third, we also examine the effect of unemployment on a control outcome -- life satisfaction. This additional analysis allows us to ensure that our findings are not merely a result of the design choices we made. By showing that our design identifies short-term effects of unemployment on life satisfaction, we alleviate concerns that it may be too conservative to study effects on trust in government or satisfaction with democracy.
We proceed as follows: Section \protect\hyperlink{sec:theory}{2} outlines arguments and empirical evidence that link unemployment and political evaluations. Section \protect\hyperlink{sec:data}{3} presents the design, data and measures. Section \protect\hyperlink{sec:results}{4} summarizes the results. Section \protect\hyperlink{sec:conclusion}{5} provides a summary, discusses limitations and provides rationales for future research.

\hypertarget{sec:theory}{%
\section{Theory, hypotheses and empirical evidence}\label{sec:theory}}

In this study, we link short-term unemployment to political evaluations.\footnote{While the effects of long-term unemployment are just as relevant (e.g. European Commission 2012), panel surveys generally include too few observations of long-term unemployed respondents to study them in a meaningful way.} Various studies have pointed to direct and indirect mechanisms that connect unemployment to political evaluations (Ahn, Garcia, and Jimeno 2004; Chabanet 2007; Hudson 2006; Newton and Zmerli 2011). First, we may argue that there is a direct causal path. Let's assume that A loses her job. Given that A blames the government or the political system in general, we would assume that A's support for these same institutions decreases (Hudson 2006, 59; Mishler and Rose 2005). Following this idea, it is argued that job ``{[}d{]}isplacement may erode institutional-based trust in employers and the economic sphere in general'' (Laurence 2015, 47).\footnote{Laurence (2015, 48) suggests that the a potential effect of unemployment on generalised trust is mediated by individuals' institutional trust. See also Delhey and Newton (2003), Misztal (2001), Perrucci and Perrucci (2009) and Uslaner (2002).} While we would expect stronger effects for evaluations of government, people may very well translate their frustration into dissatisfaction with a political system in general.\\
Second, there may be various indirect causal paths: becoming unemployed leads to other events that in turn may affect someone's political evaluations. To start, unemployed individuals encounter and experience various institutions that assess their right to benefits and assist them in finding a new job. Those institutions often demand a lot of engagement on the part of the unemployed. Negative experiences with such lower-level institutions (e.g.~an employment office) may spill over into one's overall evaluation of political institutions. Unemployment is also linked to various other negative outcomes, i.e.~it is supposed to lead to a loss of identity and self-esteem, to a feeling of marginalization or to decrease life satisfaction, optimism, personal efficacy, political participation and to increase stress, anxiety about the future and depression (Ahn, Garcia, and Jimeno 2004; Archer and Rhodes 1993; Chabanet 2007; Leana and Feldman 1992; Goldsmith, Veum, and Darity 1996; Laurence 2015; Linn, Sandifer, and Stein 1985; Rantakeisu, Starrin, and Hagquist 1997; Scott and Acock 1979; Waters 2007; Winkelmann and Winkelmann 1998; Zawadzki and Lazarsfeld 1935, 235). These outcomes in turn may affect political evaluations such as trust in government/satisfaction with democracy. For instance, as depression changes the outlook on life more generally, it should also affect the evaluation of political objects negatively. Overall, these various mechanisms lead to a first hypothesis: \emph{unemployment has a negative effect on trust in government and satisfaction with democracy (\(H_{1}\))}.\\
At the same time, the above arguments hinge on certain assumptions, the rejection of which leads to an alternative hypothesis. In what concerns the direct effect described, it really hinges on the assumption that someone who becomes unemployed blames the political system or specific institutions for his misfortune. In other words, if someone does not draw the connection between his personal situation and the government/political system, this explanation loses validity. It is also possible that the blame is directed at other actors, e.g.~economic actors.\\
Second, states make various efforts to cope with the problem of unemployment and implement policies as well as special programs to simplify the reinsertion in the labor market. Fighting unemployment is one of governments' most important tasks (Cezanne 2005, 275). Someone who loses his job is not left alone, but rather helped by the state in many ways, especially in developed countries. If unemployed persons feel that the political institutions are on their side and help them, their political evaluations should either not change at all or possibly in a positive direction (Roth 2009). These arguments lead to an alternative hypothesis: \emph{unemployment has no effect on trust in government and satisfaction with democracy (\(H_{0}\)).}\\
While the causal pathways described above are hardly testable without the necessary fine-grained data, they provide feasible stories for both \(H_{1}\) and \(H_{0}\). Similarly, empirical evidence is inconsistent and supports both hypotheses. A first study analyses the General Social Survey 1972-79 with pooled cross-sectional models, introduces unemployment as one of many variables in a structural equation model and yields the following conclusion (Brehm and Rahn 1997, 1016): ``as aggregate unemployment and inflation fall, and economic expectations rise, confidence in federal institutions also rise''. Another study investigates data from the Eurobarometer and the Latinobarometer, uses cohorts as unit of analysis and concludes that the relationship between employment and trust depends on context: increases in cyclical unemployment precede decreases in trust among Europeans, but the opposite seems true among Latin Americans (Arias et al. 2013). A third study investigates how the financial crisis of 2009 and its consequences affected political trust. Analyzing data from the Eurobarometer, the authors investigate 27 EU countries and find that declines in trust in government are related to an increase in unemployment especially in the EU-15 countries (Roth, Nowak-Lehmann, and Otter 2011). A study of the origins of political trust in Post-Communist societies relies on data from the New Democracies Barometer V and the New Russia Barometer VII. It concludes that the ``recent experience of unemployment also significantly reduces political trust, but its effect are weak and add little to the overall explanation of trust'' (Mishler and Rose 2001, 52). Finally, a study relying on the Eurobarometer, examines the decline of political satisfaction and trust towards parliament in 26 European countries. Unemployment is added as a control variable and has a negative effect on both satisfaction and political trust (Armingeon and Guthmann 2014, 434).

\hypertarget{sec:data}{%
\section{Data, measures and design}\label{sec:data}}

We investigate three outcomes: \emph{trust in government}, \emph{satisfaction with democracy} and \emph{life satisfaction}. While we lack strong evidence that causally links unemployment and the former two outcomes, there is convincing evidence that unemployment affects life satisfaction negatively (cf. Winkelmann and Winkelmann 1998). Therefore, we use the latter as `control outcome' to validate our design.\\
The data comes from two panel surveys collected in Switzerland and the Netherlands. We restrict our sample to individuals of working age between 18 and 65 years who can potentially experience a period of unemployment. Both countries show comparably low levels of unemployment within Europe. In the first quartile of 2017, the unemployment rate (national definition) in both countries was at 5.3 percent (OECD 2017b), the more comparable harmonized unemployment rate (HUR) was at 4.9 percent in Switzerland and at 6.7 percent in the Netherlands (OECD 2017a). Moreover, both countries were among those that weathered the economic crisis relatively well. While unemployment skyrocketed in countries such as Greece or Spain, the increases in Switzerland and the Netherlands were much lower in comparison (OECD 2017a). Both countries' electoral systems can be classified as proportional; however, there are various institutional differences. Such institutional differences may, in principle, be responsible for any differences we find between the two countries. For instance, Switzerland is characterized by extensive direct democratic institutions and rights compared to the Netherlands, were the barriers to such forms of participation are higher. In other words, if we were to observe significantly different results across those two datasets, institutional factors may lay at the origin of those differences.\\
First, we use data from the \emph{Swiss Household Panel Study (SHP)}, which follows a random sample of households in Switzerland over time by means of computer-assisted telephone interviewing. The SHP started in 1999 with 5,074 households/12,931 household members. In 2004, a second sample of 2,538 households/6,569 household members was added. Second, we rely on the \emph{Longitudinal Internet Studies for the Social Sciences (LISS)}, which is the only other panel study to our knowledge that contains the measures we require. The LISS is based on a random sample of Dutch households drawn from the population register. It consists of 5000 households comprising 8000 household members. Monthly data have been collected by online questionnaires of about 15 to 30 minutes since October 2007. One member in the household provides the household data and updates this information at regular intervals. As described above, both Switzerland and the Netherlands are characterized by rather low rates of unemployment. Table \ref{table-1} gives an overview of the distribution of unemployment in our samples across time.

\input{./table-1.tex}

\input{./table-2.tex}

The measures for both outcomes and treatment are similar across the SHP and the LISS. Table \ref{table-2} gives an overview of the panel waves that contain our measures.\\
In the \emph{SHP}, our outcomes are measured as follows: Beginning with the first wave in 1999 (with the exception of 2010), respondents were asked both a trust question and a satisfaction-with-democracy question: ``\emph{How much confidence do you have in {[}The Federal Government (in Bern){]}, if 0 means `no confidence' and 10 means `full confidence'?}'' and ``\emph{Overall, how satisfied are you with the way in which democracy works in our country, if 0 means `not at all satisfied' and 10 `completely satisfied'?}'' In addition, life satisfaction was queried starting in 2000: ``\emph{In general, how satisfied are you with your life if 0 means `not at all satisfied' and 10 means `completely satisfied'?}''. Our treatment variable \texttt{Unemployed} takes the value \texttt{1} if a respondent's working status is actively occupied and is \texttt{0} if a respondent's working status is unemployed. Respondents who are not in the labor force are coded as missing. Most of the models we estimate focus on change in employment status, i.e.~the treatment group are respondents that have become unemployed, whereas the control group is made up of people that have remained employed.\footnote{As unemployment is measured in yearly intervals, a situation in which respondents become unemployed and get another job within this period can not be observed. Nevertheless, we assume that the number of such cases is relatively low. In addition, all those coded as unemployed also answered ``\emph{yes}'' to the question ``\emph{In the last four weeks, have you been looking for a job?}''. In other words, they indicated that they are actively seeking a job.}\\
In the \emph{LISS}, our outcomes are measured as follows: beginning with the first wave in October 2007 respondents were asked to respond to questions about trust in government, satisfaction with democracy and life satisfaction. Trust in government is measured with the question ``\emph{Can you indicate, on a scale from 0 to 10, how much confidence you personally have in each of the following institutions {[}Dutch government{]}? 0 means that you have no confidence in an institution and 10 means that you have full confidence}''. Satisfaction with democracy is measured with the question ``\emph{How satisfied are you with the way in which the following institutions operate in the Netherlands? 0 means that you are very dissatisfied with how the institution operates and 10 means that you are very satisfied}'' and respondents evaluate the institution ``\emph{democracy}''. Life satisfaction is measured with the question ``\emph{How satisfied are you with the life you lead at the moment? 0 means not at all satisfied with the life you lead at the moment and 10 means you are completely satisfied}''. Apart from that, respondents are queried about their employment situation. Our treatment variable \texttt{Unemployed} takes the value \texttt{1} if a respondent indicates ``\emph{I perform paid work (even if is it just for one or several hours per week or for a brief period)}'' and it is \texttt{0} if a respondent indicates ``\emph{I am looking for work following the loss of my previous job}''. While the LISS measures are not exactly the same as in the Swiss Household Panel, they represent satisfactory proxies. Table \ref{table-2} in the appendix presents summary statistics for all variables used in the analysis.\\
In terms of design, a major concern in investigating the link between unemployment and our outcomes are time-invariant and time-variant confounders that may affect both phenomena. Observing units at multiple points in time allows us to link the variance of within-unit changes in unemployment to the variance of within-unit changes in our outcomes of interest.\\
We rely on models classically used to analyze panel data (Croissant, Millo, and Others 2008) but proceed with newer estimation techniques (Imai and Kim 2016).\footnote{Analyses were conducted relying on R ({\textbf{???}}), the plm R package (Croissant et al. 2017) and the wfe R package (Kim, Imai, and Wang 2017). Tables were generated using the Stargazer R package (Hlavac 2014).} First, we estimate linear models that pool the data across all units \(i\) and time periods \(t\) (Croissant, Millo, and Others 2008, 2). The estimated treatment effects represent the difference between observations of individuals who became unemployed and observations of individuals who did not. Thus, treatment and control group may comprise observations of the same individual at different points in time. We estimate those models with and without controls (see Table \ref{table-3}). The results from this first step serve as a point of reference. Second, we continue with fixed effects models (FE models). Through demeaning the data, time-invariant individual components are removed (Wooldridge 2010, 300ff; Croissant, Millo, and Others 2008, 3). Again, we estimate models with and without controls for all three outcomes (see Table \ref{table-4}).
Third, we contrast the results from the classic FE estimation strategy with newer methods developed in Imai and Kim (2016), namely weighted linear fixed effects regression models (WFE models). We refer the reader to Imai and Kim (2016) for an elaborate discussion of the assumptions that are necessary to interpret estimates from fixed effects models as causal effects. Kim, Imai, and Wang (2017) provide the software to estimate WFE models for causal inference relying on different weighting schemes (see Table \ref{table-5}).\\
In what concerns causality, our main concern is selection on time-invariant covariates, i.e.~stable variables that may affect both an individual's propensity to become unemployed and her political evaluations. However, time-invariant confounders cancel out of the equation in the FE and WFE models. Then there may be attributes/variables that are time-variant and affect both unemployment and trust in government/satisfaction with democracy. However, such events/changes only represent a problem, i.e.~introduce bias if they are linked to both treatment and outcome and occur among a large enough number of units in our sample. While it is difficult to come up with realistic examples of that kind, we do account for a set of variables that tend to be linked to the risk of unemployment and to trust in government/satisfaction with democracy namely age, education and organizational membership (Blackaby et al. 1999; Blundell, Ham, and Meghir 1987; Collier 2005, 144; Granovetter 1973, 1360; Mishler and Rose 2001, 49; Newton and Zmerli 2011; Putnam 2000). While the phenomena we control for are largely stable, they still do change at particular times of an individual's life. And changes in education, or particular jumps on the age scale, could be related to our treatment and outcomes. Moreover, they may also function as proxies for other non-stable phenomena, i.e.~events that affect both unemployment and political evaluations may be more likely among those with low education. Table \ref{table-6}, \ref{table-7} and \ref{table-8} in the appendix present summary statistics for all variables used in the analysis.\footnote{In principle, any conclusions we derive may be threatened by non-response bias, i.e.~the treated/non-treated in our sample may be not representative of the corresponding groups in the population, selective attrition bias, i.e.~individuals who drop out at t are systematically different in terms of treatment and outcome, and finally measurement error, e.g.~individuals who become unemployed do not reveal their status to the interviewer. We have to assume that these biases are either absent or at least not strong enough to distort our findings.}
Apart from the effect on political evaluations, we investigate the effect of unemployment on life satisfaction. This is to safeguard that our findings are not merely a result of the design choices we made.\\
Finally, a comment on reverse causality. We rely on data that measures both outcome and treatment at the beginning/end of yearly periods. We relate within-year changes in the treatment to within-year changes in the outcome. In principle, we do not know when those changes occur within these time periods. In other words, we do not know when exactly people changed their employment status or their political evaluations (and what precedes what). This is a general limitation of panel data. However, in our view it is unlikely that changes in trust in government/satisfaction with democracy cause people to become unemployed. In other words, arguments that describe a causal path from trust in government/satisfaction with democracy to unemployment seem implausible, meaning that such causal paths do not realistically apply to a significant number of people in our sample.

\hypertarget{sec:results}{%
\section{Empirical results}\label{sec:results}}

Table \ref{table-3} displays the results for the pooled data for both the SHP Switzerland and the LISS Netherlands, pooling all units (individuals) across time. The large N in the respective models reflects the number of unit*time observations. The coefficients for unemployed describe the differences in the outcome averages between those who are employed and those who are not. The respective models (M1-M12) consistently show that unemployment negatively affects trust in government, satisfaction with democracy and life satisfaction. All coefficients are statistically significant both with and without controls. Moreover, while we would argue that all coefficients are also substantively significant (outcomes are measured on 11-point scales), i.e.~in terms of size, unemployment has a much larger effect on life satisfaction than on political evaluations, as can be seen from Model 5, 6, 11, 12 in Table \ref{table-3}. Table \ref{table-3} also reveals that the effects are relatively consistent across the two panel datasets. All are negative, and the differences across the two datasets are altogether not that strong. However, we would expect that the results in Table \ref{table-3} are biased, as there are various unobserved time-invariant and time-variant confounders affecting both unemployment and our outcomes of interest.

\input{./table-3.tex}

Therefore, in a second step we rely on fixed effects models (FE) as displayed in Table \ref{table-4}. We find that the differences to the pooled models are considerable. The effect on life satisfaction is consistently statistically significant and substantially significant (M17, M18, M23, M24). In contrast, the effect on satisfaction with democracy is not statistically significant and substantially small (M15, M16, M21, M22). The effects on trust in government are substantially small and not statistically significant in the SHP (M13, M14). In the LISS dataset, the effect is stronger in the model which excludes controls (M19); however, it weakens as we add controls (M20). While these results are not exactly clear-cut, in our view, they are not consistent enough to infer that there is a causal effect of unemployment on satisfaction with democracy or trust in government in the present sample, especially for the latter outcome. First, the effects on our outcomes are much smaller compared to the effect on life satisfaction, especially when we focus on the models that include covariates (M14, M16, M20, M22). Second, only a single coefficient (M20) reaches statistical significance considering a p \textless{} 0.05 threshold. However, such a p-value is regarded by some as only providing suggestive evidence (Benjamin et al. 2017), while others suggest to abandon such arbitrary cut-off values altogether (McShane et al. 2017).

\input{./table-4.tex}

\input{./table-5.tex}

Finally, following the arguments provided in Imai and Kim (2016), we estimate a further set of weighted linear fixed effects (WFE) models. Table \ref{table-5} displays the corresponding results, which mirror those obtained through FE estimation. The effect on life satisfaction remains robust, with and without controls. Moreover, the effect sizes seem substantively significant. In comparison, the effects on trust in government and satisfaction (M26, M28, M32, M34) are only partly statistically significant (p \textless{} 0.05 in M28, M32). Furthermore, they are generally small in size as compared to the effect on life satisfaction, despite the fact that all outcomes are measured on 11-point scales.\footnote{The within-unit over time variation of life satisfaction is lower than that of trust in government and satisfaction with democracy. Besides, scholars recently suggested that p-values between 0.005 and 0.05 can only be regarded as suggestive evidence (Benjamin et al. 2017, 3).} Given this inconsistency, our results seem to support \(H_{0}\), namely that \emph{unemployment has no effect on trust in government or satisfaction with democracy}. This general pattern is visualized in Figure \ref{fig-results}, which summarizes the results. We discuss limitations that may undermine this conclusion below.

\begin{figure}[h]
\centering
\caption{Visualization of effects across models, outcomes and datasets}\label{fig-results}
        \includegraphics[width=1\linewidth]{fig-1.jpg}
\begin{flushleft}
\scriptsize Note: Filled (SHP data) and empty (LISS data) symbols represent point estimates of effects for 36 models; lines represent 95\% confidence intervals;  model names M1-M36 correspond to model names in Table 3, 4 and 5; see plot legend for further explanation; FE = fixed effects, WFE = Weighted linear fixed effects; data: Swiss Household Panel (SHP) and Longitudinal Internet Studies for the Social sciences (LISS).
\end{flushleft}
\end{figure}

\hypertarget{sec:conclusion}{%
\section{Discussion and conclusion}\label{sec:conclusion}}

We investigate whether unemployment affects trust in government and satisfaction with democracy. We thereby contribute to current scholarship on the effects of unemployment (Brand 2015; Naumann, Buss, and Bähr 2016; Margalit 2013), on causes of political trust and satisfaction with democracy (e.g. Listhaug and Jakobsen 2017), and on the more general link between experiences and trust (Listhaug and Jakobsen 2017; Dinesen and Bekkers 2015). Relying on panel data and corresponding models, we find no consistent evidence that unemployment negatively affects trust in government or satisfaction with democracy, which is in line with \(H_{0}\). However, we can replicate earlier findings on the negative relationship between unemployment and life satisfaction (cf. Winkelmann and Winkelmann 1998), which suggests that our apparent non-finding is not merely a result of the methods we apply. Our findings somewhat contrast macro-level evidence that links unemployment to political trust (e.g. Kroknes, Jakobsen, and Grønning 2015; Roth, Nowak-Lehmann, and Otter 2011) but also micro-level evidence that links unemployment to support for the welfare state and unemployment benefits (Naumann, Buss, and Bähr 2016; Margalit 2013). The former contrast can possibly be explained by both the classic pocketbook--sociotropic voter argument and by case selection. The latter difference is more intriguing. It seems to indicate that an experience of unemployment may affect concrete attitudes towards policies linked to unemployment, while more abstract attitudes remain largely unaffected.\\
Our study is characterized by limitations. These may explain the above-mentioned differences but also serve as starting points for future research. First, in line with other panel-data studies that focus on single countries (e.g. Margalit 2013; Naumann, Buss, and Bähr 2016), we analyze panel data from ``only'' two countries, Switzerland and the Netherlands. As discussed before, the relationship between unemployment and political evaluations may hinge on the prevalence of certain norms, on the basis of which the unemployed blame the government or the political system for their fate or not. Such a mechanism seems highly unlikely in some contexts, e.g.~the U.S., but more likely in other contexts, e.g.~Spain. While the effects we find are relatively consistent across two countries, more panel data from a wider set of countries may allow researchers to investigate such potential for context dependence.\\
A second drawback concerns the particular types of unemployment experiences we study. We do not have enough information to properly unpack what experiences lurk behind our unemployment variable. The reasons why someone has become unemployed should matter. Future studies would ideally measure and differentiate between such reasons for unemployment in a more fine-grained way. For instance, someone whose unemployment was a direct consequence of the crisis may be quicker to connect her situation to politics. Furthermore, we focus on the effects of direct unemployment experiences. However, following the sociotropic argument, indirect experiences of unemployment, e.g.~observing people in one's network (Newman and Vickrey 2017) or in one's neighborhood (Bisgaard 2015; Oesch and Lipps 2013), may equally matter. Studying and contrasting such indirect experiences with direct experiences is an important area of future research.\\
Third, time matters. To start, the length of treatment could matter. It seems plausible that long-term unemployment affects political evaluations to a greater extent than short-term unemployment. Our data do not contain enough observations of the long-term unemployed. Although collecting such data is challenging, we nevertheless think that studying the political attitudes of citizens who have been excluded from the labor market for long periods is relevant, especially given predictions of how automation may increase levels of unemployment (e.g. Arntz, Gregory, and Zierahn 2016). Of course, studying such long-term lags and the effects of long-term unemployment is challenging from a design perspective. The longer an individual's period of unemployment is, the less likely we are to find a suitable control unit or observation that displays a similar life trajectory and differentiates itself only through being employed. On another note, with one-year panel periods we may fail to capture effects that are more short-term. Thus, future studies would ideally measure our individual-level outcomes on a more frequent basis both before and after the onset of unemployment.\\
Finally, our investigation is limited by the sample size. In principle, it is possible that the effect of unemployment is heterogeneous across (subgroups of) individuals (treatment effect heterogeneity). For certain individuals, the causal story we provide may seem more plausible. For instance, unemployment may have a stronger effect on groups that are already disadvantaged in the labor market, such as women or individuals with lower class background. Similarly, individuals' ideology should determine whether they link their personal economic situation to a government or to the wider political system. Future data collections that comprise more individuals may allow for an exploration of such assumed treatment heterogeneity.

\newpage

\hypertarget{sec:appendix}{%
\section{Appendix}\label{sec:appendix}}

\input{./table-6.tex}

\input{./table-7.tex}

\input{./table-8.tex}

\normalsize

\clearpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Ahn2004-mg}{}%
Ahn, Namkee, Juan Ramon Garcia, and Juan Francisco Jimeno. 2004. ``Well-Being Consequences of Unemployment in Europe.''

\leavevmode\hypertarget{ref-Almond1963-bp}{}%
Almond, Gabriel A, and Sidney Verba. 1963. \emph{The Civic Culture: Political Attitudes and Democracy in Five Nations}. New Jersey: Princeton University Press.

\leavevmode\hypertarget{ref-Archer1993-bq}{}%
Archer, John, and Valerie Rhodes. 1993. ``The Grief Process and Job Loss: A Cross-Sectional Study.'' \emph{British Journal of Psychology} 84 (3). Wiley Online Library: 395--410.

\leavevmode\hypertarget{ref-Arias2013-px}{}%
Arias, Omar, Walter Sosa-Escudero, Davis Alfaro Serrano, Maria Edo, and Indira Santos. 2013. ``Do Jobs Lead to More Trust? A Synthetic Cohorts Approach.''

\leavevmode\hypertarget{ref-Armingeon2014-ut}{}%
Armingeon, Klaus, and Besir Ceka. 2014. ``The Loss of Trust in the European Union During the Great Recession Since 2007: The Role of Heuristics from the National Political System.'' \emph{European Union Politics} 15 (1): 82--107.

\leavevmode\hypertarget{ref-Armingeon2014-xg}{}%
Armingeon, Klaus, and Kai Guthmann. 2014. ``Democracy in Crisis? The Declining Support for National Democracy in European Countries, 2007--2011.'' \emph{European Journal of Political Research} 53 (3): 423--42.

\leavevmode\hypertarget{ref-Arntz2016-od}{}%
Arntz, Melanie, Terry Gregory, and Ulrich Zierahn. 2016. ``The Risk of Automation for Jobs in OECD Countries: A COMPARATIVE ANALYSIS.'' \emph{OECD Social, Employment, and Migration Working Papers; Paris}. United States--US, France: Organisation for Economic Cooperation; Development (OECD).

\leavevmode\hypertarget{ref-Bay2002-fg}{}%
Bay, Ann-Helén, and Morten Blekesaune. 2002. ``Youth, Unemployment and Political Marginalisation.'' \emph{International Journal of Social Welfare} 11 (2). Blackwell Publishers Ltd: 132--39.

\leavevmode\hypertarget{ref-Benjamin2017-rf}{}%
Benjamin, Daniel J, James O Berger, Magnus Johannesson, Brian A Nosek, E-J Wagenmakers, Richard Berk, Kenneth A Bollen, et al. 2017. ``Redefine Statistical Significance.'' \emph{Nature Human Behaviour}, September. Nature Publishing Group, 1.

\leavevmode\hypertarget{ref-Bisgaard2015-xb}{}%
Bisgaard, Martin. 2015. ``Bias Will Find a Way: Economic Perceptions, Attributions of Blame, and Partisan-Motivated Reasoning During Crisis.'' \emph{The Journal of Politics} 77 (3): 849--60.

\leavevmode\hypertarget{ref-Blackaby1999-qd}{}%
Blackaby, David, Derek Leslie, Philip Murphy, and Nigel O'Leary. 1999. ``Unemployment Among Britain's Ethnic Minorities.'' \emph{The Manchester School of Economic and Social Studies} 67 (1): 1--20.

\leavevmode\hypertarget{ref-Blundell1987-qz}{}%
Blundell, Richard, John Ham, and Costas Meghir. 1987. ``Unemployment and Female Labour Supply.'' \emph{The Economic Journal of Nepal} 97 (January): 44--64.

\leavevmode\hypertarget{ref-Brand2015-rr}{}%
Brand, Jennie E. 2015. ``The Far-Reaching Impact of Job Loss and Unemployment.'' \emph{Annual Review of Sociology} 41: 359--75.

\leavevmode\hypertarget{ref-Brehm1997-qy}{}%
Brehm, John, and Wendy Rahn. 1997. ``Individual-Level Evidence for the Causes and Consequences of Social Capital.'' \emph{American Journal of Political Science} 41 (3): 999--1023.

\leavevmode\hypertarget{ref-Chabanet2007-ro}{}%
Chabanet. 2007. ``Die Politischen Konsequenzen von Arbeitslosigkeit Und Prekärer Beschäftigung in Europa.'' \emph{Forschungsjournal NSB} 20 (1): 71--80.

\leavevmode\hypertarget{ref-Collier2005-ja}{}%
Collier, William. 2005. ``Unemployment Duration and Individual Heterogeneity: A Regional Study.'' \emph{Applied Economics} 37 (2): 133--53.

\leavevmode\hypertarget{ref-Croissant2008-tb}{}%
Croissant, Yves, Giovanni Millo, and Others. 2008. ``Panel Data Econometrics in R: The Plm Package.'' \emph{Journal of Statistical Software} 27 (2): 1--43.

\leavevmode\hypertarget{ref-Croissant2017-mt}{}%
Croissant, Yves, Giovanni Millo, Kevin Tappe, Ott Toomet, Christian Kleiber, Achim Zeileis, Arne Henningsen, Liviu Andronic, and Nina Schoenfelder. 2017. ``Linear Models for Panel Data {[}R Package Plm Version 1.6-6{]}.'' Comprehensive R Archive Network (CRAN).

\leavevmode\hypertarget{ref-Dalton2004-ba}{}%
Dalton, Russell J. 2004. \emph{Democratic Challenges, Democratic Choices: The Erosion of Political Support in Advanced Industrial Democracies}. Comparative Politics. Oxford: Oxford University Press.

\leavevmode\hypertarget{ref-Delhey2003-hv}{}%
Delhey, J, and K Newton. 2003. ``Who Trusts? The Origins of Social Trust in Seven Societies.'' \emph{European Societies} 5: 93--137.

\leavevmode\hypertarget{ref-Dinesen2015-fr}{}%
Dinesen, Peter Thisted, and René Bekkers. 2015. ``The Foundations of Individuals' Generalized Social Trust: A Review.'' In \emph{Trust in Social Dilemmas}, edited by Paul A M Van Lange, Bettina Rockenbach, and Toshio Yamagishi, 77--100. Oxford University Press.

\leavevmode\hypertarget{ref-Easton1975-pe}{}%
Easton, David. 1975. ``A Re-Assessment of the Concept of Political Support.'' \emph{British Journal of Political Science} 5 (04). Cambridge Univ Press: 435--57.

\leavevmode\hypertarget{ref-European_Commission2012-pk}{}%
European Commission. 2012. ``European Employment Observatory Review: Long-Term Unemployment 2012.'' European Commission: Directorate-General for Employment, Social Affairs; Inclusion.

\leavevmode\hypertarget{ref-Falk2011-ni}{}%
Falk, Armin, Andreas Kuhn, and Josef Zweimueller. 2011. ``Unemployment and Right-Wing Extremist Crime.'' \emph{Scand. J. Econ.} 113 (2). Blackwell Publishing Ltd: 260--85.

\leavevmode\hypertarget{ref-Foster2017-si}{}%
Foster, Chase, and Jeffry Frieden. 2017. ``Crisis of Trust: Socio-Economic Determinants of Europeans' Confidence in Government.'' \emph{European Union Politics}, August, 1465116517723499.

\leavevmode\hypertarget{ref-Goldsmith1996-ks}{}%
Goldsmith, Arthur H, Jonathan R Veum, and William Darity Jr. 1996. ``The Psychological Impact of Unemployment and Joblessness.'' \emph{The Journal of Socio-Economics} 25 (3): 333--58.

\leavevmode\hypertarget{ref-Granovetter1973-vq}{}%
Granovetter, Mark S. 1973. ``The Strength of Weak Ties.'' \emph{The American Journal of Sociology} 78 (6): 1360--80.

\leavevmode\hypertarget{ref-Hansford2015-pd}{}%
Hansford, Thomas G, and Brad T Gomez. 2015. ``Reevaluating the Sociotropic Economic Voting Hypothesis.'' \emph{Electoral Studies} 39: 15--25.

\leavevmode\hypertarget{ref-Hetherington1998-kn}{}%
Hetherington, Marc J. 1998. ``The Political Relevance of Political Trust.'' \emph{The American Political Science Review} 92 (4): 791--808.

\leavevmode\hypertarget{ref-Hetherington2005-el}{}%
---------. 2005. \emph{Why Trust Matters: Declining Political Trust and the Demise of American Liberalism}. Princeton, NJ: Princeton University Press.

\leavevmode\hypertarget{ref-Hlavac2014-wd}{}%
Hlavac, Marek. 2014. ``Stargazer: LaTeX Code and ASCII Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{R Foundation for Statistical Computing}.

\leavevmode\hypertarget{ref-Hudson2006-hz}{}%
Hudson, John. 2006. ``Institutional Trust and Subjective Well-Being Across the EU.'' \emph{Kyklos} 59 (1): 43--62.

\leavevmode\hypertarget{ref-Imai2016-td}{}%
Imai, Kosuke, and In Song Kim. 2016. ``When Should We Use Linear Fixed Effects Regression Models for Causal Inference with Longitudinal Data?'' \emph{Working Paper}.

\leavevmode\hypertarget{ref-Jahoda1974-or}{}%
Jahoda, Marie, and Hans Zeisel. 1974. \emph{Marienthal: The Sociography of an Unemployed Community}. New Jersey: Transaction Publishers.

\leavevmode\hypertarget{ref-Kim2017-vu}{}%
Kim, In Song, Kosuke Imai, and Erik Wang. 2017. ``Weighted Linear Fixed Effects Regression Models for Causal Inference {[}R Package Wfe Version 1.6{]}.'' Comprehensive R Archive Network (CRAN).

\leavevmode\hypertarget{ref-Kinder1981-nz}{}%
Kinder, Donald R, and D Roderick Kiewiet. 1981. ``Sociotropic Politics: The American Case.'' \emph{British Journal of Political Science} 11 (2): 129--61.

\leavevmode\hypertarget{ref-Kroknes2015-ft}{}%
Kroknes, Veronica Fagerland, Tor Georg Jakobsen, and Lisa-Marie Grønning. 2015. ``Economic Performance and Political Trust: The Impact of the Financial Crisis on European Citizens.'' \emph{European Societies} 17 (5): 700--723.

\leavevmode\hypertarget{ref-Laurence2015-nk}{}%
Laurence, James. 2015. ``(Dis)placing Trust: The Long-Term Effects of Job Displacement on Generalised Trust over the Adult Lifecourse.'' \emph{Social Science Research} 50 (March): 46--59.

\leavevmode\hypertarget{ref-Leana1992-cp}{}%
Leana, Carrie R, and Daniel C Feldman. 1992. \emph{Coping with Job Loss: How Individuals, Organizations, and Communities Respond to Layoffs}. New York: Free Press.

\leavevmode\hypertarget{ref-Levi2000-dx}{}%
Levi, Margaret, and Laura Stoker. 2000. ``Political Trust and Trustworthiness.'' \emph{Annual Review of Political Science} 3: 475--507.

\leavevmode\hypertarget{ref-Linn1985-gi}{}%
Linn, M W, R Sandifer, and S Stein. 1985. ``Effects of Unemployment on Mental and Physical Health.'' \emph{American Journal of Public Health} 75 (5): 502--6.

\leavevmode\hypertarget{ref-Listhaug2017-et}{}%
Listhaug, Ola, and Tor Georg Jakobsen. 2017. ``Foundations of Political Trust.'' In \emph{The Oxford Handbook of Social and Political Trust}, edited by Eric M Uslaner. Oxford: Oxford University Press.

\leavevmode\hypertarget{ref-Lundin2009-gh}{}%
Lundin, Andreas, and Tomas Hemmingsson. 2009. ``Unemployment and Suicide.'' \emph{The Lancet} 374 (9686): 270--71.

\leavevmode\hypertarget{ref-Margalit2013-ph}{}%
Margalit, Yotam. 2013. ``Explaining Social Policy Preferences: Evidence from the Great Recession.'' \emph{The American Political Science Review} 107 (1): 80--103.

\leavevmode\hypertarget{ref-McShane2017-bc}{}%
McShane, Blakeley B, David Gal, Andrew Gelman, Christian Robert, and Jennifer L Tackett. 2017. ``Abandon Statistical Significance,'' September.

\leavevmode\hypertarget{ref-Mishler2001-fp}{}%
Mishler, William, and Richard Rose. 2001. ``What Are the Origins of Political Trust?: Testing Institutional and Cultural Theories in Post-Communist Societies.'' \emph{Comparative Political Studies} 34 (1): 30--62.

\leavevmode\hypertarget{ref-Mishler2005-mk}{}%
---------. 2005. ``What Are the Political Consequences of Trust?: A Test of Cultural and Institutional Theories in Russia.'' \emph{Comparative Political Studies} 38 (9): 1050--78.

\leavevmode\hypertarget{ref-Misztal2001-vv}{}%
Misztal, Barbara A. 2001. ``Trust and Cooperation: The Democratic Public Sphere.'' \emph{Journal of Sociology} 37 (4): 371--86.

\leavevmode\hypertarget{ref-Muro2014-jg}{}%
Muro, Diego, and Guillem Vidal. 2014. ``Persistent Unemployment Poses a Substantive Threat to Democracy in Southern European Countries.'' \url{http://blogs.lse.ac.uk/europpblog/2014/03/13/persistent-unemployment-poses-a-substantive-threat-to-democracy-in-southern-european-countries/}.

\leavevmode\hypertarget{ref-Naumann2016-yh}{}%
Naumann, Elias, Christopher Buss, and Johannes Bähr. 2016. ``How Unemployment Experience Affects Support for the Welfare State: A Real Panel Approach.'' \emph{European Sociological Review} 32 (1): 81--92.

\leavevmode\hypertarget{ref-Newman2017-ls}{}%
Newman, Benjamin J, and Clifford D Vickrey. 2017. ``Friends on the Dole: Social Networks, Vicarious Economic Distress, and Support for Social Welfare Spending.'' \emph{International Journal of Public Opinion Research} 29 (1): 172--88.

\leavevmode\hypertarget{ref-Newton2011-ix}{}%
Newton, Ken, and Sonja Zmerli. 2011. ``Three Forms of Trust and Their Association.'' \emph{European Political Science Review} 3 (2): 169--200.

\leavevmode\hypertarget{ref-Oecd2017-pq}{}%
OECD. 2017a. ``Harmonised Unemployment Rate (HUR).'' \url{http://dx.doi.org/10.1787/52570002-en}.

\leavevmode\hypertarget{ref-Oecd2017-lj}{}%
---------. 2017b. ``Unemployment Rate.'' \url{http://dx.doi.org/10.1787/997c8750-en}.

\leavevmode\hypertarget{ref-Oesch2013-za}{}%
Oesch, Daniel, and Oliver Lipps. 2013. ``Does Unemployment Hurt Less If There Is More of It Around? A Panel Analysis of Life Satisfaction in Germany and Switzerland.'' \emph{European Sociological Review} 29 (5). Oxford University Press: 955--67.

\leavevmode\hypertarget{ref-Perrucci2009-yq}{}%
Perrucci, Robert, and Carolyn C Perrucci. 2009. \emph{America at Risk: The Crisis of Hope, Trust, and Caring}. Lanham, MD: Rowman \& Littlefield Publishers.

\leavevmode\hypertarget{ref-Pharr2000-qy}{}%
Pharr, S, and R Putnam. 2000. \emph{Disaffected Democracies: What's Troubling the Trilateral Countries?} Princeton, NJ: Princeton University Press.

\leavevmode\hypertarget{ref-Putnam2000-ea}{}%
Putnam, Robert David. 2000. \emph{Bowling Alone: The Collapse and Revival of American Community}. New York: Simon \& Schuster.

\leavevmode\hypertarget{ref-Rantakeisu1997-lb}{}%
Rantakeisu, U, B Starrin, and C Hagquist. 1997. ``Unemployment, Shame and Ill Health --- an Exploratory Study.'' \emph{Scandinavian Journal of Social Welfare} 6 (1): 13--23.

\leavevmode\hypertarget{ref-Roth2009-jh}{}%
Roth, Felix. 2009. ``The Effect of the Financial Crisis on Systemic Trust.'' \emph{Intereconomics} 44 (4): 203--8.

\leavevmode\hypertarget{ref-Roth2011-nb}{}%
Roth, Felix, Felicitas Nowak-Lehmann, and Thomas Otter. 2011. ``Has the Financial Crisis Shattered Citizens' Trust in National and European Governmental Institutions? Evidence from the EU Member States, 1999-2010.'' \emph{Centre for European Policy Studies Papers} 343 (4159).

\leavevmode\hypertarget{ref-Scott1979-aw}{}%
Scott, Wilbur J, and Alan C Acock. 1979. ``Socioeconomic Status, Unemployment Experience, and Political Participation: A Disentangling of Main and Interaction Effects.'' \emph{Political Behavior} 1 (4): 361--81.

\leavevmode\hypertarget{ref-Siedler2006-yw}{}%
Siedler, Thomas. 2006. ``Family and Politics: Does Parental Unemployment Cause Right-Wing Extremism?'' \emph{IZA Discussion Paper} 2411: 1--49.

\leavevmode\hypertarget{ref-Stokes1984-so}{}%
Stokes, Graham, and Raymond Cochrane. 1984. ``A Study of the Psychological Effects of Redundancy and Unemployment.'' \emph{Journal of Occupational Psychology} 57 (4): 309--22.

\leavevmode\hypertarget{ref-Uslaner2002-ks}{}%
Uslaner, Eric M. 2002. \emph{The Moral Foundations of Trust}. Cambridge, United Kingdom: Cambridge University Press.

\leavevmode\hypertarget{ref-Waters2007-os}{}%
Waters, Lea. 2007. ``Experiential Differences Between Voluntary and Involuntary Job Redundancy on Depression, Job-Search Activity, Affective Employee Outcomes and Re-Employment Quality.'' \emph{Journal of Occupational and Organizational Psychology} 80 (2): 279--99.

\leavevmode\hypertarget{ref-Winkelmann1998-kb}{}%
Winkelmann, Liliana, and Rainer Winkelmann. 1998. ``Why Are the Unemployed so Unhappy?Evidence from Panel Data.'' \emph{Economica} 65 (257): 1--15.

\leavevmode\hypertarget{ref-Wooldridge2010-jb}{}%
Wooldridge, Jeffrey M. 2010. \emph{Econometric Analysis of Cross Section and Panel Data}. Cambridge, MA: MIT press.

\leavevmode\hypertarget{ref-Zawadzki1935-gg}{}%
Zawadzki, Bohan, and Paul Lazarsfeld. 1935. ``The Psychological Consequences of Unemployment.'' \emph{The Journal of Social Psychology} 6 (2): 224--51.

\end{document}

### 2020-04-28 Milestones/milestone6.5.Rmd
organzing my repo

--- 2020-04-18 milestone7.Rmd
@@
 ---
-title: "GOV 1006: Milestone 7"
+title: "GOV 1006: Milestone 6.5"
 subtitle: "Paper Replication"
 author: "Pieter Quinton"
-date: "4/17/2020"
-abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy.
-I was able to completely replicate the majority of his findings aside from a summary table of the data.
-My extension evaluates how consistent or long-term unemployment may impact one's views.
-Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
+date: "4/3/2020"
 output: 
@@
     keep_tex: true
-    toc: no
-document_class: article
 bibliography: milestone5_bib.bib
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.align = "left")
+knitr::opts_chunk$set(echo = FALSE)
 
-library(rsconnect)
 library(stargazer)
@@
 library(tidyverse)
-```
-
-```{r data}
-
-# Loaded the LISS data from the directory
-
-load(file = "./data-long-liss.RData")
-
-# Saved the loaded data as liss
-
-liss <- data.long.liss
-
-# Loaded the SHP data from the directory
-
-load(file = "./data-long-shp.RData")
-
-# Saved the data as SHP
-
-shp <- data.long.shp
 ```
@@
 
+The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
+The goal of my extension to provide further insights and clarity into that relationship.
+I intend build off the general models created by Bauer by including an interaction term between education and age in the regressions.
+As it stands, Bauer uses an additive regression with age, education, and membership as the controls.
+Given the entirety of the dataset is used in the current analysis, there is a limitation as to what is available for my extension.
+However, I feel that the addition of an interaction term between education and age could prove to be a valuable contribution to the models presented in the paper.
+My assumption is that there could be heterogeneous effects of education on the relationship between unemployment and trust in government or satisfaction with democracy depending on one's age.
+This proposed interaction is relatively straight forward.
+
+Though the inclusion of the interaction is valuable, I feel there is an even more important extension I can attach to Bauer’s paper.
+Because his paper utilizes panel data, it tracks households across time.
+He mentions a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
+My hope is to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
+By identifying these households, I would like to test how their unemployment experiences effect their views on democracy and the government and compare that to households with one-off unemployment and households without unemployment.
+My hypothesis is in line with Bauer’s.
+I predict that households that are experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
+
+I’m still working through my exact plan of action for completing the long-term vs.
+short-term unemployment extension.
+However, my initial thoughts suggest that I will create a new variable indicating whether someone had been unemployed the year before.
+That variable can be added to the regression as a control.
+I am also thinking about creating a variable with the number of years a household reported being unemployed during the reporting and attaching that to the regression.
+I may end up running separate regressions so to avoid overfitting the data but we will see.
+
 ## Literature Review
@@
 
-## Replication
-
-I the appendix, I provide five replicated tables from the original publication.
-Of the five, Tables 1,3,4,5 were all replicable with no discrepencies.
-However, my replication of Table 2, did not completely match that of the paper.
-In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source.
-In his replication material, I can find where Bauer creates each of the other tables but not Table 2.
-Nonetheless, I attempted to replicate the table and largely suceeded.
-There were two variations between our tables.
-Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent.
-These discrepencies need to be explored further.
-
-## Extension
-
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
-The goal of my extension to provide further insights and clarity into that relationship.
-
-Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes.
-In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
-
-My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
-By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment.
-My hypothesis was in line with Bauer’s.
-I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
-
-To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment.
-I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment.
-The coefficient on the interaction term represents a household with unemployment in the present year and in the year before.
-The interaction coefficient is the one I am most interested in.
-As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.
-
-```{r extension}
-
-liss <- liss %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
-
-shp <- shp %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
-
-```
-
-```{r tableExtension1, results='asis'}
-
-# SHP
-# I run six regressions
-# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
-# The first regression is just with unemployed as the indenpendent variable
-# The second regression includes the controls (age, education, and member)
-# The regression uses a pooling technique (plm) to track observations across units (households) 
-# over time
-
-shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# LISS
-# Same as above but with the LISS data instead of the SHP data
-
-liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# I display the results using a stargazer table
-# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
-# adjusting the separation width between columns
-# I can't figure out how to add a split header above the dependent variables to separate between 
-# SHP and LISS
-# I will keep working on this
-
-stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          column.sep.width = "-8.5pt",
-          title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
-          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-
-```
-
-```{r tableExtension2, results = 'asis'}
-
-# SHP
-# The same process as above but I used a fixed effects model instead of a pooled model
-# The only difference is I change model from "pooled" to "within"
-
-shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# LISS
-# Same as for SHP but with the LISS data
-
-liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# Stargazer output with the same formatting as Table 3
-
-stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          label = "table-5",
-          column.sep.width = "-8.5pt",
-          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
-          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-```
-
-```{r extension3, include=FALSE}
-
-# SHP
-# Same regressions but this time with the weighted fixed effects
-# I didn't really understand how these were created so I largely mimicked what Bauer did in his
-# replication code
-
-shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                      unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# LISS
-# Same as SHP but with LISS data
-
-liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# The above regressions do not create an output that can be displayed through stargazer
-# Instead I needed to manually run the regression with the included weights and then manually
-# input those values into stargazer
-# Again, I didn't really know how to do this so I just followed what Bauer did.
-
-  regressors_int <- c("Unemployed", "Lagged")
-
-  regressors_cont <- c("Age", "Education", "Member")
-
-  d <- as.data.frame(matrix(rnorm(10 * 7), nc = 7))
-
-  dep.var1 <- "Trust_in_government"
-
-  names(d) <- c(dep.var1, regressors_int, regressors_cont)
-
-  f <- as.formula(paste(dep.var1, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p1 <- lm(f, d)
-
-  dep.var2 <- "Satisfaction_with_democracy"
-
-  names(d) <- c(dep.var2, regressors_int, regressors_cont)
-
-   f <- as.formula(paste(dep.var2, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p2 <- lm(f, d)
-
-  dep.var3 <- "Life_satisfaction"
-
-  names(d) <- c(dep.var3, regressors_int, regressors_cont)
-
-   f <- as.formula(paste(dep.var3, "~ 0 +", paste(regressors_int, collapse = "*"), "+", paste(regressors_cont, collapse = "+")))
-
-  p3 <- lm(f, d)
-
-```
-
-```{r table3output, results='asis'}
-
-# Stargazer output
-# I manually pull out the coefficient values from the regressions and add those to the
-# skeleton of the regression that was created above
-# I have to do this for each coefficient, each standard error, and each t and p value
-
-# Then I format the stargazer table in the same manner as the previous two
-
-  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
-    coef = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])
-
-                ),
-    se = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
-              ),
-    t = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])
-
-             ),  
-    p = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),
-
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
-             ),  
-    omit.stat = "all",
-    notes = "SEs in parentheses.\n Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
-    notes.append = TRUE,
-    font.size = "tiny",
-    digits = 2,
-    column.sep.width = "-10pt", 
-    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
-    digit.separator="",
-    rownames = FALSE,
-    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
-    model.names = FALSE,
-    model.numbers = FALSE,
-    star.cutoffs=c(0.05,0.01,0.001),
-    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-    header = FALSE
-    )
-
-```
-
-\newpage
-
-## Conclusion
-
 \newpage

### 2020-04-28 Milestones/milestone6.Rmd
organzing my repo

--- 2020-04-18 milestone6.Rmd
@@
   shp_1,
+  type = "latex",
+  out="./replication-table-1.tex",
   header = FALSE,
@@
   shp_2,
+  type = "latex",
+  out="./replication-table-2.tex",
   header = FALSE,

### 2020-04-28 analysis.Rmd
organzing my repo

--- 2020-04-18 milestone7.Rmd
@@
 ---
-title: "GOV 1006: Milestone 7"
-subtitle: "Paper Replication"
+title: "Paper Analysis Code"
 author: "Pieter Quinton"
-date: "4/17/2020"
-abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy.
-I was able to completely replicate the majority of his findings aside from a summary table of the data.
-My extension evaluates how consistent or long-term unemployment may impact one's views.
-Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
+date: "4/23/2020"
 output:
-  bookdown::pdf_document2:
-    keep_tex: true
-    toc: no
-document_class: article
-bibliography: milestone5_bib.bib
+  pdf_document: default
+  html_document: default
 ---
@@
 
-load(file = "./data-long-liss.RData")
+load(file = "./Dataverse/data-long-liss.RData")
 
@@
 
-load(file = "./data-long-shp.RData")
+load(file = "./Dataverse/data-long-shp.RData")
 
@@
 
-## Introduction
-
-The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018).
-^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] It was authored by Paul C.
-Bauer in 2018.
-The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general.
-Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.
-
-The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general.
-Bauer also controls for variations in age, education, and party membership.
-Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon.
-All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.
-
-Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy.
-These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions.
-However, Bauer does find that unemployment is negatively related to life satisfaction.
-People who are unemployed are generally less satisfied with their lives than those who are employed.
-This finding is consistent with previous research on the topic.
-Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
-For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.
-
-## Literature Review
-
-The impetus for Bauer's paper relies on the fundamental assumption that should a person blame the government or its institutions for their current situation in life, a decrease in the quality of that situation would result in a corresponding decrease in their satisfaction with the government.
-This assumption stems from the work of John Hudson who examined the relationship between trust in institutions and one's subjective well-being (@hudson2006).
-Research shows a statistically significant relationship between one's employment status and their life satisfaction (@jimeno2007).
-As one moves from employed to unemployed, their life satisfaction tends to decrease.
-Given the two findings, the aim of Bauer's work is to test the hypothesis that unemployment leads to lower levels of trust in government and satisfaction with democracy.
-
-## Replication
-
-I the appendix, I provide five replicated tables from the original publication.
-Of the five, Tables 1,3,4,5 were all replicable with no discrepencies.
-However, my replication of Table 2, did not completely match that of the paper.
-In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source.
-In his replication material, I can find where Bauer creates each of the other tables but not Table 2.
-Nonetheless, I attempted to replicate the table and largely suceeded.
-There were two variations between our tables.
-Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent.
-These discrepencies need to be explored further.
-
-## Extension
-
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
-The goal of my extension to provide further insights and clarity into that relationship.
-
-Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes.
-In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
-
-My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
-By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment.
-My hypothesis was in line with Bauer’s.
-I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
-
-To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment.
-I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment.
-The coefficient on the interaction term represents a household with unemployment in the present year and in the year before.
-The interaction coefficient is the one I am most interested in.
-As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.
-
-```{r extension}
+```{r extension data}
 
@@
   ungroup(unit)
-
 ```
 
-```{r tableExtension1, results='asis'}
+```{r extension table1, results = 'asis'}
 
@@
 stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
+          type = "latex",
+          out="./extension-table-1.tex",
           omit.stat=c("LL","ser","f","adj.rsq"),
@@
           digits = 2,
-          column.sep.width = "-8.5pt",
+          column.sep.width = "-10pt",
           title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
           column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
+          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
           model.names = FALSE,
@@
           )
-
 ```
 
-```{r tableExtension2, results = 'asis'}
+```{r extension table2, results = 'asis'}
 
@@
 stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
+          type = "latex",
+          out="./extension-table-2.tex",
           omit.stat=c("LL","ser","f","adj.rsq"),
@@
           digits = 2,
-          label = "table-5",
-          column.sep.width = "-8.5pt",
+          label = "table-2",
+          column.sep.width = "-10pt",
           title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
           column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
+          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
           model.names = FALSE,
@@
 
-```{r extension3, include=FALSE}
+```{r extension table3 data, include = FALSE}
 
@@
   p3 <- lm(f, d)
-
 ```
 
-```{r table3output, results='asis'}
+```{r extension table3 output, results = 'asis'}
 
@@
              ),  
+    type = "latex",
+    out="./extension-table-3.tex",
     omit.stat = "all",
@@
     star.cutoffs=c(0.05,0.01,0.001),
-    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "Unemployed:Lagged Unemployed"),
-    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
+    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
     header = FALSE
     )  
-
 ```
-
-\newpage
-
-## Conclusion
-
-\newpage
-
-## References

### 2020-04-28 Milestones/miletsone5.Rmd
organizing my repo

--- 2020-04-04 milestone6.Rmd
@@
 ---
-title: "GOV 1006: Milestone 6"
+title: "GOV 1006: Milestone 5"
 subtitle: "Paper Replication"
 author: "Pieter Quinton"
-date: "4/3/2020"
+date: "3/31/2020"
 output: 
@@
 library(plyr)
-library(plm)
-library(wfe)
 library(tidyverse)
@@
 
-I the appendix, I provide five replicated tables from the original publication.
-Of the five, Tables 1,3,4,5 were all replicable with no discrepencies.
-However, my replication of Table 2, did not completely match that of the paper.
-In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source.
-In his replication material, I can find where Bauer creates each of the other tables but not Table 2.
-Nonetheless, I attempted to replicate the table and largely suceeded.
-There were two variations between our tables.
-Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent.
-These discrepencies need to be explored further.
+In the below section, I make use of the data collected by Bauer to conduct an analysis on how unemployment, age, and education level affect a person's life satisfaction.
+I run three regressions, each adding an additional explanatory variable in the above ordering.
+This is a similar analysis to that conducted in Table 3 of his paper, though I only include the LISS data from The Netherlands.
+My regressions make use of several packages including the tidyverse, stats, and stargazer (@R-tidyverse; @R-stargazer).
+The inspiration for my analysis comes from the King et.
+al.
+article entitled "Making the Most of Statistical Analyses: Improving Interpretation and Presentation" (@king2000).
 
-## Extension
+```{r, results='asis'}
 
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
-The goal of my extension to provide further insights and clarity into that relationship.
-I intend build off the general models created by Bauer by including an interaction term between education and age in the regressions.
-As it stands, Bauer uses an additive regression with age, education, and membership as the controls.
-Given the entirety of the dataset is used in the current analysis, there is a limitation as to what is available for my extension.
-However, I feel that the addition of an interaction term between education and age could prove to be a valuable contribution to the models presented in the paper.
-My assumption is that there could be heterogeneous effects of education on the relationship between unemployment and trust in government or satisfaction with democracy depending on one's age.
-This proposed interaction is relatively straight forward.
+# Read in the data from the LISS study and save it as data
 
-Though the inclusion of the interaction is valuable, I feel there is an even more important extension I can attach to Bauer’s paper.
-Because his paper utilizes panel data, it tracks households across time.
-He mentions a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-My hope is to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
-By identifying these households, I would like to test how their unemployment experiences effect their views on democracy and the government and compare that to households with one-off unemployment and households without unemployment.
-My hypothesis is in line with Bauer’s.
-I predict that households that are experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
+data <- read_rds("data-long.rds")
 
-I’m still working through my exact plan of action for completing the long-term vs.
-short-term unemployment extension.
-However, my initial thoughts suggest that I will create a new variable indicating whether someone had been unemployed the year before.
-That variable can be added to the regression as a control.
-I am also thinking about creating a variable with the number of years a household reported being unemployed during the reporting and attaching that to the regression.
-I may end up running separate regressions so to avoid overfitting the data but we will see.
+# Select the variables I want for my regressions
+
+x <- data %>%
+  select(education, age, member, life_satisfaction, unemployed) %>%
+  drop_na()
+
+# Run three linear regressions, each time adding another explanatory variable
+
+fit1 <- lm(life_satisfaction ~ unemployed, data = x)
+
+fit2 <- lm(life_satisfaction ~ unemployed + age, data = x)
+
+fit3 <- lm(life_satisfaction ~ unemployed + age + education, data = x)
+
+# Display the results in a singular stargazer table
+# Set header to false to hide the commentary from the creator
+# Renamed the covariate labels and dependent variable to match the formatting in the paper
+# Added a title and source note
+
+stargazer(fit1, fit2, fit3,
+          header = FALSE,
+          covariate.labels = c("Unemployment", "Age", "Education"),
+          dep.var.labels = "Life Satisfaction",
+          title = "Effects of Unemployment on Life Satisfaction",
+          notes = "Data from Bauer 2018"
+          )
+```
+
+The results of my regressions confirm the general findings of Bauer.
+Like he, I also found that unemployment negatively effects a person's life satisfaction.
+I did not test the effects of unemployment on trust in government and satisfaction in democracy though I will do so in future analyses.
 
@@
 
-```{r data}
+```{r}
 
@@
 
-```{r table1, results='asis'}
+```{r, results='asis'}
 
@@
 
-```{r table2,results='asis'}
+**The actual table from the paper is below:**
 
-# I begin with the LISS data
-# I go through each column and classify whether there was a response or not (- for response and
-# blank for NA)
-# I summarize to calculate which years there were no responses for a given survey question
-# I spread the data to get the years as columns
+```{r image, out.width="100%"}
 
-liss_2 <- liss %>%
-  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
-  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
-  group_by(time) %>%
-  summarize(tig_2 = sum(trust_in_government),
-            swd_2 = sum(satisfaction_with_democracy),
-            ls_2 = sum(life_satisfaction),
-            ue_2 = sum(unemployed)) %>%
-  mutate_at(c("tig_2", "swd_2", "ls_2", "ue_2"), ~ifelse(. == 0, "", "-")) %>%
-  gather("topic", "value", tig_2:ue_2) %>%
-  group_by(topic) %>%
-  spread(time, value)
+# I wasn't sure how to add an image but I found this technique on stackoverflow and seems to
+# work well.
+# You can set the width of the image in the {r} section above which I did
 
-# I create an ordering of rows that will be used in the below table formatting
-
-ordering <- c("tig","swd","ls","ue","tig_2","swd_2","ls_2","ue_2")
-
-# I repeat the steps from LISS for SHP
-# Once I have made the table and add the LISS table below
-# I arrange by the ordering vector I just made
-
-shp_2<- shp %>%
-  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
-  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
-  group_by(time) %>%
-  summarize(tig = sum(trust_in_government),
-            swd = sum(satisfaction_with_democracy),
-            ls = sum(life_satisfaction),
-            ue = sum(unemployed)) %>%
-  mutate_at(c("tig", "swd", "ls", "ue"), ~ifelse(. == 0, "", "-")) %>%
-  gather("topic", "value", tig:ue) %>%
-  group_by(topic) %>%
-  spread(time, value) %>%
-  rbind.fill(liss_2) %>%
-  replace(is.na(.), "") %>%
-  mutate(topic = factor(topic, levels = ordering)) %>%
-  arrange(topic) %>%
-  select(-topic)
-
-# Change row names to match those in the paper
-
-row.names(shp_2) <- c("Trust in government (SHP)", "Satisfaction with democracy (SHP", "Life Satisfaction (SHP)", "Employment Status (SHP)", "Trust in government (LISS)", "Satisfaction with democracy (LISS)", "Life Satisfaction (LISS)", "Employment Status (LISS)")
-
-# Displayed the table using stargazer
-# Set header to false to hide the comments from the creator of the package
-# Set summary to false to just display the table as is
-# Changed font size and column separation width to get the table the right size for the pdf
-
-stargazer(
-  shp_2,
-  header = FALSE,
-  summary = FALSE,
-  font.size = "small",
-  column.sep.width = "-7.5pt",
-  title = "Measures across panel waves in the SHP and the LISS"
-)
+knitr::include_graphics("milestone5.png")
 ```
 
-```{r table3, results='asis'}
-
-# SHP
-# I run six regressions
-# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
-# The first regression is just with unemployed as the indenpendent variable
-# The second regression includes the controls (age, education, and member)
-# The regression uses a pooling technique (plm) to track observations across units (households) 
-# over time
-
-shp.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-shp.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# LISS
-# Same as above but with the LISS data instead of the SHP data
-
-liss.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-liss.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "pooling")
-
-# I display the results using a stargazer table
-# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
-# adjusting the separation width between columns
-# I can't figure out how to add a split header above the dependent variables to separate between 
-# SHP and LISS
-# I will keep working on this
-
-stargazer(shp.fit.pooling.tig, shp.fit.pooling.control.tig, shp.fit.pooling.swd, shp.fit.pooling.control.swd, shp.fit.pooling.ls, shp.fit.pooling.control.ls, liss.fit.pooling.tig, liss.fit.pooling.control.tig, liss.fit.pooling.swd, liss.fit.pooling.control.swd, liss.fit.pooling.ls, liss.fit.pooling.control.ls,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          column.sep.width = "-7.5pt",
-          title = "SHP Switzerland and LISS Netherlands: pooled models",
-          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
-          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-
-```
-
-```{r table4, results = 'asis'}
-
-# SHP
-# The same process as above but I used a fixed effects model instead of a pooled model
-# The only difference is I change model from "pooled" to "within"
-
-shp.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# LISS
-# Same as for SHP but with the LISS data
-
-liss.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# Stargazer output with the same formatting as Table 3
-
-stargazer(shp.fit.fe.tig, shp.fit.fe.control.tig, shp.fit.fe.swd, shp.fit.fe.control.swd, shp.fit.fe.ls, shp.fit.fe.control.ls, liss.fit.fe.tig, liss.fit.fe.control.tig, liss.fit.fe.swd, liss.fit.fe.control.swd, liss.fit.fe.ls, liss.fit.fe.control.ls,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          label = "table-3",
-          column.sep.width = "-7.5pt",
-          title = "SHP Switzerland and LISS Netherlands: fixed effects models",
-          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"), 
-          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-```
-
-```{r table5calc, include=FALSE}
-
-# SHP
-# Same regressions but this time with the weighted fixed effects
-# I didn't really understand how these were created so I largely mimicked what Bauer did in his
-# replication code
-
-shp.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        treat = "unemployed",
-                      unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-shp.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = shp,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# LISS
-# Same as SHP but with LISS data
-
-liss.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        treat = "unemployed",
-                       unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-liss.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
-                        data = liss,
-                        treat = "unemployed",
-                        unit.index = "unit", time.index = "time", method = "unit",
-               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
-               White = TRUE, White.alpha = 0.05, verbose = TRUE)
-
-# The above regressions do not create an output that can be displayed through stargazer
-# Instead I needed to manually run the regression with the included weights and then manually
-# input those values into stargazer
-# Again, I didn't really know how to do this so I just followed what Bauer did.
-
-  regressors <- c("Unemployed", "Age", "Education", "Member")
-  d <- as.data.frame(matrix(rnorm(10 * 5), nc = 5))
-  dep.var <- "Trust_in_government"
-  names(d) <- c(dep.var, regressors)
-  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
-  p1 <- lm(f, d)
-  dep.var <- "Satisfaction_with_democracy"
-  names(d) <- c(dep.var, regressors)
-  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
-  p2 <- lm(f, d)
-  dep.var <- "Life_satisfaction"
-  names(d) <- c(dep.var, regressors)
-  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
-  p3 <- lm(f, d)
-
-```
-
-```{r table5output, results='asis'}
-
-# Stargazer output
-# I manually pull out the coefficient values from the regressions and add those to the
-# skeleton of the regression that was created above
-# I have to do this for each coefficient, each standard error, and each t and p value
-
-# Then I format the stargazer table in the same manner as the previous two
-
-  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
-    coef = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,1]),
-
-                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,1])
-
-                ),
-    se = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,2]),
-
-                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,2])
-              ),
-    t = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,3]),
-
-                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,3])
-
-             ),  
-    p = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,4]),
-
-                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,4])
-             ),  
-    omit.stat = "all",
-    notes = "SEs in parentheses.",
-    notes.append = TRUE,
-    font.size = "tiny",
-    digits = 2,
-    column.sep.width = "-7.5pt", 
-    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
-    digit.separator="",
-    rownames = FALSE,
-    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
-    model.names = FALSE,
-    model.numbers = FALSE,
-    star.cutoffs=c(0.05,0.01,0.001),
-    covariate.labels = c("Unemployed", "Age", "Education", "Member"),
-    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-    header = FALSE)
-
-```
-
+This photo is displayed using a function from the knitr package (@R-knitr).
 \newpage

### 2020-05-05 analysis.Rmd
making progress

@@
 library(wfe)
+library(berryFunctions)
 library(tidyverse)
@@
 
-shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
+shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
+shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
+liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
+liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
           column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+          covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
           dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
+          dep.var.caption = c("SHP, LISS"),
           model.names = FALSE,
-          model.numbers = FALSE
+          model.numbers = FALSE,
+          order = c(1,2,6,3,4,5)
           )
@@
 
-shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
+shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
+shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
+liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
+liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
+liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
           column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+          covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
           dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
           model.names = FALSE,
-          model.numbers = FALSE
+          model.numbers = FALSE,
+          order = c(1,2,6,3,4,5)
           )
@@
 
-shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
+shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
+shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
+shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = shp,
@@
 
-liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
+liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
+liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
-liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
+liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed, 
                         data = liss,
@@
 
+```{r stargazer data}
+wfe_regression_data <- data.frame(
+  c1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
+  c2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
+  c3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
+  c4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
+  c5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
+  c6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
+  se1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
+  se2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
+  se3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
+  se4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
+  se5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
+  se6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
+  t1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
+  t2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
+  t3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
+  t4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
+  t5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
+  t6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
+  p1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
+  p2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
+  p3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
+  p4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
+  p5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
+  p6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4])
+) %>%
+  insertRows(3:5)
+```
+
 ```{r extension table3 output, results = 'asis'}
@@
   stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
-    coef = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
+    order = c(1,2,6,3,4,5),
+    coef = list(wfe_regression_data$c1,
                 as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
+                wfe_regression_data$c2,
                 as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
+                wfe_regression_data$c3,
                 as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),
 
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
+                wfe_regression_data$c4,
                 as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
+                wfe_regression_data$c5,
                 as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
+                wfe_regression_data$c6,
                 as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])
@@
                 ),
-    se = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
+    se = list(wfe_regression_data$se1,
                 as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
+                wfe_regression_data$se2,
                 as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
+                wfe_regression_data$se3,
                 as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),
 
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
+                wfe_regression_data$se4,
                 as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
+                wfe_regression_data$se5,
                 as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
+                wfe_regression_data$se6,
                 as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
               ),
-    t = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
+    t = list(wfe_regression_data$t1,
                 as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
+                wfe_regression_data$t2,
                 as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
+                wfe_regression_data$t3,
                 as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),
 
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
+                wfe_regression_data$t4,
                 as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
+                wfe_regression_data$t5,
                 as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
+                wfe_regression_data$t6,
                 as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])
@@
              ),  
-    p = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
+    p = list(wfe_regression_data$p1,
                 as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
+                wfe_regression_data$p2,
                 as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
+                wfe_regression_data$p3,
                 as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),
 
-                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
+                wfe_regression_data$p4,
                 as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
+                wfe_regression_data$p5,
                 as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
-                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4]),
+                wfe_regression_data$p6,
                 as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
@@
     star.cutoffs=c(0.05,0.01,0.001),
-    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
+    covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
     dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),

### 2020-05-05 paper.Rmd
making progress

--- 2020-04-26 milestone8.Rmd
@@
 ---
-title: "GOV 1006: Milestone 8"
-subtitle: "Paper Replication Rough Draft"
+title: "Unemployment Effects"
+subtitle: "GOV 1006: Paper Replication"
 author: "Pieter Quinton"
@@
 
-Because were are unable to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model.
+Because the data provided does not provide the ability to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model.
 There are strong differences between the pooled model and the fixed effects model.

### 2020-05-07 analysis.Rmd
added captions to my tables plus some other paper edits

@@
 library(berryFunctions)
+library(kableExtra)
 library(tidyverse)
@@
           type = "latex",
+          table.placement = "H",
           out="./extension-table-1.tex",
@@
           dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
-          dep.var.caption = c("SHP, LISS"),
           model.names = FALSE,
           model.numbers = FALSE,
-          order = c(1,2,6,3,4,5)
+          order = c(1,2,6,3,4,5),
+          notes = "\\parbox[t]{15cm}{The above table presents the results from a series of pooled effects regressions examining the relationship between unemployment and trust in government, satisfaction with democracy, and life satisfaction.
+The regression includes an interaction between unemployment (present year) and lagged unemployment (previous year) to test for the possibility of hetergenous effects between short and long-term unemployment.
+Columns 1-6 are regression outputs from the SHP survey data while columns 7-12 are regression outputs from the LISS survey data.
+Looking at the results, the 'Unemployed' coefficients are statistically across all questions for both surveys with and without controls.
+However, the lagged unemployment coefficient is only statistically significant for the SHP data and the interaction coefficient is only significant for the life satisfaction question, for both surveys.
+}"
           )
@@
           model.numbers = FALSE,
-          order = c(1,2,6,3,4,5)
+          order = c(1,2,6,3,4,5),
+          notes = "\\parbox[t]{15cm}{The above table presents the results from a series of fixed effects regressions examining the relationship between unemployment and trust in government, satisfaction with democracy, and life satisfaction.
+The regression includes an interaction between unemployment (present year) and lagged unemployment (previous year) to test for the possibility of hetergenous effects between short and long-term unemployment.
+Columns 13-18 are regression outputs from the SHP survey data while columns 19-24 are regression outputs from the LISS survey data.
+Looking at the results, the 'Unemployed' coefficients are statistically significant for the life satisfaction question for both surveys with and without controls.
+However, the lagged unemployment coefficient is only statistically significant for the satisfaction with democracy question on the SHP survey while the interaction coefficient is significant for the satisfaction with democracy on the LISS survey.}"
           )
@@
   stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
-    order = c(1,2,6,3,4,5),
     coef = list(wfe_regression_data$c1,
@@
     omit.stat = "all",
-    notes = "SEs in parentheses. Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
-    notes.append = TRUE,
+    notes = "\\parbox[t]{15cm}{The above table presents the results from a series of weighted pooled effects regressions examining the relationship between unemployment and trust in government, satisfaction with democracy, and life satisfaction.
+The regression includes an interaction between unemployment (present year) and lagged unemployment (previous year) to test for the possibility of hetergenous effects between short and long-term unemployment.
+Columns 25-30 are regression outputs from the SHP survey data while columns 31-36 are regression outputs from the LISS survey data.
+Looking at the results, the 'Unemployed' coefficient is statistically significant for the life satisfaction question on both surveys with and without controls.
+However, the lagged unemployment coefficient and the interaction coefficient are not statistically significant for any of the questions on either survey.}",
     font.size = "tiny",
@@
     dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
-    header = FALSE
+    header = FALSE,
+    order = c(1,2,6,3,4,5)
     )  

### 2020-05-07 paper.Rmd
added captions to my tables plus some other paper edits

@@
 library(wfe)
+library(kableExtra)
 library(tidyverse)
@@
 Bauer's work draws on the theoretical concepts of James Laurence who argued that the loss of one's job may lead to a deterioration of their trust in the economic system (@laurence2015).
-Furthermore, the loss of one's job brings people into closer connect with bureaucratic institutions and government social programs.
+Furthermore, the loss of one's job brings people into closer contact with bureaucratic institutions and government social programs.
 Such interactions may incite a frusturation with the way in which the government supports individuals experiencing joblessness and could lead to a dissolusionment with the current government (@waters2007).
@@
 
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction with democracy.
+The fundamental motivation behind Bauer’s paper is to study how unemployment affects trust in government and satisfaction with democracy.
 The goal of my extension to provide further insights and clarity into that relationship.
@@
 The first regression, displayed in Table 1, illustrates the results of the pooled model.
-In that model, unemployed is statistically significant across all questions of both surveys.
-Lagged unemployed is statistically significant across all questions from the SHP survey but is only statistically significant for the life satisfaction question of the LISS survey.
+In that model, 'Unemployed' is statistically significant across all questions from both surveys.
+There is a negative relationship unemployment and satisfaction with the government.
+"Lagged unemployed" is statistically significant across all questions from the SHP survey but is only statistically significant for the life satisfaction question of the LISS survey.
+The coefficients are negative but smaller in magnitude than they are for "Unemployed".
 The interaction term is only statistically significant for the life statisfaction question of each survey.
+Furthermore, the coefficients on the trust in government and satisfaction with democracy questions from the SHP survey are positive, though not significant.
 
@@
 
-Because the data provided does not provide the ability to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model.
+Because the data made available does not provide the ability to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model.
 There are strong differences between the pooled model and the fixed effects model.
@@
 As such, fewer coefficients are statistically significant.
-Unemployed is no longer statistically significant, aside from the life satisfaction questions.
-Lagged unemployed remains statistically significant for satisfaction with democracy while the interaction term is only statistically significant for life satisfaction.
+'Unemployed' is no longer statistically significant, aside from the life satisfaction questions.
+'Lagged unemployed' remains statistically significant for satisfaction with democracy while the interaction term is only statistically significant for life satisfaction.
 
@@
 
-Finally, I conduct the regression analysis using the weighted fixed effects model used by Bauer.
+Lastly, I conduct the regression analyses using the weighted fixed effects model used by Bauer.
 The coefficients have remained similar, in size, to the fixed effects model.
-However, lagged unemployed and the interaction between unemployed and lagged unemployed are no longer statistically significant for any question.
-Unemployed is statistically significant for the life satisfaction question.
+However, 'Lagged unemployed' and the interaction between 'Unemployed' and 'Lagged unemployed' are no longer statistically significant for any question.
+'Unemployed' is statistically significant for the life satisfaction question.
 
@@
 The interaction term between unemployment in the present year and unemployment in the previous year was not statistically significant.
-The lack of statistical significance indicates that the aggregation of two years of unemployment does not create significant impacts on one's views towards government and democracy.
 However, in the dataset from Switzerland (SHP) there was a statistically significant negative relationship between satisfaction with democracy and lagged unemployment.
@@
 Because the relationship between lagged unemployment and satisfaction with democracy is not present in the weighted fixed effects model, supposedly the most robust model, it is unclear how strong that finding is.
+Ultimately though, the lack of statistical significance for the interaction term indicates that the aggregation of two years of unemployment does not create significant impacts on one's views towards government and democracy.
 
@@
 Using data from the SHP and LISS household surveys, Bauer found that there was no statistically significant effect between unemployment and either trust in government or statisfaction with democracy.
-These findings challenged his hypothesis that short-term unemployment would people to loss faith in the government and its institutions.
-Bauer's hypothesis was based on theory and prior findings of a link between unemployment and decreasing life satisfcation.
+These findings challenged his hypothesis that short-term unemployment would lead people to lose faith in the government and its institutions.
+Bauer's hypothesis was based on theory and prior findings indicating a link between unemployment and decreasing life satisfaction.
 
 Using RStudio, I took Bauer's data and models and attempted to explore the possibility of heterogenous effects between short-term and long-term unemployment.
-I took advantage of the panel data to create a variable called lagged unemployment, which indicated whether a household had been unemployed in the previous year.
+I took advantage of the panel data to create a variable called lagged unemployment, which indicated whether a household had reported unemployment in the previous year.
 I included the lagged unemployment variable in Bauer's regression models as an interaction term with unemployment.
 I was very interested in the coefficient on the interaction term (signifying a household that was unemployed in both the previous year and the current year).
-I assumed, like Bauer, that the extended period of unemployment would lead to a decrease in their trust in government and satisfaction with democracy.
+I assumed, like Bauer, that the extended period of unemployment would lead to a decrease in a household's trust in government and satisfaction with democracy.
 The results from the regressions disproved that hypothesis and reaffirmed Bauer's findings.
@@
 Both my results, and Bauer's, can offer encouraging interpretations.
-As Felix Roth theorized, positive interactions with government programs and institutions arising from one's unemployment may in fact lead to improvements in that individuals feelings towards the government, or at the very least no real change (@roth2009).
-It is possible that the lack of statistically significant effects in the regression models is due to highly effective government programs for those experiencing joblessness in Switzerland and the Netherlands.
-However, it could also be due to limitations with the data.
-Regardless, futher studies making use of longer term data across several countries are warranted to more conclusively understand the link between unemployment and feelings towards government.
+As Felix Roth theorized, positive interactions with government programs and institutions during a period of unemployment may lead to improvements in that individual's feelings towards the government, or, at the very least, prevent a strong decrease in attitude (@roth2009).
+Thus, the lack of statistically significant effects in these regression models may indicate highly effective programs for those experiencing joblessness.
+Looking at the countries surveyed, Switzerland and the Netherlands, such an optimistic interpretation is plausible given the robustness of their social welfare programs.
+However, the lack of a consistent effect could also stem from limitations with the data.
+As such, futher studies making use of longer term data across several countries are warranted to more conclusively understand the link between unemployment and feelings towards government.
 

### 2020-05-08 analysis.Rmd
organized my replication code into a single r markdown file

@@
           out="./extension-table-2.tex",
+          table.placement = "H",
           omit.stat=c("LL","ser","f","adj.rsq"),
@@
     out="./extension-table-3.tex",
+    table.placement = "H",
     omit.stat = "all",
@@
     column.sep.width = "-10pt", 
-    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
+    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models with lagged unemployment",
     digit.separator="",

### 2020-05-08 paper.Rmd
organized my replication code into a single r markdown file

@@
 ---
-title: "Unemployment Effects"
+title: "Unemployment Effects: How Multi-Year Periods of Unemployment Influence Feelings Towards the Government"
 subtitle: "GOV 1006: Paper Replication"
 author: "Pieter Quinton"
-date: "4/17/2020"
+date: "5/08/2020"
 abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy.
@@
 Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
+header-includes:
+    - \usepackage{setspace}\doublespacing
 output: 

### 2020-05-08 replication.Rmd
organized my replication code into a single r markdown file

--- 2020-04-28 Milestones/milestone6.Rmd
@@
 ---
-title: "GOV 1006: Milestone 6"
-subtitle: "Paper Replication"
+title: "Replication Code"
 author: "Pieter Quinton"
-date: "4/3/2020"
-abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy.
-I was able to completely replicate the majority of his findings aside from a summary table of the data.
-My extension evaluates how consistent or long-term unemployment may impact one's views.
-Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
-output: 
-  bookdown::pdf_document2:
-    keep_tex: true
-    toc: no
-document_class: article
-bibliography: milestone5_bib.bib
+date: "5/8/2020"
+output: html_document
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = TRUE)
 
-library(rsconnect)
 library(stargazer)
@@
 shp <- data.long.shp
-```
-
-## Introduction
-
-The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018).
-^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone6/milestone6.pdf).] It was authored by Paul C.
-Bauer in 2018.
-The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general.
-Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.
-
-The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general.
-Bauer also controls for variations in age, education, and party membership.
-Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon.
-All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.
-
-Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy.
-These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions.
-However, Bauer does find that unemployment is negatively related to life satisfaction.
-People who are unemployed are generally less satisfied with their lives than those who are employed.
-This finding is consistent with previous research on the topic.
-Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
-For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.
-
-## Replication
-
-I the appendix, I provide five replicated tables from the original publication.
-Of the five, Tables 1,3,4,5 were all replicable with no discrepencies.
-However, my replication of Table 2, did not completely match that of the paper.
-In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source.
-In his replication material, I can find where Bauer creates each of the other tables but not Table 2.
-Nonetheless, I attempted to replicate the table and largely suceeded.
-There were two variations between our tables.
-Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent.
-These discrepencies need to be explored further.
-
-## Extension
-
-The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy.
-The goal of my extension to provide further insights and clarity into that relationship.
-
-Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes.
-In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment.
-Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.
-
-My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time.
-By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment.
-My hypothesis was in line with Bauer’s.
-I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.
-
-To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment.
-I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment.
-The coefficient on the interaction term represents a household with unemployment in the present year and in the year before.
-The interaction coefficient is the one I am most interested in.
-As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.
-
-```{r extension}
-
-liss_2.0 <- liss %>%
-  group_by(unit) %>%
-  summarize(total_unemployment = sum(unemployed))
-
-liss_3.0 <- liss %>%
-  filter(time == 2014) %>%
-  inner_join(liss_2.0, by = "unit")
-
-modelExtension_1 <- lm(trust_in_government ~ unemployed + age + education + member, data = liss_3.0)
-
-liss <- liss %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
-
-shp_2.0 <- shp %>%
-  group_by(unit) %>%
-  summarize(total_unemployment = sum(unemployed))
-
-shp <- shp %>%
-  group_by(unit) %>%
-  arrange(time) %>%
-  mutate(lagged_unemployed = lag(unemployed)) %>%
-  ungroup(unit)
 
 ```
-
-```{r tableExtension, results = 'asis'}
-
-# SHP
-# The same process as above but I used a fixed effects model instead of a pooled model
-# The only difference is I change model from "pooled" to "within"
-
-shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = shp,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# LISS
-# Same as for SHP but with the LISS data
-
-liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
-                        data = liss,
-                        index = c("unit", "time"),
-                        model = "within")
-
-# Stargazer output with the same formatting as Table 3
-
-stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
-          omit.stat=c("LL","ser","f","adj.rsq"),
-          header = FALSE,
-          font.size = "tiny",
-          digits = 2,
-          label = "table-5",
-          column.sep.width = "-7.5pt",
-          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
-          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
-          covariate.labels = c("Unemployed", "Lagged Unemployed", "Unemployed:Lagged Unemployed", "Age", "Education", "Member"),
-          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
-          model.names = FALSE,
-          model.numbers = FALSE
-          )
-```
-
-\newpage
-
-## Appendix
 
@@
 ```
-
-\newpage
-
-## References

### 2020-05-08 analysis.Rmd
added some stuff to my literature review

@@
 ```{r extension data}
+# Create the lagged unemployed variable
+# Arrange the panel data by unit and time so the lag command works
+# Did this for both the liss and the shp data
 
@@
 # Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
-# The first regression is just with unemployed as the indenpendent variable
-# The second regression includes the controls (age, education, and member)
+# The first set of regressions is just with the unemployed and lagged unemployed interaction as the indenpendent variable
+# The second set of regressions includes the controls (age, education, and member)
 # The regression uses a pooling technique (plm) to track observations across units (households) 
@@
 ```{r stargazer data}
+
+# Because I the wfe regression model does not create an output suitable for stargazer, 
+# Bauer had to input the data manually
+
+# After I added the interaction term the manual entries didn't match the labels so I
+# had to create this new dataframe with added blank rows to get the data to match
+
 wfe_regression_data <- data.frame(
@@
 # I have to do this for each coefficient, each standard error, and each t and p value
+
+# The data from the regressions without controls are pulled from my datatable (created # above)
+# The data from the regressions with controls are pulled from the regression outputs
 

### 2020-05-08 paper.Rmd
added some stuff to my literature review

@@
 
-"Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation", authored by Paul Bauer, explores how unemployment affects a person's trust in the government and their views towards democracy in general (@bauer2018).
-Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment status and feelings towards government on an individual level.
+"Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation", authored by Paul Bauer, explores how unemployment affects a person's trust in the government and their views towards democracy in general.^[@bauer2018] Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment status and feelings towards government on an individual level.
 Due to prior findings on the link between life satisfaction and unemployment, Bauer uses that relationship as a base metric to evaluate the magnitude of the other effects upon.
 Bauer finds that a household's unemployment status has no consistent effect on either trust in the government or satisfaction with democracy.
-These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions.
+These findings contradict the hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions.
 However, Bauer does find that unemployment is negatively associated with life satisfaction.
 People who are unemployed are generally less satisfied with their lives than those who are employed.
-This finding is consistent with previous research on the topic (@hudson2006; @jimeno2007).
-Moving forward, Bauer indicates an interest in increasing the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
+This finding is consistent with previous research on the topic.^[@hudson2006; @jimeno2007] Moving forward, Bauer indicates an interest in increasing the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals.
 For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.
 
-Starting with the replication materials provided by Bauer through the Harvard Dataverse, I worked to replicate the findings of Bauer's paper (@dataverse).^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is available through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] As Bauer did, I conducted my replication and subsequent extension in RStudio (@RStudio).
-Thanks to Bauer's well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.
+Starting with the replication materials provided by Bauer through the Harvard Dataverse, I worked to replicate the findings of Bauer's paper.^[@dataverse] As Bauer did, I conducted my replication and subsequent extension in RStudio.^[@RStudio] Thanks to Bauer's well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is available through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).]
 
@@
 
-The impetus for Bauer's paper relies on the fundamental assumption that should a person blame the government or its institutions for their current situation in life, a decrease in the quality of that situation would result in a corresponding decrease in their satisfaction with the government.
-This assumption stems from the work of John Hudson who examined the relationship between trust in institutions and one's subjective well-being (@hudson2006).
-Research shows a statistically significant relationship between one's employment status and their life satisfaction (@jimeno2007).
-As one moves from employed to unemployed, their life satisfaction tends to decrease.
+The impetus for Bauer's paper relies on the fundamental assumption that should a person blame the government or its institutions for their current situation in life, a decrease in the quality of that situation would result in a corresponding decrease in their satisfaction with the government.^[@bauer2018] This assumption stems from the work of John Hudson who examined the relationship between trust in institutions and one's subjective well-being.^[@hudson2006] Hudson found that unemployed people have,on average, lower levels of trust in government institutions from the federal to the local level.^[@hudson2006] Research shows a statistically significant relationship between one's employment status and their life satisfaction.^[@jimeno2007] As one moves from employed to unemployed, their life satisfaction tends to decrease.
 Given the two findings, the aim of Bauer's work is to test the hypothesis that unemployment leads to lower levels of trust in government and satisfaction with democracy.
 
-Bauer's work draws on the theoretical concepts of James Laurence who argued that the loss of one's job may lead to a deterioration of their trust in the economic system (@laurence2015).
-Furthermore, the loss of one's job brings people into closer contact with bureaucratic institutions and government social programs.
-Such interactions may incite a frusturation with the way in which the government supports individuals experiencing joblessness and could lead to a dissolusionment with the current government (@waters2007).
-It is from this theoretical basis that Bauer hypothesizes unemployment to be negatively associated with trust in government and satisfaction with democracy.
-There is, however, an alternative theory.
-Should a person feel supported and appreciated by the government and its programs during their period of joblessness, their feelings towards the government may not change or may even improve (@roth2009).
+Bauer's work draws on the theoretical concepts of James Laurence who argued that the loss of one's job may lead to a deterioration of their trust in the economic system.^[@laurence2015] The decrease in trust may be born out of blame for the situation however, it may also be due to increased exposure to government programs.
+The loss of one's job brings people into closer contact with bureaucratic institutions and government social programs.^[@bauer2018] Such interactions may incite a frusturation with the way in which the government supports individuals experiencing joblessness and could lead to a dissolusionment with the current government.^[@waters2007] It is from this theoretical basis that Bauer poses two hypotheses.
+The first, unemployment is negatively associated with trust in government and satisfaction with democracy.^[@bauer2018] Alternatively, should a person feel supported and appreciated by the government and its programs during their period of joblessness, their feelings towards the government may not change or may even improve.^[@roth2009] Thus, the second, or null, hypothesis is that unemployment will lead to no changes in trust in government or satisfaction with democracy.
 
@@
 
-In 2018, Paul Bauer published the paper, "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" in which he explored the relationship between a person's unemployment status and their trust in government and satisfaction with democracy (@bauer2018).
-Using data from the SHP and LISS household surveys, Bauer found that there was no statistically significant effect between unemployment and either trust in government or statisfaction with democracy.
-These findings challenged his hypothesis that short-term unemployment would lead people to lose faith in the government and its institutions.
-Bauer's hypothesis was based on theory and prior findings indicating a link between unemployment and decreasing life satisfaction.
+In 2018, Paul Bauer published the paper, "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" in which he explored the relationship between a person's unemployment status and their trust in government and satisfaction with democracy.^[@bauer2018] Using data from the SHP and LISS household surveys, Bauer found that there was no statistically significant effect between unemployment and either trust in government or statisfaction with democracy.
+These findings challenged the hypothesis that short-term unemployment would lead people to lose faith in the government and its institutions.
+That hypothesis was based on theory and prior findings indicating a link between unemployment and decreasing life satisfaction.
 
@@
 Both my results, and Bauer's, can offer encouraging interpretations.
-As Felix Roth theorized, positive interactions with government programs and institutions during a period of unemployment may lead to improvements in that individual's feelings towards the government, or, at the very least, prevent a strong decrease in attitude (@roth2009).
-Thus, the lack of statistically significant effects in these regression models may indicate highly effective programs for those experiencing joblessness.
+As Felix Roth theorized, positive interactions with government programs and institutions during a period of unemployment may lead to improvements in that individual's feelings towards the government, or, at the very least, prevent a strong decrease in attitude.^[@roth2009] Thus, the lack of statistically significant effects in these regression models may indicate highly effective programs for those experiencing joblessness.
 Looking at the countries surveyed, Switzerland and the Netherlands, such an optimistic interpretation is plausible given the robustness of their social welfare programs.
@@
 
-My replications of the first two tables in Bauer's paper are below.
-
-\input{./replication-table-1.tex}
+My replication of the second table from Bauer's paper is below.
 
@@
 
-The actual tables created by Bauer are below. As you can see, there are discrepencies between my Table 2 and his.
-
-\input{./table-1.tex}
+The actual table created by Bauer are below. As you can see, there are discrepencies between my Table 2 and his.
 

### 2020-05-08 replication_code.Rmd
reformatted

--- 2020-05-08 replication.Rmd
@@
   summary = FALSE,
-  font.size = "small",
+  font.size = "tiny", 
   column.sep.width = "-7.5pt",
-  title = "Measures across panel waves in the SHP and the LISS"
+  title = "Measures across panel waves in the SHP and the LISS",
+  notes = "\\parbox[t]{15cm}{The above table indicates the years in which data was present for each question on the two surveys. The lines represent years for which we have data. }"
 )

### 2020-05-08 paper.Rmd
renamed bib file

@@
 document_class: article
-bibliography: milestone5_bib.bib
+bibliography: bibliography.bib
 mainfont: Wingdings
